---
title: "NIHTB Age Analyses (Zero Order Correlations)"
author: "Josue Rodriguez"
date: ""
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = T, fig.width = 12, fig.height = 12)

library(BGGM)
library(dplyr)
library(ggplot2)
library(cowplot)
source("helpers.R")
```


```{r include=FALSE}
adhd_raw <- 
  haven::read_sav("../NIHTBNetwork26Oct2020.sav") %>%
  janitor::clean_names()
adhd <- as.data.frame(adhd_raw)
ef_vars <- c("dccs", "list_sort", "flank")
```



# CENTRALITY + EDGES







## 7-10 (Yg1) vs 3-6 (Yg2)

### Global Strength


```{r, echo=FALSE}
d2_ef <- make_groups(adhd, grp = 2, vars = ef_vars)
current <- d2_ef$current_age
prior1 <-  d2_ef$prior_age1
prior2 <-  d2_ef$prior_age2


net_3_to_6 <- BGGM::pcor_to_cor(estimate(d2_ef$prior_age2, progress = FALSE))
net_7_to_10 <- BGGM::pcor_to_cor(estimate(d2_ef$current_age, progress = FALSE))
```

```{r}
net_current <- net_7_to_10
net_prior2 <- net_3_to_6

gs_diffs <- get_gs_diffs(net_current, net_prior2, type = "cor", data = current)
knitr::kable(gs_diffs)
```

```{r}
obs <- gs_diffs["GS Diff", "Post.mean"]

ppc <- ggm_compare_ppc(current,
                       prior2,
                       FUN = f_gs_cor,
                       custom_obs = obs,
                       iter = 10000,
                       progress = FALSE)

ppc

plot(ppc)$plot_custom +
  theme_minimal() +
  guides(fill = FALSE) +
  ylab("")
```


### Edge-wise

```{r, echo=FALSE}
knitr::kable(get_zero_order_diffs(net_current, net_prior2, data = current))

plot_edges_diff(net_current, net_prior2, data = current) +
  coord_flip() +
  geom_hline(yintercept = c(-0.1, 0.1), col = "red", linetype = "dashed") +
  theme_minimal()


```

### Expected Influence

```{r, echo=FALSE, results="asis"}
ei_df <- get_ei_diffs(net_current, net_prior2, type = "cor", data = current)
for (i in 1:3) {
  cat("**", names(ei_df[i]), "**", sep = "")
  print(knitr::kable(ei_df[[i]]))
}
```












## 11-13 vs 3-6


### Global Strength


```{r, echo=FALSE}
d3_ef <- make_groups(adhd, grp = 3, vars = ef_vars)
current <- d3_ef$current_age

net_11_to_13 <- BGGM:::pcor_to_cor(estimate(current, progress = FALSE))
net_current <- net_11_to_13

net_prior1 <- net_3_to_6
net_prior2 <- net_7_to_10
```

```{r, echo = FALSE}
gs_diffs <- get_gs_diffs(net_current, net_prior1, type = "cor", data = current)
knitr::kable(gs_diffs)
```

```{r}
obs <- gs_diffs["GS Diff", "Post.mean"]

ppc <- ggm_compare_ppc(current,
                       prior1,
                       FUN = f_gs_cor,
                       custom_obs = obs,
                       iter = 10000,
                       progress = FALSE)

ppc

plot(ppc)$plot_custom +
  theme_minimal() +
  guides(fill = FALSE) +
  ylab("")
```

### Edge-wise

```{r, echo=FALSE}
knitr::kable(get_zero_order_diffs(net_current, net_prior1, data = current))

plot_edges_diff(net_current, net_prior1, data = current) +
  coord_flip() +
  geom_hline(yintercept = c(-0.1, 0.1), col = "red", linetype = "dashed") +
  theme_minimal()
```

### Expected Influence

```{r, echo=FALSE, results="asis"}
ei_df <- get_ei_diffs(net_current, net_prior1, type = "cor", data = current)
for (i in 1:3) {
  cat("**", names(ei_df[i]), "**", sep = "")
  print(knitr::kable(ei_df[[i]]))
}
```










## 11-13 vs 7-10

### Global Strength


```{r, echo=FALSE}
gs_diffs <- get_gs_diffs(net_current, net_prior2, type = "cor", data = current)
knitr::kable(gs_diffs)
```

```{r}
obs <- gs_diffs["GS Diff", "Post.mean"]

ppc <- ggm_compare_ppc(current,
                       prior2,
                       FUN = f_gs_cor,
                       custom_obs = obs,
                       iter = 10000,
                       progress = FALSE)

ppc

plot(ppc)$plot_custom +
  theme_minimal() +
  guides(fill = FALSE) +
  ylab("")
```

### Edge-wise

```{r, echo=FALSE}
knitr::kable(get_zero_order_diffs(net_current, net_prior2, data = current))

plot_edges_diff(net_current, net_prior2, data = current) +
  coord_flip() +
  geom_hline(yintercept = c(-0.1, 0.1), col = "red", linetype = "dashed") +
  theme_minimal()
```

### Expected Influence

```{r, echo=FALSE, results="asis"}
ei_df <- get_ei_diffs(net_current, net_prior2, type = "cor", data = current)
for (i in 1:3) {
  cat("**", names(ei_df[i]), "**", sep = "")
  print(knitr::kable(ei_df[[i]]))
}
```









## 14-17 vs 7-10


### Global Strength


```{r, echo=FALSE}
d4_ef <- make_groups(adhd, grp = 4, vars = ef_vars)
current <- d4_ef$current_age

net_14_to_17 <- BGGM:::pcor_to_cor(estimate(current, progress = FALSE))
net_current <- net_14_to_17
net_prior1 <- net_7_to_10
net_prior2 <- net_11_to_13
```

```{r, echo = FALSE}
gs_diffs <- get_gs_diffs(net_current, net_prior1, type = "cor", data = current)
knitr::kable(gs_diffs)
```

```{r}
obs <- gs_diffs["GS Diff", "Post.mean"]

ppc <- ggm_compare_ppc(current,
                       prior1,
                       FUN = f_gs_cor,
                       custom_obs = obs,
                       iter = 10000,
                       progress = FALSE)

ppc

plot(ppc)$plot_custom +
  theme_minimal() +
  guides(fill = FALSE) +
  ylab("")
```

### Edge-wise

```{r, echo=FALSE}
knitr::kable(get_zero_order_diffs(net_current, net_prior1, data = current))

plot_edges_diff(net_current, net_prior1, data = current) +
  coord_flip() +
  geom_hline(yintercept = c(-0.1, 0.1), col = "red", linetype = "dashed") +
  theme_minimal()
```

### Expected Influence

```{r, echo=FALSE, results="asis"}
ei_df <- get_ei_diffs(net_current, net_prior1, type = "cor", data = current)
for (i in 1:3) {
  cat("**", names(ei_df[i]), "**", sep = "")
  print(knitr::kable(ei_df[[i]]))
}
```








## 14-17 vs 11-13

### Global Strength


```{r, echo=FALSE}
gs_diffs <- get_gs_diffs(net_current, net_prior2, type = "cor", data = current)
knitr::kable(gs_diffs)
```

```{r}
obs <- gs_diffs["GS Diff", "Post.mean"]

ppc <- ggm_compare_ppc(current,
                       prior2,
                       FUN = f_gs_cor,
                       custom_obs = obs,
                       iter = 10000,
                       progress = FALSE)

ppc

plot(ppc)$plot_custom +
  theme_minimal() +
  guides(fill = FALSE) +
  ylab("")
```

### Edge-wise

```{r, echo=FALSE}
knitr::kable(get_zero_order_diffs(net_current, net_prior2, data = current))

plot_edges_diff(net_current, net_prior2, data = current)  +
  coord_flip() +
  geom_hline(yintercept = c(-0.1, 0.1), col = "red", linetype = "dashed") +
  theme_minimal()
```

### Expected Influence

```{r, echo=FALSE, results="asis"}
ei_df <- get_ei_diffs(net_current, net_prior2, type = "cor", data = current)
for (i in 1:3) {
  cat("**", names(ei_df[i]), "**", sep = "")
  print(knitr::kable(ei_df[[i]]))
}
```









## 18-39 vs 11-13

### Global Strength


```{r, echo=FALSE}
d5_ef <- make_groups(adhd, grp = 5, vars = ef_vars)
current <- d5_ef$current_age

net_18_to_39 <- BGGM:::pcor_to_cor(estimate(current, progress = FALSE))
net_current <- net_18_to_39
net_prior1 <- net_11_to_13
net_prior2 <- net_14_to_17
```

```{r, echo = FALSE}
gs_diffs <- get_gs_diffs(net_current, net_prior1, type = "cor", data = current)
knitr::kable(gs_diffs)
```

```{r}
obs <- gs_diffs["GS Diff", "Post.mean"]

ppc <- ggm_compare_ppc(current,
                       prior1,
                       FUN = f_gs_cor,
                       custom_obs = obs,
                       iter = 10000,
                       progress = FALSE)

ppc

plot(ppc)$plot_custom +
  theme_minimal() +
  guides(fill = FALSE) +
  ylab("")
```

### Edge-wise

```{r, echo=FALSE}
knitr::kable(get_zero_order_diffs(net_current, net_prior1, data = current))

plot_edges_diff(net_current, net_prior1, data = current)+
  coord_flip() +
  geom_hline(yintercept = c(-0.1, 0.1), col = "red", linetype = "dashed") +
  theme_minimal()
```

### Expected Influence

```{r, echo=FALSE, results="asis"}
ei_df <- get_ei_diffs(net_current, net_prior1, type = "cor", data = current)
for (i in 1:3) {
  cat("**", names(ei_df[i]), "**", sep = "")
  print(knitr::kable(ei_df[[i]]))
}
```









## 18-39 vs 14-17

### Global Strength

```{r, echo=FALSE}
gs_diffs <- get_gs_diffs(net_current, net_prior2, type = "cor", data = current)
knitr::kable(gs_diffs)
```

```{r}
obs <- gs_diffs["GS Diff", "Post.mean"]

ppc <- ggm_compare_ppc(current,
                       prior2,
                       FUN = f_gs_cor,
                       custom_obs = obs,
                       iter = 10000,
                       progress = FALSE)

ppc

plot(ppc)$plot_custom +
  theme_minimal() +
  guides(fill = FALSE) +
  ylab("")
```

### Edge-wise

```{r, echo=FALSE}
knitr::kable(get_zero_order_diffs(net_current, net_prior2, data = current))

plot_edges_diff(net_current, net_prior2, data = current) +
  coord_flip() +
  geom_hline(yintercept = c(-0.1, 0.1), col = "red", linetype = "dashed") +
  theme_minimal()
```

### Expected Influence

```{r, echo=FALSE, results="asis"}
ei_df <- get_ei_diffs(net_current, net_prior2, type = "cor", data = current)
for (i in 1:3) {
  cat("**", names(ei_df[i]), "**", sep = "")
  print(knitr::kable(ei_df[[i]]))
}
```









## 40-64 vs 14-17

### Global Strength


```{r, echo=FALSE}
d6_ef <- make_groups(adhd, grp = 6, vars = ef_vars)
current <- d6_ef$current_age

net_40_to_64 <- BGGM:::pcor_to_cor(estimate(current, progress = FALSE))
net_current <- net_40_to_64
net_prior1 <- net_14_to_17
net_prior2 <- net_18_to_39
```

```{r, echo = FALSE}
gs_diffs <- get_gs_diffs(net_current, net_prior1, type = "cor", data = current)
knitr::kable(gs_diffs)
```

```{r}
obs <- gs_diffs["GS Diff", "Post.mean"]

ppc <- ggm_compare_ppc(current,
                       prior1,
                       FUN = f_gs_cor,
                       custom_obs = obs,
                       iter = 10000,
                       progress = FALSE)

ppc

plot(ppc)$plot_custom +
  theme_minimal() +
  guides(fill = FALSE) +
  ylab("")
```

### Edge-wise

```{r, echo=FALSE}
knitr::kable(get_zero_order_diffs(net_current, net_prior1, data = current))

plot_edges_diff(net_current, net_prior1, data = current) +
  coord_flip() +
  geom_hline(yintercept = c(-0.1, 0.1), col = "red", linetype = "dashed") +
  theme_minimal()
```

### Expected Influence

```{r, echo=FALSE, results="asis"}
ei_df <- get_ei_diffs(net_current, net_prior1, type = "cor", data = current)
for (i in 1:3) {
  cat("**", names(ei_df[i]), "**", sep = "")
  print(knitr::kable(ei_df[[i]]))
}
```










## 40-64 vs 18-39


### Global Strength
```{r, echo=FALSE}
gs_diffs <- get_gs_diffs(net_current, net_prior2, type = "cor", data = current)
knitr::kable(gs_diffs)
```

```{r}
obs <- gs_diffs["GS Diff", "Post.mean"]

ppc <- ggm_compare_ppc(current,
                       prior2,
                       FUN = f_gs_cor,
                       custom_obs = obs,
                       iter = 10000,
                       progress = FALSE)

ppc

plot(ppc)$plot_custom +
  theme_minimal() +
  guides(fill = FALSE) +
  ylab("")
```

### Edge-wise

```{r, echo=FALSE}
knitr::kable(get_zero_order_diffs(net_current, net_prior2, data = current))

plot_edges_diff(net_current, net_prior2, data = current) +
  coord_flip() +
  geom_hline(yintercept = c(-0.1, 0.1), col = "red", linetype = "dashed") +
  theme_minimal()
```

### Expected Influence

```{r, echo=FALSE, results="asis"}
ei_df <- get_ei_diffs(net_current, net_prior2, type = "cor", data = current)
for (i in 1:3) {
  cat("**", names(ei_df[i]), "**", sep = "")
  print(knitr::kable(ei_df[[i]]))
}
```










## 65-85 vs 18-39

### Global Strength


```{r, echo=FALSE}
d7_ef <- make_groups(adhd, grp = 7, vars = ef_vars)
current <- d7_ef$current_age

net_65_to_85 <- BGGM::pcor_to_cor(estimate(current, progress = FALSE))
net_current <- net_65_to_85
net_prior1 <- net_18_to_39
net_prior2 <- net_40_to_64
```

```{r, echo = FALSE}
gs_diffs <- get_gs_diffs(net_current, net_prior1, type = "cor", data = current)
knitr::kable(gs_diffs)
```

```{r}
obs <- gs_diffs["GS Diff", "Post.mean"]

ppc <- ggm_compare_ppc(current,
                       prior1,
                       FUN = f_gs_cor,
                       custom_obs = obs,
                       iter = 10000,
                       progress = FALSE)

ppc

plot(ppc)$plot_custom +
  theme_minimal() +
  guides(fill = FALSE) +
  ylab("")
```

### Edge-wise

```{r, echo=FALSE}
knitr::kable(get_zero_order_diffs(net_current, net_prior1, data = current))

plot_edges_diff(net_current, net_prior1, data = current) +
  coord_flip() +
  geom_hline(yintercept = c(-0.1, 0.1), col = "red", linetype = "dashed") +
  theme_minimal()
```

### Expected Influence

```{r, echo=FALSE, results="asis"}
ei_df <- get_ei_diffs(net_current, net_prior1, type = "cor", data = current)
for (i in 1:3) {
  cat("**", names(ei_df[i]), "**", sep = "")
  print(knitr::kable(ei_df[[i]]))
}
```










## 65-85 vs 40-64

### Global Strength


```{r, echo=FALSE}
gs_diffs <- get_gs_diffs(net_current, net_prior2, type = "cor", data = current)
knitr::kable(gs_diffs)
```

```{r}
obs <- gs_diffs["GS Diff", "Post.mean"]

ppc <- ggm_compare_ppc(current,
                       prior2,
                       FUN = f_gs_cor,
                       custom_obs = obs,
                       iter = 10000,
                       progress = FALSE)

ppc

plot(ppc)$plot_custom +
  theme_minimal() +
  guides(fill = FALSE) +
  ylab("")
```

### Edge-wise

```{r, echo=FALSE}
knitr::kable(get_zero_order_diffs(net_current, net_prior2, data = current))

plot_edges_diff(net_current, net_prior2, data = current) +
  coord_flip() +
  geom_hline(yintercept = c(-0.1, 0.1), col = "red", linetype = "dashed") +
  theme_minimal()
  ```

### Expected Influence

```{r, echo=FALSE, results="asis"}
ei_df <- get_ei_diffs(net_current, net_prior2, type = "cor", data = current)
for (i in 1:3) {
  cat("**", names(ei_df[i]), "**", sep = "")
  print(knitr::kable(ei_df[[i]]))
}
```




# DESCRIPTIVES


## ALL



```{r}
ef_all <- adhd[, ef_vars]

net_all <- BGGM::pcor_to_cor(estimate(ef_all, progress = FALSE))

desc_all <-  get_zero_order_diffs(net_all, net_all, data = ef_all, summary = TRUE)

knitr::kable(desc_all[[1]])
```


## 3 to 6


```{r}
desc_3_to_6 <- get_zero_order_diffs(net_3_to_6, net_3_to_6, data = d2_ef$prior_age2, summary = TRUE)

knitr::kable(desc_3_to_6[[1]])
```

## 7 to 10


```{r}
desc_7_to_10 <-  get_zero_order_diffs(net_7_to_10, net_7_to_10, data = d2_ef$current_age, summary = TRUE)


knitr::kable(desc_7_to_10[[1]])
```

## 11 to 13


```{r}
desc_11_to_13 <- get_zero_order_diffs(net_11_to_13, net_11_to_13, data = d3_ef$current_age, summary = TRUE)
knitr::kable(desc_11_to_13[[1]])
```

## 14 to 17


```{r}
desc_14_to_17  <- get_zero_order_diffs(net_14_to_17, net_14_to_17, data = d4_ef$current_age, summary = TRUE)

knitr::kable(desc_14_to_17[[1]])
```

## 18 to 39


```{r}
desc_18_to_39  <- get_zero_order_diffs(net_18_to_39, net_18_to_39, data = d5_ef$current_age, summary = TRUE)

knitr::kable(desc_18_to_39[[1]])
```


## 40 to 64


```{r}
desc_40_to_64 <- get_zero_order_diffs(net_40_to_64, net_40_to_64, data = d6_ef$current_age, summary = TRUE)

knitr::kable(desc_40_to_64[[1]])
```

## 65 to 85


```{r}
desc_65_to_85 <- get_zero_order_diffs(net_65_to_85, net_65_to_85, data = d7_ef$current_age, summary = TRUE)

knitr::kable(desc_65_to_85[[1]])
```









































# PLOTS

```{r message=FALSE, warning=FALSE}
source("make_net_plot_cor.R")


# Font
windowsFonts(Times = windowsFont("Times New Roman"))
```


## 3 - 6


```{r}
make_net_plot_cor(
  net = net_3_to_6,
  data = d2_ef$prior_age2,
  node_labels = c("DCCS", "LstSrt", "Flanker")
) +
  ggtitle("3 to 6 years") -> plot_3_6
```

## 7 - 10


```{r}
make_net_plot_cor(
  net = net_7_to_10,
  data = d2_ef$current_age,
  node_labels = c("DCCS", "LstSrt", "Flanker")
) +
  ggtitle("7 to 10 years") -> plot_7_10
```


## 11 to 13


```{r}
make_net_plot_cor(
  net = net_11_to_13,
  data = d3_ef$current_age,
  node_labels = c("DCCS", "LstSrt", "Flanker")
) +
  ggtitle("11 to 13 years") -> plot_11_13
```


## 14 to 17


```{r}
make_net_plot_cor(
  net = net_14_to_17,
  data = d4_ef$current_age,
  node_labels = c("DCCS", "LstSrt", "Flanker")
) +
  ggtitle("14 to 17 years") -> plot_14_17
```


## 18 to 39


```{r}
make_net_plot_cor(
  net = net_18_to_39,
  data = d5_ef$current_age,
  node_labels = c("DCCS", "LstSrt", "Flanker")
) +
  ggtitle("18 to 39 years") -> plot_18_39
```

## 40 to 64


```{r}
make_net_plot_cor(
  net = net_40_to_64,
  data = d6_ef$current_age,
  node_labels = c("DCCS", "LstSrt", "Flanker")
) +
  ggtitle("40 to 64 years") -> plot_40_to_64
```

## 65 to 85


```{r}
make_net_plot_cor(
  net = net_65_to_85,
  data = d7_ef$current_age,
  node_labels = c("DCCS", "LstSrt", "Flanker")) +
  ggtitle("65 to 85 years") -> plot_65_to_85
```


## Concatenate plots

```{r include = FALSE, eval = T}

plot_grid_ages <-
  plot_grid(
    plot_3_6,
    NULL,
    plot_7_10,
    NULL,
    plot_11_13,
    NULL,
    plot_14_17,
    NULL,
    plot_18_39,
    NULL,
    plot_40_to_64,
    NULL,
    plot_65_to_85,
    NULL,
    nrow = 14,
    rel_heights = rep(c(100, 20), 7),
    axis = "trbl"
)


# plot_grid_ages
# 
ggsave(
  "network_plot_zero_order.png",
  plot_grid_ages,
  dpi = 500,
  width = 6.5,
  height = 12,
  units = "in",
  bg = "white",
  scale = 2
  )
```

