---
title: "Between-person network model"
author: "Marwin Carmo"
date: ""
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,  message=FALSE, include=TRUE, warning = FALSE, fig.width = 8, fig.height = 5)

library(BGGM)
library(dplyr)
library(ggplot2)
library(networktools)
library(patchwork)
library(kableExtra)
```

```{r data, include=FALSE}
raw_data <- haven::read_sav("../data/PCSNetworkModelAnalysis.sav") |> janitor::clean_names()
data_dictionary <- readxl::read_excel("../Data Dictionary.xlsx")

symptoms <- names(raw_data)[19:length(names(raw_data))]
symptoms_names <- data_dictionary[data_dictionary$`Variable Name` %in% symptoms,]$`Variable Label`
```

## Averaged between-person network

We estimate the Gaussian graphical model with all the symptoms averaged across all time points, controlling for the effect of sex, and including the whole sample.

```{r }
# Averaging data across all timepoints

avg_data <- raw_data |> 
  # dplyr::select(-c(time_completed, gender, race,psych, conctime, loc, pta, 
  #                  ptanum, agefirstinj, conmech, locnum
  #                  )
  #               ) |> 
  dplyr::filter(survey_day != 0) |> 
  dplyr::with_groups(subject_id,
                     dplyr::summarise,
                     dplyr::across(age:vis,
                                   ~mean(.x)
                                   )
                     )  
  

```

```{r }

# selecting only the relevant variables
dat <- avg_data |> 
  dplyr::select(sex, head:vis)

# estimate the network controlling for sex
fit_between <- estimate(dat, type="continuous",
                        formula = ~ sex
                        )
```

```{r include=TRUE}
summary(fit_between)$dat_results |> 
  dplyr::arrange(desc(abs(Post.mean))) |> 
  kbl() |> 
  kable_paper() |> 
  scroll_box(height = "300px")
```

## Network model

```{r}
selected_between <- BGGM::select(fit_between)
```

```{r}
plot(selected_between, edge_magnify = 5, node_size = 13)$plt
```

### Bridge strength

```{r}

bridgestrenght <- function(x, ...){
  bridge(x, ...)$`Bridge Strength`
}

ei <- function(x,...){
     expectedInf(x,...)$step1
}
```

```{r eval=FALSE}
strength_between <- roll_your_own(fit_between,
                          FUN = bridgestrenght,
                          select = TRUE,
                          communities = symptoms,
                          progress = TRUE)
saveRDS(strength_between, "../data/strength_between.rds")
```

```{r}
strength_between <- readRDS("../data/strength_between.rds")
dimnames(strength_between$results) <- list(symptoms_names)

plot(strength_between) +
  theme_minimal()
```

### Expected influence

```{r}
ei_between <- roll_your_own(fit_between,
                          FUN = ei,
                          progress = FALSE)
```

```{r}
dimnames(ei_between$results) <- list(symptoms_names)

plot(ei_between) +
  theme_minimal()
```


## Network comparison (concussion vs. no concussion)

```{r}
concussion <- avg_data[avg_data$concussion == 1, ]

control <- avg_data[avg_data$concussion == 0, ]
```

```{r}
fit_concussion <- estimate(concussion[,symptoms], type="continuous")

fit_control <- estimate(control[,symptoms], type="continuous")
```
```{r}
selected_concussion <- BGGM::select(fit_concussion)
selected_control <- BGGM::select(fit_control)

```

### View differences network

```{r warning=FALSE}
fit_compare <- ggm_compare_estimate(concussion[,symptoms], control[,symptoms])

sum_compare <- summary(fit_compare)

sel_compare <- BGGM::select(fit_compare)
```

```{r}
plot(sel_compare, edge_magnify = 5, node_size = 13)[[1]] + 
  labs(title = "Concussion - Control")
```

```{r include=TRUE}
summary(fit_compare)$dat_results[[1]] |> 
  dplyr::arrange(desc(abs(Post.mean))) |> 
  kbl() |> 
  kable_paper() |> 
  scroll_box(height = "300px")
```

```{r, fig.width = 8, fig.height = 5}
pconc <- plot(selected_concussion, edge_magnify = 5, node_size = 13)$plt + labs(title = "Concussion")
pctrl <- plot(selected_control, edge_magnify = 5, node_size = 13)$plt + labs(title = "Control")

pconc + pctrl

```

## Edge weights - Concussion

```{r include=TRUE}
summary(fit_concussion)$dat_results |> 
  dplyr::arrange(desc(abs(Post.mean))) |> 
  kbl() |> 
  kable_paper() |> 
  scroll_box(height = "300px")
```

## Bridge strenght - Concussion

```{r eval=FALSE}
strength_concussion <- roll_your_own(fit_concussion,
                          FUN = bridgestrenght,
                          select = TRUE,
                          communities = symptoms,
                          progress = TRUE)
saveRDS(strength_concussion, "../out/strength_concussion.rds")
```

```{r}
strength_concussion <- readRDS("../out/strength_concussion.rds")

dimnames(strength_concussion$results) <- list(symptoms_names)

plot(strength_concussion) +
  theme_minimal()
```
## Edge weights - Control

```{r include=TRUE}
summary(fit_control)$dat_results |> 
  dplyr::arrange(desc(abs(Post.mean))) |> 
  kbl() |> 
  kable_paper() |> 
  scroll_box(height = "300px")
```

## Bridge strenght - Control

```{r eval=FALSE}
strength_control <- roll_your_own(fit_control,
                          FUN = bridgestrenght,
                          select = TRUE,
                          communities = symptoms,
                          progress = TRUE)
saveRDS(strength_control, "../out/strength_control.rds")
```

```{r}
strength_control <- readRDS("../out/strength_control.rds")

dimnames(strength_control$results) <- list(symptoms_names)

plot(strength_control) +
  theme_minimal()
```