---
title: "Between neworks: survey time"
author: "Marwin Carmo"
date: ""
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  message=FALSE, warning = FALSE, fig.width = 12, fig.height = 12)

library(BGGM)
library(dplyr)
library(ggplot2)
#library(qgraph)
```


```{r data, include=FALSE}
raw_data <- haven::read_sav("../data/PCSNetworkModelAnalysis.sav") |> janitor::clean_names()

symptoms <- names(raw_data)[19:length(names(raw_data))]
```


We want to estimate three different networks averaged across all days for each survey time to check if there are any differences between them.

## Aggregate data by subject and survey time

```{r}
agg_data_days <- raw_data |> 
  dplyr::with_groups(c(subject_id, survey_time),
                     dplyr::summarise,
                     dplyr::across(
                       head:vis, ~mean(.x)
                                   )
                     )
```

## Create a different data set for each time of the day

```{r}
morning <- agg_data_days[agg_data_days["survey_time"] == 10, ]

noon <- agg_data_days[agg_data_days["survey_time"] == 3, ]

evening <- agg_data_days[agg_data_days["survey_time"] == 8, ]
```

### Estimate the network models

```{r}
fit_morning <- estimate(Y = morning[, -c(1,2)],
                        type = "continuous") 

fit_noon <- estimate(Y = noon[, -c(1,2)],
                        type = "continuous") 

fit_evening <- estimate(Y = evening[, -c(1,2)],
                        type = "continuous") 
```

### View morning network model summary

```{r}
summary(fit_morning)
```

### View morning partial correlation matrix

```{r}
pcor_mat(fit_morning)
```

### View morning network model plots

```{r}
selected_morning <- BGGM::select(fit_morning)
```

```{r}
plot(selected_morning, edge_magnify = 5, node_size = 13)
```


## Comparing networks

```{r warning=FALSE}
fit_compare <- ggm_compare_estimate(morning[, -c(1,2)], noon[, -c(1,2)], evening[, -c(1,2)])

sum_compare <- summary(fit_compare)

sel_compare <- BGGM::select(fit_compare)

plot(sel_compare, edge_magnify = 5, node_size = 13)
```
```{r}
sel_compare
```

