---
title: "Between neworks: survey time"
author: "Marwin Carmo"
date: ""
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,  message=FALSE, warning = FALSE, fig.width = 8, fig.height = 8)

library(BGGM)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(networktools)
```


```{r data, include=FALSE}
raw_data <- haven::read_sav("../data/PCSNetworkModelAnalysis.sav") |> janitor::clean_names()
data_dictionary <- readxl::read_excel("../Data Dictionary.xlsx")

symptoms <- names(raw_data)[19:length(names(raw_data))]
symptoms_names <- data_dictionary[data_dictionary$`Variable Name` %in% symptoms,]$`Variable Label`

bridgestrenght <- function(x, ...){
  bridge(x, ...)$`Bridge Strength`
}
```


We want to estimate three different networks averaged across all days for each survey time to check if there are any differences between them.

## Aggregate data by subject and survey time

```{r}
agg_data_days <- raw_data |> 
  dplyr::with_groups(c(subject_id, survey_time),
                     dplyr::summarise,
                     dplyr::across(
                       head:vis, ~mean(.x)
                                   )
                     )
```

## Create a different data set for each time of the day

```{r}
morning <- agg_data_days[agg_data_days["survey_time"] == 10, ]

noon <- agg_data_days[agg_data_days["survey_time"] == 3, ]

evening <- agg_data_days[agg_data_days["survey_time"] == 8, ]
```

## Estimate the network models

```{r}
fit_morning <- estimate(Y = morning[, -c(1,2)],
                        type = "continuous") 

fit_noon <- estimate(Y = noon[, -c(1,2)],
                        type = "continuous") 

fit_evening <- estimate(Y = evening[, -c(1,2)],
                        type = "continuous") 
```

### View 10AM network model summary

```{r}
summary(fit_morning)$dat_results |> 
  kbl() |> 
  kable_paper() |> 
  scroll_box(height = "300px")
```

### View 10AM partial correlation matrix

```{r}
pcor_mat(fit_morning)
```

### View 10AM network model plots

```{r}
selected_morning <- BGGM::select(fit_morning)
```

```{r, fig.width = 8, fig.height = 8}
plot(selected_morning, edge_magnify = 5, node_size = 13)$plt
```

### Bridge strength 10AM

```{r eval=FALSE}
strength_morning <- roll_your_own(fit_morning,
                          FUN = bridgestrenght,
                          select = TRUE,
                          communities = symptoms,
                          progress = TRUE)
saveRDS(strength_morning, "../out/strength_morning.rds")
```

```{r echo=FALSE}
strength_morning <- readRDS("../out/strength_morning.rds")
dimnames(strength_morning$results) <- list(symptoms_names)

plot(strength_morning) +
  theme_minimal()
```

### View 3PM network model summary

```{r}
summary(fit_noon)$dat_results |> 
  kbl() |> 
  kable_paper() |> 
  scroll_box(height = "300px")
```

### View 3PM partial correlation matrix

```{r}
pcor_mat(fit_noon)
```

### View 3PM network model plots

```{r}
selected_noon <- BGGM::select(fit_noon)
```

```{r, fig.width = 8, fig.height = 8}
plot(selected_noon, edge_magnify = 5, node_size = 13)$plt
```

### Bridge strength 3PM network

```{r eval=FALSE}
strength_noon <- roll_your_own(fit_noon,
                          FUN = bridgestrenght,
                          select = TRUE,
                          communities = symptoms,
                          progress = TRUE)
saveRDS(strength_noon, "../out/strength_noon.rds")
```

```{r echo=FALSE}
strength_noon <- readRDS("../out/strength_noon.rds")
dimnames(strength_noon$results) <- list(symptoms_names)

plot(strength_noon) +
  theme_minimal()
```

### View 8PM network model summary

```{r}
summary(fit_evening)$dat_results |> 
  kbl() |> 
  kable_paper() |> 
  scroll_box(height = "300px")
```

### View 8PM partial correlation matrix

```{r}
pcor_mat(fit_evening)
```

### View 8PM network model plots

```{r}
selected_evening <- BGGM::select(fit_evening)
```

```{r, fig.width = 8, fig.height = 8}
plot(selected_evening, edge_magnify = 5, node_size = 13)$plt
```

### Bridge strength 8PM network

```{r eval=FALSE}
strength_evening <- roll_your_own(fit_evening,
                          FUN = bridgestrenght,
                          select = TRUE,
                          communities = symptoms,
                          progress = TRUE)
saveRDS(strength_evening, "../out/strength_evening.rds")
```

```{r echo=FALSE}
strength_evening <- readRDS("../out/strength_evening.rds")
dimnames(strength_evening$results) <- list(symptoms_names)

plot(strength_evening) +
  theme_minimal()
```

## Comparing networks

```{r warning=FALSE}
fit_compare <- ggm_compare_estimate(morning[, -c(1,2)], noon[, -c(1,2)], evening[, -c(1,2)])

sum_compare <- summary(fit_compare)

sel_compare <- BGGM::select(fit_compare)

```

```{r}
plot(sel_compare, edge_magnify = 5, node_size = 13)[[1]] + 
  labs(title = "10AM - 3PM")
```
```{r}
plot(sel_compare, edge_magnify = 5, node_size = 13)[[2]] + 
  labs(title = "10AM - 8PM")
```
```{r}
plot(sel_compare, edge_magnify = 5, node_size = 13)[[3]] + 
  labs(title = "3PM - 8PM")
```