---
title: "Untitled"
author: "Your name"
date: "2025-01-31"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(flextable)
library(officer)
library(dplyr)
```


```{r}
raw_data <- haven::read_sav("../data/PCSNetworkModelAnalysis.sav") |> 
  janitor::clean_names()
# data_dictionary <- readxl::read_excel("../Data Dictionary.xlsx")
symptoms <- names(raw_data)[19:length(names(raw_data))]
symptoms_names <- data_dictionary[data_dictionary$`Variable Name` %in% symptoms,]$`Variable Label`
long_data <- raw_data |> 
  tidyr::pivot_longer(
    cols = dplyr::all_of(symptoms),
    names_to = "symptom",
    values_to = "score"
  )

## Transform data to long 
# person centering
c_data <- long_data |> 
  dplyr::with_groups(
    symptom,
    dplyr::mutate,
    z_score = as.vector(scale(score)) # scale the symptoms across all individuals and all time points
  ) |> 
  dplyr::with_groups(
    c(symptom, subject_id),
    dplyr::mutate,
    mean_score = mean(z_score, na.rm = TRUE) # mean person score in standardized units
  ) |> 
  dplyr::with_groups(
    symptom,
    dplyr::mutate,
    pc_score = z_score - mean_score # person centered score is the person deviation 
    # at each measurement from their own average 
  )
# revert back to wide
pc_data <- c_data[,c("subject_id", "pc_score", "symptom")] |> 
  tidyr::pivot_wider(id_cols = subject_id,
                     names_from = symptom,
                     values_from = pc_score) |>
  tidyr::unnest()

converged <- as.numeric(gsub("[^0-9]", "", list.files("../out/results_noise")))

failed <- unique(raw_data$subject_id)[!(unique(raw_data$subject_id) %in% converged)]

## First lets rule out how many had less data than nodes

n_nodes <- ncol(pc_data) -1 #excluding subject_id

low_n <- pc_data |> 
  dplyr::filter(subject_id %in% failed
  ) |> 
  dplyr::with_groups(subject_id, dplyr::summarise, n = dplyr::n()) |> 
  dplyr::filter(n < n_nodes) |> 
  dplyr::pull(subject_id)
# There were 58/113

## Now looking at the other cases

multicol <- pc_data |> 
  dplyr::filter(subject_id %in% failed,
                !(subject_id %in% low_n)) 
```

# 1. Those who didn't complete enough responses (n=58)
## i. What are the subsample sizes for the control and concussion groups?

```{r}
raw_data |> 
  dplyr::filter(subject_id %in% low_n) |> 
  dplyr::with_groups(subject_id,
                     dplyr::slice_head) |> 
  dplyr::count(concussion) |> 
  dplyr::mutate(pct = n/sum(n)) |> 
  flextable() |> 
  set_table_properties(width = 1, layout = "autofit")
```

## ii. For this group overall, what was the Mean, Standard Deviation, and range of # of responses completed

```{r}
raw_data |> 
  dplyr::filter(subject_id %in% low_n) |> 
  dplyr::with_groups(subject_id,
                     dplyr::summarise, n = dplyr::n()) |> 
  dplyr::summarise(dplyr::across(n, .fns =
                     list(min = min,
                          median = median,
                          mean = mean,
                          stdev = sd,
                          q25 = ~quantile(., 0.25),
                          q75 = ~quantile(., 0.75),
                          max = max))) |> 
  tidyr::pivot_longer(dplyr::everything()) |> 
  dplyr::mutate(name = stringr::str_extract(name, "[^n_].+")) |> 
  flextable() |> 
  set_table_properties( layout = "autofit")
  
  # dplyr::pull(n) |> 
  # psych::describe()
```

## 2. Those with multicollinearity (n=55)
### i. What are the subsample sizes for the control and concussion groups?

```{r}
raw_data |> 
  dplyr::filter(subject_id %in% unique(multicol$subject_id)) |> 
  dplyr::with_groups(subject_id,
                     dplyr::slice_head) |> 
  dplyr::count(concussion) |> 
  dplyr::mutate(pct = n/sum(n)) |> 
  flextable() |> 
  set_table_properties(width = 1, layout = "autofit")
```

### ii. Table summarizing the most common pairs of highly correlated symptoms and the magnitude of correlations

The VAR networks of 55 participants could not be estimated due to multicollinearity between symptoms. 

```{r}
# add random noise
set.seed(999)
for (j in 2:ncol(pc_data)) {
  for (i in 1:nrow(pc_data)){
    noise <- rnorm(1, 0, 0.001)
    pc_data[i, j] <- pc_data[i, j] + noise 
  }
}


# Step 1: Compute personal correlation matrices for each subject
personal_cor_matrices <- pc_data |> 
  dplyr::filter(subject_id %in% 
                  c(unique(multicol$subject_id))) |> 
  dplyr::group_by(subject_id) |> 
  tidyr::nest() |> 
  dplyr::mutate(
    cor_matrix = purrr::map(
      data,
      ~cor(.[, -1], use = "complete.obs")
    )
  )

# Step 2: Average correlations across subjects

# Extract all correlation matrices into a list
cor_list <- personal_cor_matrices$cor_matrix

# Initialize a matrix to store the sum of correlations
sum_cor_matrix <- matrix(0, nrow = ncol(cor_list[[1]]), ncol = ncol(cor_list[[1]]))
colnames(sum_cor_matrix) <- colnames(cor_list[[1]])
rownames(sum_cor_matrix) <- colnames(cor_list[[1]])

# Sum all correlation matrices
for (cor_matrix in cor_list) {
  sum_cor_matrix <- sum_cor_matrix + cor_matrix
}

# Compute the average correlation matrix
average_cor_matrix <- sum_cor_matrix / length(cor_list)

# Step 3: Count how frequently each pair surpasses a threshold
threshold <- 0.7  # Set your correlation threshold here

# Initialize a matrix to store the count of high correlations
high_cor_count_matrix <- matrix(0, nrow = ncol(cor_list[[1]]), ncol = ncol(cor_list[[1]]))
colnames(high_cor_count_matrix) <- colnames(cor_list[[1]])
rownames(high_cor_count_matrix) <- colnames(cor_list[[1]])

# Count how often each pair exceeds the threshold
for (cor_matrix in cor_list) {
  # Create a logical matrix indicating whether correlations exceed the threshold
  # Use `is.na()` to ignore NA values
  exceeds_threshold <- cor_matrix > threshold
  exceeds_threshold[is.na(exceeds_threshold)] <- FALSE  # Treat NA as FALSE
  
  # Add to the count matrix
  high_cor_count_matrix <- high_cor_count_matrix + exceeds_threshold
}

# Convert the count matrix to a data frame for easier interpretation
high_cor_count_df <- as.data.frame(high_cor_count_matrix) |> 
  tibble::rownames_to_column(var = "Symptom1") |> 
  tidyr::pivot_longer(-Symptom1, names_to = "Symptom2", values_to = "Frequency") |> 
  dplyr::filter(Symptom1 < Symptom2) |> # Avoid duplicate pairs (e.g., A-B and B-A)
  dplyr::arrange(dplyr::desc(Frequency))
```

```{r}
high_cor_count_df |> 
  flextable() |> 
  set_table_properties(width = 1, layout = "autofit")
```

