---
title: "Within-person network model"
author: "Marwin Carmo"
date: ""
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

In the within-person network model we investigate the associations between the symptoms at each measurement occasion, after subtracting out the person-average from each measurement. That is, first we scaled the symptoms across all the individuals and all measurement occasions. Then, calculated the mean person score in standardized units. Finally, subtracted each standardized score from their own average to obtain a person centered score. That way we can observe whether fluctuations around each participant's mean in one symptom are associated with fluctuations in this same participant's mean in another symptom. For example, we can examine if someone experiencing more than average vomiting at one measurement occasion would also experience more than average nausea at the same measurement occasion.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,  message=FALSE, warning = FALSE, fig.width = 8, fig.height = 8)

library(BGGM)
library(dplyr)
library(ggplot2)
library(networktools)
library(kableExtra)
library(qgraph)
library(network)
library(GGally)
```


```{r data, include=FALSE}
raw_data <- haven::read_sav("../data/PCSNetworkModelAnalysis.sav") |> janitor::clean_names()

data_dictionary <- readxl::read_excel("../Data Dictionary.xlsx")

symptoms <- names(raw_data)[19:length(names(raw_data))]
symptoms_names <- data_dictionary[data_dictionary$`Variable Name` %in% symptoms,]$`Variable Label`

getCentral <- function(x, cred = 0.95) {
  
  lb <- (1-cred) / 2
  ub <- 1 - lb
  
  mu <-  apply( x$results, 1, mean)
  p <- length(mu)
  scale <- apply( x$results, 1, sd)
  ci_lb <- apply( x$results, 1, quantile, lb)
  ci_ub <- apply( x$results, 1, quantile, ub)
  
  res<- data.frame(Node = symptoms_names,
                   Post.mean = round(mu, 3),
                   Post.sd = round(scale, 3),
                   Cred.lb = round(ci_lb, 3),
                   Cred.ub = round(ci_ub, 3))
  rownames(res) <- NULL
  res
}
```

```{r}
# wide to long

long_data <- raw_data |> 
  tidyr::pivot_longer(
    cols = dplyr::all_of(symptoms),
    names_to = "symptom",
    values_to = "score"
  )

# person centering
c_data <- long_data |> 
  dplyr::with_groups(
    symptom,
    dplyr::mutate,
    z_score = as.vector(scale(score)) # scale the symptoms across all individuals and all time points
  ) |> 
  dplyr::with_groups(
    c(symptom, subject_id),
    dplyr::mutate,
    mean_score = mean(z_score, na.rm = TRUE) # mean person score in standardized units
  ) |> 
  dplyr::with_groups(
    symptom,
    dplyr::mutate,
    pc_score = z_score - mean_score # person centered score is the person deviation 
                                    # at each measurement from their own average 
  )

# revert back to wide

pc_data <- c_data[,c("subject_id", "sex", "concussion", "pc_score", "symptom")] |> 
  tidyr::pivot_wider(id_cols = c(subject_id, sex, concussion),
                     names_from = symptom,
                     values_from = pc_score) |>
  tidyr::unnest()

```

<!-- Do post concussion symptom net differ between history of concussion history or not -->

<!-- control for sex -->

## Within-person network model - Entire sample

```{r}
fit_within <- BGGM::estimate(pc_data[, -c(1,3)], formula = ~ sex)
```
### Edge weights

```{r}
summary(fit_within)$dat_results |> 
  dplyr::arrange(desc(abs(Post.mean))) |> 
  kbl() |> 
  kable_paper() |> 
  scroll_box(height = "300px")
```

### Network plot

```{r}
sel_within <- BGGM::select(fit_within)
plot(sel_within, edge_magnify = 5, node_size = 13)$plt

```

### Bridge strength

```{r}
bridgestrenght <- function(x, ...){
  bridge(x, ...)$`Bridge Strength`
}
```

```{r eval=FALSE}
strength_within <- roll_your_own(fit_within,
                          FUN = bridgestrenght,
                          select = TRUE,
                          communities = symptoms,
                          progress = TRUE)

saveRDS(strength_within, "../out/strength_within.rds")
```

```{r}

strength_within <- readRDS("../out/strength_within.rds")
  
  
dimnames(strength_within$results) <- list(symptoms_names)

plot(strength_within) +
  theme_minimal()
```
```{r}
getCentral(strength_within) |> 
  kbl() |> 
  kable_paper()
```

## Within-person network model - Concussion

```{r}
fit_within_concussion <- BGGM::estimate(pc_data[pc_data$concussion == 1, -c(1,3)], formula = ~ sex)
```
### Edge weights

```{r}
summary(fit_within_concussion)$dat_results |> 
  dplyr::arrange(desc(abs(Post.mean))) |> 
  kbl() |> 
  kable_paper() |> 
  scroll_box(height = "300px")
```

### Network plot

```{r}
sel_within_concussion <- BGGM::select(fit_within_concussion)
plot(sel_within_concussion, edge_magnify = 5, node_size = 13)$plt

```

### Bridge strength

```{r}
bridgestrenght <- function(x, ...){
  bridge(x, ...)$`Bridge Strength`
}
```

```{r eval=FALSE}
strength_within_concussion <- roll_your_own(fit_within_concussion,
                          FUN = bridgestrenght,
                          select = TRUE,
                          communities = symptoms,
                          progress = TRUE)

saveRDS(strength_within_concussion, "../out/strength_within_concussion.rds")
```

```{r}

strength_within_concussion <- readRDS("../out/strength_within_concussion.rds")
  
  
dimnames(strength_within_concussion$results) <- list(symptoms_names)

plot(strength_within_concussion) +
  theme_minimal()
```
```{r}
getCentral(strength_within_concussion) |> 
  kbl() |> 
  kable_paper()
```

## Within-person network model - Control

```{r}
fit_within_control <- BGGM::estimate(pc_data[pc_data$concussion == 0, -c(1,3)], formula = ~ sex)
```

```{r}
summary(fit_within_control)$dat_results |> 
  dplyr::arrange(desc(abs(Post.mean))) |> 
  kbl() |> 
  kable_paper() |> 
  scroll_box(height = "300px")
```

### Network plot

```{r}
sel_within_control <- BGGM::select(fit_within_control)
plot(sel_within_control, edge_magnify = 5, node_size = 13)$plt

```

### Bridge strength

```{r}
bridgestrenght <- function(x, ...){
  bridge(x, ...)$`Bridge Strength`
}
```

```{r eval=FALSE}
strength_within_control <- roll_your_own(fit_within_control,
                          FUN = bridgestrenght,
                          select = TRUE,
                          communities = symptoms,
                          progress = TRUE)

saveRDS(strength_within_control, "../out/strength_within_control.rds")
```

```{r}

strength_within_control <- readRDS("../out/strength_within_control.rds")
  
  
dimnames(strength_within_control$results) <- list(symptoms_names)

plot(strength_within_control) +
  theme_minimal()
```

```{r}
getCentral(strength_within_control) |> 
  kbl() |> 
  kable_paper()
```

## Concussion vs. Control

```{r warning=FALSE}
fit_compare <- ggm_compare_estimate(pc_data[pc_data$concussion == 1, -c(1,3)], pc_data[pc_data$concussion == 0, -c(1,3)],
                                    formula = ~ sex)

res_compare <- summary(fit_compare)

sel_compare <- BGGM::select(fit_compare)
```

```{r, fig.width = 12, fig.height = 6}
plot(res_compare)[[1]] +
  labs(title = "Concussion - Control")
```

### Edge weights

```{r include=TRUE}
summary(fit_compare)$dat_results[[1]] |> 
  dplyr::arrange(desc(abs(Post.mean))) |> 
  kbl() |> 
  kable_paper() |> 
  scroll_box(height = "300px")
```

### Network plot

```{r}

palette = "Set3"
cn <- symptoms
x <- sel_compare
p <- ncol(x$pcor_adj[[1]])
diag(x$pcor_adj[[1]]) <- 0
net <- network::network(x$pcor_adj[[1]])

# edge weights
network::set.edge.value(x = net, attrname = "weights",
                          value = x$pcor_adj[[1]])
  
# edge weights absolute
network::set.edge.value(x = net, attrname = "abs_weights",
                          value = abs(x$pcor_adj[[1]]) * 5)
# edge colors
network::set.edge.attribute(x = net, attrname = "edge_color",
                              value = ifelse(net %e% "weights" < 0,
                                             "#D55E00",
                                             "#009E73"))
e <- abs(as.numeric(x$pcor_adj[[1]]))
    
plt <- ggnet2(net, edge.alpha = e[e != 0] / max(e),
              edge.size = "abs_weights",
              edge.color = "edge_color",
              node.size = 13,
              mode = "circle") +
  geom_point(color = "black",
              size = 14) +
  geom_point(size = 13, color = "white")  +
  guides(color = "none") +
  geom_text(label = cn) +
  labs(title = "Concussion - Control")
plt
```

