---
title: "ESM cleaning"
author: "Stephen Raynes"
date: "6/28/2022"
output: html_document
---

#Setup
```{r Libraries, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(car)
library("ggpubr")
library("corrplot")

```

```{r CSVs}
#load in most recent csv's 
Pre <- read_csv("ESM+Pre-Survey_November+30,+2022_17.43.csv")

Instruction <- read_csv("INSTRUCTION 2.csv")
Corpus <- read_csv("Corpus 6.csv")

Post <- read_csv("ESM+Post-Survey_November+30,+2022_17.46.csv")

```


Rename corpus and instruction columns first
```{r Rename Columns}
Instruction <-
  Instruction %>% 
  dplyr::rename(
         participantID = ...6,
         participantNUM = Survey,
         PID = `Question 5`
         )

Corpus <-
  Corpus %>% 
  dplyr::rename(
         duration = ...4,
         finished = ...5,
         participantID = ...6,
         participantNUM = Survey,
         attention = Q2,
         wb = Q3,
         inner_speech = Q4,
         clarity = Q5, 
         valence = Q6,
         reaction = Q7,
         interesting = Q8,
         inner_experience = Q9...18,
         no_inner_speech_clarity = Q10,
         no_inner_speech_valence = Q11,
         no_inner_speech_reaction = Q12,
         no_inner_speech_interesting = Q13,
         activity = Q14...24)

```


```{r Remove rows}

Pre <-
  Pre[-(1:2),]
Instruction <-
  Instruction[-(1:2),]
Corpus <-
  Corpus[-(1:2),]
Post <-
  Post[-(1:2),]

```

```{r Remove columns}
Pre <-
  Pre %>% 
  dplyr::select(-Status,
                -Finished,
                -IPAddress,
                -RecipientLastName,
                -RecipientFirstName,
                -RecipientEmail,
                -ExternalReference,
                -LocationLatitude,
                -LocationLongitude,
                -DistributionChannel,
                -UserLanguage)

Instruction <-
 Instruction %>% 
  dplyr::select(-...1,
                -...2,
                -...3,
                -...4,
                -...5,
                -...7,
                -...8,
                -`Question 1`,
                -`Question 2`,
                -`Question 3`,
                -`Question 4`)

Corpus <-
  Corpus %>% 
  dplyr::select(-...7,
                -...8,
                -`Question 1`)

Post <-
  Post %>% 
  dplyr::select(-Status,
                -Finished,
                -IPAddress,
                -RecipientLastName,
                -RecipientFirstName,
                -RecipientEmail,
                -ExternalReference,
                -LocationLatitude,
                -LocationLongitude,
                -DistributionChannel,
                -UserLanguage)

```


```{r Combine ESM Parts}

#ensure these are all the same
length(unique(Corpus$participantID))
length(unique(Corpus$participantNUM))

length(unique(Instruction$participantID))
length(unique(Instruction$participantNUM))

#differences likely due to people who missed the instruction but did the rest of the ESM... there's not a way to link pre, corpus, and post without PID - which was collected in instruction but not corpus. Therefore I need to remove those people. Looks like that was 57 people. 

phone <-  Corpus %>% 
  left_join(Instruction, by = "participantID")

length(unique(phone$participantID))
length(unique(phone$PID))

unique(Corpus$participantID)
unique(Instruction$participantID)

#this seems to work. Then can delete it if PID is NA 
phone <- phone[!(is.na(phone$PID)), ]
length(unique(phone$PID))

unique(phone$PID)


##clean up PID so it's all the same - repeat this with Qualtrics parts
#remove tests
phone <- 
  phone %>%
  filter(PID != "Test") %>%
  filter(PID != "Madeleine")
#standardize names
phone$PID <- toupper(phone$PID) #make letters all uppercase
phone$PID <- gsub('A', '', phone$PID) # remove the "A" since many didn't do this 
phone$PID <- gsub('PID：', '', phone$PID)
phone$PID <- gsub('UCSD ', '', phone$PID)
phone$PID[phone$PID=="(16353844) I WS NOT PRESENT, I WS FEELING -1, I WS EXPERIENCING INNER SPEECH, I WS EXPERIENCING HUNGER, MY INNER SPEECH WS SOMEWHT CLER (5), I’D RTE MY INNER SPEECH  -1, I FEEL  MODERTE RECTION TO IT (3), I PERSONLLY DON’T FIND IT VERY INTERESTING (1), I WS BEING “SOCIL” (I WS IN N ONLINE ZOOM MEETING FOR  GROUP PROJECT)"] = "16353844"
phone$PID[phone$PID=="16812819"] = "15812819" #specific case of student emailing to say they typed in incorrect PID 


unique(phone$PID)


#this is ESM N before data cleaning 
length(unique(phone$PID))



```

```{r Combine pre/post parts}

##Pre
Pre <-
  Pre %>% 
  dplyr::rename(
        PID = pid
         )

unique(Pre$PID)

#clean up PID so it's all the same

#remove tests
Pre <- 
  Pre %>%
  filter(PID != "Test") %>%
  filter(PID != "madeleine") %>%
  filter(PID != "AAAAAAAA") %>%
  filter(PID != "asdfasdasd") %>%
  filter(PID != "asdfasdf") %>%
  filter(PID != "NA") 

#standardize names
Pre$PID <- toupper(Pre$PID) #make letters all uppercase
Pre$PID <- gsub('A', '', Pre$PID) # remove the "A" since many didn't do this 

unique(Pre$PID)

Pre$PID <- gsub('PID：', '', Pre$PID)
Pre$PID <- gsub('UCSD ', '', Pre$PID)

unique(Pre$PID)


#this is PRE N before data cleaning 
length(unique(Pre$PID))

##Post

Post <-
  Post %>% 
  dplyr::rename(
        PID = pid
         )

##clean up PID so it's all the same 
unique(Post$PID)
#remove tests
Post <- 
  Post %>%
  filter(PID != "Test") %>%
  filter(PID != "Madeleine") %>%
  filter(PID != "AAAAAAAA") %>%
  filter(PID != "asdfasdasd") %>%
  filter(PID != "asdfasdf") %>%
  filter(PID != "NA") 

#standardize names
Post$PID <- toupper(Post$PID) #make letters all uppercase
Post$PID <- gsub('A', '', Post$PID) # remove the "A" since many didn't do this 

unique(Post$PID)

#this is POST N before data cleaning 
length(unique(Post$PID))



##Combine Pre/Post by PID
Qualtrics <-
  merge(x = Pre,
        y = Post,
        by = "PID",
        no.dups = F)

Qualtrics <- Qualtrics[!(is.na(Qualtrics$PID)), ]

length(unique(Qualtrics$PID))

```



#Clean pre/post parts

Clean pre/post before combining everything together:
```{r Incompletes} 

#Pre-reg doesn't say 100% complete, so don't use this; incompletes will be filtered out when combining parts anyway 

# 
# Qualtrics$Progress.x <-
#   as.numeric(as.character(Qualtrics$Progress.x))
# Qualtrics$Progress.y <-
#   as.numeric(as.character(Qualtrics$Progress.y))
# 
# 
# Qualtrics <- 
#   Qualtrics %>%
#   filter(Progress.x > 26) %>% #to keep people who didn't click to last page 
#   filter(Progress.y > 26)
# 
# 
# unique(Qualtrics$PID)
```

TIME TO COMPLETE STUDY - just for qualtrics
Didn't say in pre-reg I'd do this so ignore
```{r Duration for Qualtrics}

# ##Duration in minutes
# Qualtrics$`Duration (in seconds).x` <- as.numeric(Qualtrics$`Duration (in seconds).x`)
# Qualtrics$`Duration (in seconds).y` <- as.numeric(Qualtrics$`Duration (in seconds).y`)
# 
# 
# 
# #3 +/- SD away from mean 
# dur.posSD.1 <- mean(Qualtrics$`Duration (in seconds).x`) +
#   3*sd(Qualtrics$`Duration (in seconds).x`)
# dur.negSD.1 <- mean(Qualtrics$`Duration (in seconds).x`) -
#   3*sd(Qualtrics$`Duration (in seconds).x`)
# 
# dur.posSD.2 <- mean(Qualtrics$`Duration (in seconds).y`) +
#   3*sd(Qualtrics$`Duration (in seconds).y`)
# dur.negSD.2 <- mean(Qualtrics$`Duration (in seconds).y`) -
#   3*sd(Qualtrics$`Duration (in seconds).y`)
# 
# 
# #remove anyone who is above 3SD from mean 
# 
# Qualtrics <-
#   Qualtrics %>% 
#   mutate(duration.1 = ifelse(`Duration (in seconds).x`> dur.posSD.1 | 
#                              `Duration (in seconds).x`< dur.negSD.1, 1, 0),
#        duration.2 = ifelse(`Duration (in seconds).y`> dur.posSD.2 | 
#                              `Duration (in seconds).y`< dur.negSD.2, 1, 0))
# 
# duration.fail<-
#   Qualtrics %>% 
#   filter(duration.1 > 0 | duration.2 > 0 ) %>%
#   pull(PID)
# 
# length(duration.fail)
# 
# Qualtrics <-
#   Qualtrics %>% 
#   filter(!PID %in% duration.fail)


```

```{r Validation}
# phone$VAL1 - pre integrity - 1 or 4 are top 2
# phone$VAL2 - post integrity - 1 or 4 are top 2 

Qualtrics <-
  Qualtrics %>% 
  mutate(validation = ifelse(((VAL1 == "1" | VAL1 == "4") &
                              (VAL2 == "1" | VAL2 == "4")
                             ),0,1))

#failed validation check (note I did 1 OR 2, for BOTH parts, above)
validation.fail<-
  Qualtrics %>% 
  filter(validation > 0) %>%
  pull(PID)

length(validation.fail)

Qualtrics <-
  Qualtrics %>% 
  filter(!PID %in% validation.fail)


length(unique(Qualtrics$PID))

```

Hearing about study - have question, but didn't include in pre-reg so ignore 
```{r Hear about study}
#hear_about_study - in post

# Qualtrics$hear_about_study <- as.numeric(Qualtrics$hear_about_study)
# 
# hear.fail<-
#   Qualtrics %>% 
#   filter(hear_about_study < 2) %>%
#   pull(PID)
# 
# length(hear.fail)
# 
# Qualtrics <-
#   Qualtrics %>% 
#   filter(!PID %in% hear.fail)


```


ATTENTION CHECKS 
```{r Catch Questions}

# Qualtrics$personality_28 - 0
# Qualtrics$personality_51 - 0
# Qualtrics$ffmq_16 - 1

#rename attention checks so we can find them
Qualtrics <-
  Qualtrics %>% 
  dplyr::rename(att.1 = personality_28,
         att.2 = personality_51,
         att.3 = ffmq_16)

#recode as 0 and 1
Qualtrics <-
  Qualtrics %>%
  mutate(att.1 = ifelse(att.1 == "0", 0, 1),
         att.2 = ifelse(att.2 == "0", 0, 1),
         att.3 = ifelse(att.3 == "1", 0, 1))


#create total attention fail score
Qualtrics <-
  Qualtrics %>% 
  mutate(att.1 = as.numeric(att.1),
         att.2 = as.numeric(att.2), 
         att.3 = as.numeric(att.3),
         att.total = (att.1 + att.2 + att.3))


#count of fails and remove
att.fail <-
  Qualtrics %>% 
  filter(att.total > 1) %>% 
  pull(PID)

length(att.fail)

Qualtrics <-
  Qualtrics %>% 
  filter(!PID %in% att.fail)

length(unique(Qualtrics$PID))

```


Exclude people with 0 inner speech prompts
```{r No Inner Speech prompts}
# 1 = "Inner Speech"
# 2= "No Inner Speech"

#make inner speech 0 and numeric to filter it easier 
phone$inner_speech[phone$inner_speech==1] = 0 #inner speech
phone$inner_speech[phone$inner_speech==2] = 1 #no inner speech 
phone$inner_speech <- as.numeric(phone$inner_speech)


#inner speeech counts per person, before filtering
prompts<- phone %>%
  group_by(participantID) %>%
 summarise(n = length(participantID), 
           InSp=length(inner_speech[inner_speech==0]),
           NoInSp=length(inner_speech[inner_speech==1])) %>%
  arrange(n)
prompts


#filter
prompt.fail <-
 phone %>%
   group_by(participantID) %>%
   filter(length(inner_speech[inner_speech==0])==0) %>%
  pull(unique(participantID))
#how many participants had 0 inner speech prompts
length(unique(prompt.fail))
#delete them
phone <-
  phone %>% 
  filter(!participantID %in% prompt.fail)


#after filter
prompts<- phone %>%
  group_by(participantID) %>%
 summarise(n = length(participantID), 
           InSp=length(inner_speech[inner_speech==0]),
           NoInSp=length(inner_speech[inner_speech==1])) %>%
  arrange(n)
prompts

```

```{r Under-age}

#Age 

#recode dropdown input answers
Qualtrics$age <-
  as.character(Qualtrics$age)
#numbers are getting confusing with overlaps (i.e. it's changing 1 to 18  and then it repeats 18 with the other thing)
#so have to first change to letters to avoid overlap

Qualtrics$age[Qualtrics$age == "1"] <- "a" 
Qualtrics$age[Qualtrics$age == "2"] <- "b"
Qualtrics$age[Qualtrics$age == "3"] <- "c"
Qualtrics$age[Qualtrics$age == "4"] <- "d"
Qualtrics$age[Qualtrics$age == "5"] <- "e"
Qualtrics$age[Qualtrics$age == "6"] <- "f"
Qualtrics$age[Qualtrics$age == "7"] <- "g"
Qualtrics$age[Qualtrics$age == "8"] <- "h"
Qualtrics$age[Qualtrics$age == "9"] <- "i"
Qualtrics$age[Qualtrics$age == "10"] <- "j"
Qualtrics$age[Qualtrics$age == "11"] <- "k"
Qualtrics$age[Qualtrics$age == "12"] <- "l"
Qualtrics$age[Qualtrics$age == "13"] <- "m"
Qualtrics$age[Qualtrics$age == "14"] <- "n"
Qualtrics$age[Qualtrics$age == "15"] <- "o"
Qualtrics$age[Qualtrics$age == "16"] <- "p"
Qualtrics$age[Qualtrics$age == "17"] <- "q"
Qualtrics$age[Qualtrics$age == "18"] <- "r"
Qualtrics$age[Qualtrics$age == "19"] <- "s"
Qualtrics$age[Qualtrics$age == "20"] <- "t"
Qualtrics$age[Qualtrics$age == "21"] <- "u"
Qualtrics$age[Qualtrics$age == "22"] <- "v"
Qualtrics$age[Qualtrics$age == "23"] <- "w"
Qualtrics$age[Qualtrics$age == "24"] <- "x"
Qualtrics$age[Qualtrics$age == "25"] <- "y"
Qualtrics$age[Qualtrics$age == "26"] <- "z"
Qualtrics$age[Qualtrics$age == "27"] <- "aa"
Qualtrics$age[Qualtrics$age == "28"] <- "bb"
Qualtrics$age[Qualtrics$age == "29"] <- "cc"
Qualtrics$age[Qualtrics$age == "30"] <- "dd"
Qualtrics$age[Qualtrics$age == "31"] <- "ee"
Qualtrics$age[Qualtrics$age == "32"] <- "ff"
Qualtrics$age[Qualtrics$age == "33"] <- "gg"
Qualtrics$age[Qualtrics$age == "34"] <- "hh"
Qualtrics$age[Qualtrics$age == "35"] <- "ii"
#now can change letters to numbers without overlap thing
Qualtrics$age[Qualtrics$age == "a"] <- "13"
Qualtrics$age[Qualtrics$age == "b"] <- "14"
Qualtrics$age[Qualtrics$age == "c"] <- "15"
Qualtrics$age[Qualtrics$age == "d"] <- "16"
Qualtrics$age[Qualtrics$age == "e"] <- "17"
Qualtrics$age[Qualtrics$age == "f"] <- "18"
Qualtrics$age[Qualtrics$age == "g"] <- "19"
Qualtrics$age[Qualtrics$age == "h"] <- "20"
Qualtrics$age[Qualtrics$age == "i"] <- "21"
Qualtrics$age[Qualtrics$age == "j"] <- "22"
Qualtrics$age[Qualtrics$age == "k"] <- "23"
Qualtrics$age[Qualtrics$age == "l"] <- "24"
Qualtrics$age[Qualtrics$age == "m"] <- "25"
Qualtrics$age[Qualtrics$age == "n"] <- "26"
Qualtrics$age[Qualtrics$age == "o"] <- "27"
Qualtrics$age[Qualtrics$age == "p"] <- "28"
Qualtrics$age[Qualtrics$age == "q"] <- "29"
Qualtrics$age[Qualtrics$age == "r"] <- "30"
Qualtrics$age[Qualtrics$age == "s"] <- "31"
Qualtrics$age[Qualtrics$age == "t"] <- "32"
Qualtrics$age[Qualtrics$age == "u"] <- "33"
Qualtrics$age[Qualtrics$age == "v"] <- "34"
Qualtrics$age[Qualtrics$age == "w"] <- "35"
Qualtrics$age[Qualtrics$age == "x"] <- "36"
Qualtrics$age[Qualtrics$age == "y"] <- "37"
Qualtrics$age[Qualtrics$age == "z"] <- "38"
Qualtrics$age[Qualtrics$age == "aa"] <- "39"
Qualtrics$age[Qualtrics$age == "bb"] <- "40"
Qualtrics$age[Qualtrics$age == "cc"] <- "41"
Qualtrics$age[Qualtrics$age == "dd"] <- "42"
Qualtrics$age[Qualtrics$age == "ee"] <- "43"
Qualtrics$age[Qualtrics$age == "ff"] <- "44"
Qualtrics$age[Qualtrics$age == "gg"] <- "45"
Qualtrics$age[Qualtrics$age == "hh"] <- "46"
Qualtrics$age[Qualtrics$age == "ii"] <- "47"

Qualtrics$age <- as.numeric(Qualtrics$age)

psych::describe(Qualtrics$age)

#unclear what the NA's here are... just ignore 
age<-group_by(Qualtrics, age) %>%
 dplyr::summarise(n = length(age)) %>%
   arrange(desc(age))



#remove participants who are under 18 (should be nobody)
Qualtrics <-
  Qualtrics %>% 
  mutate(age.failure = ifelse(age < 18,1,0))


age.fail<-
  Qualtrics %>% 
  filter(age.failure > 0) %>%
  pull(PID)

length(age.fail)

Qualtrics <-
  Qualtrics %>% 
  filter(!PID %in% age.fail)

```

exclusion table - sort of easier to just not do that for this study
```{r Exclusion Table}

# #N after participant data cleaning
# ending<- nrow(Qualtrics)
# 
# #horizontal table
# exclusion_table <- matrix(c(
#   starting,
#  paste0("(", length(incomplete.fail), ")"),
#  paste0("(", length(attention.fail), ")"),
#   paste0("(", length(subjective.validity.fail), ")"),
#   paste0("(", length(task.engagement.fail), ")"),
#  paste0("(", length(duration.fail), ")"),
#  paste0("(", length(outlier.fail), ")"),
#  paste0("(", length(age.fail), ")"),
#   paste0(ending, " ",
#          "(",starting-ending,
#          ";", " ", 
#          100-round(ending/starting*100,2), "%",")")
#                   ), 
#                     ncol=9,
#                     byrow=F)
# 
# 
# colnames(exclusion_table) <- c("Starting N", "Completion Fail", "Attention Check Fail", "Subjective Validity Fail", "Task Engagement Fail", "Duration Fail", "Outlier Fail", "Age Fail", "Final N")
# rownames(exclusion_table) <- "Total"
# # exclusion_table <- round(exclusion_table,3)
# exclusion_table
# 
# 
# #check math adds up 
# sub<-
#   starting - 
#     length(incomplete.fail) - 
#     length(attention.fail) - 
#     length(subjective.validity.fail) - 
#     length(task.engagement.fail) - 
#     length(duration.fail) - 
#     length(outlier.fail) - 
#     length(age.fail) 
# 
# ending
# 
# isTRUE(sub==ending)
# 

```


#Recode Variables

```{r Gender / Sex}
# gender
Qualtrics$gender <-
  as.character(Qualtrics$gender)
Qualtrics$gender[Qualtrics$gender == "1"] <- "Male"
Qualtrics$gender[Qualtrics$gender == "2"] <- "Female"
Qualtrics$gender[Qualtrics$gender == "3"] <- "Transgender man"
Qualtrics <- Qualtrics %>% mutate(gender = 
                       ifelse(is.na(gender), "Transgender woman", gender)) #not sure why output did NA instead of 4 but this is correct
Qualtrics$gender[Qualtrics$gender == "5"] <- "Non-binary"
Qualtrics$gender[Qualtrics$gender == "6"] <- "Other"
Qualtrics$gender[Qualtrics$gender == "7"] <- "Prefer not to say"

unique(Qualtrics$gender)

# sex_at_birth
unique(Qualtrics$sex_at_birth)

Qualtrics$sex_at_birth <-
  as.character(Qualtrics$sex_at_birth)
Qualtrics$sex_at_birth[Qualtrics$sex_at_birth == "1"] <- "Male"
Qualtrics$sex_at_birth[Qualtrics$sex_at_birth == "2"] <- "Female"
Qualtrics <- Qualtrics %>% mutate(sex_at_birth = 
                       ifelse(is.na(sex_at_birth), "Intersex", sex_at_birth)) 
Qualtrics$sex_at_birth[Qualtrics$sex_at_birth == "4"] <- "Prefer not to say"

```


```{r Race}
# ethnoracial

Qualtrics$ethnoracial <-
  as.character(Qualtrics$ethnoracial)
Qualtrics$ethnoracial[Qualtrics$ethnoracial == "1"] <- "Asian"
Qualtrics$ethnoracial[Qualtrics$ethnoracial == "2"] <- "White"
Qualtrics$ethnoracial[Qualtrics$ethnoracial == "3"] <- "Hispanic or Latino"
Qualtrics$ethnoracial[Qualtrics$ethnoracial == "4"] <- "Black or African American"
Qualtrics$ethnoracial[Qualtrics$ethnoracial == "5"] <- "Middle Eastern or North African"
Qualtrics$ethnoracial[Qualtrics$ethnoracial == "6"] <- "Native Hawaiian or Other Pacific Islander"
Qualtrics$ethnoracial[Qualtrics$ethnoracial == "7"] <- "First Nation or Indigenous American"
Qualtrics$ethnoracial[Qualtrics$ethnoracial == "8"] <- "Mixed"
Qualtrics$ethnoracial[Qualtrics$ethnoracial == "9"] <- "Prefer not to say"
Qualtrics <- Qualtrics %>% mutate(ethnoracial = 
                       ifelse(is.na(ethnoracial), "Prefer not to say", ethnoracial)) 
unique(Qualtrics$ethnoracial)



```

COUNTRY
```{r Country}
##not sure how to easily do all this from qualtrics, so for now just manually rename the unqiue country codes

# country_born
test<-as.numeric(unique(Qualtrics$country_born))
test[order(test)]

Qualtrics$country_born[Qualtrics$country_born == "10"] <- "Austrailia"
Qualtrics$country_born[Qualtrics$country_born == "11"] <- "Austria"
Qualtrics$country_born[Qualtrics$country_born == "32"] <- "Canada"
Qualtrics$country_born[Qualtrics$country_born == "80"] <- "Iran"
Qualtrics$country_born[Qualtrics$country_born == "37"] <- "China"
Qualtrics$country_born[Qualtrics$country_born == "86"] <- "Japan"
Qualtrics$country_born[Qualtrics$country_born == "112"] <- "Mexico"
Qualtrics$country_born[Qualtrics$country_born == "137"] <- "Philippines"
Qualtrics$country_born[Qualtrics$country_born == "141"] <- "Moldova"
Qualtrics$country_born[Qualtrics$country_born == "171"] <- "Taiwan"
Qualtrics$country_born[Qualtrics$country_born == "187"] <- "United Kingdom"
Qualtrics$country_born[Qualtrics$country_born == "189"] <- "United States of America"
Qualtrics$country_born[Qualtrics$country_born == "194"] <- "Viet Nam"
Qualtrics$country_born[Qualtrics$country_born == "151"] <- "Saudi Arabia"
Qualtrics$country_born[Qualtrics$country_born == "75"] <- "Hong Kong"
Qualtrics$country_born[Qualtrics$country_born == "79"] <- "Indonesia"
Qualtrics$country_born[Qualtrics$country_born == "85"] <- "Jamaica"
Qualtrics$country_born[Qualtrics$country_born == "78"] <- "India"

unique(Qualtrics$country_born)




# country_raised
test<-as.numeric(unique(Qualtrics$country_raised))
test[order(test)]

Qualtrics$country_raised[Qualtrics$country_raised == "10"] <- "Austrailia"
Qualtrics$country_raised[Qualtrics$country_raised == "37"] <- "China"
Qualtrics$country_raised[Qualtrics$country_raised == "32"] <- "Canada"
Qualtrics$country_raised[Qualtrics$country_raised == "75"] <- "Hong Kong"
Qualtrics$country_raised[Qualtrics$country_raised == "86"] <- "Japan"
Qualtrics$country_raised[Qualtrics$country_raised == "112"] <- "Mexico"
Qualtrics$country_raised[Qualtrics$country_raised == "137"] <- "Philippines"
Qualtrics$country_raised[Qualtrics$country_raised == "141"] <- "Moldova"
Qualtrics$country_raised[Qualtrics$country_raised == "171"] <- "Taiwan"
Qualtrics$country_raised[Qualtrics$country_raised == "187"] <- "United Kingdom"
Qualtrics$country_raised[Qualtrics$country_raised == "189"] <- "United States of America"
Qualtrics$country_raised[Qualtrics$country_raised == "194"] <- "Viet Nam"
Qualtrics$country_raised[Qualtrics$country_raised == "151"] <- "Saudi Arabia"
Qualtrics$country_raised[Qualtrics$country_raised == "75"] <- "Hong Kong"
Qualtrics$country_raised[Qualtrics$country_raised == "79"] <- "Indonesia"
Qualtrics$country_raised[Qualtrics$country_raised == "85"] <- "Jamaica"
Qualtrics$country_raised[Qualtrics$country_raised == "78"] <- "India"
Qualtrics$country_raised[Qualtrics$country_raised == "103"] <- "Madagascar"

unique(Qualtrics$country_raised)


# country_reside

test<-as.numeric(unique(Qualtrics$country_reside))
test[order(test)]

Qualtrics$country_reside[Qualtrics$country_reside == "10"] <- "Austrailia"
Qualtrics$country_reside[Qualtrics$country_reside == "37"] <- "China"
Qualtrics$country_reside[Qualtrics$country_reside == "86"] <- "Japan"
Qualtrics$country_reside[Qualtrics$country_reside == "112"] <- "Mexico"
Qualtrics$country_reside[Qualtrics$country_reside == "137"] <- "Philippines"
Qualtrics$country_reside[Qualtrics$country_reside == "171"] <- "Taiwan"
Qualtrics$country_reside[Qualtrics$country_reside == "187"] <- "United Kingdom"
Qualtrics$country_reside[Qualtrics$country_reside == "189"] <- "United States of America"
Qualtrics$country_reside[Qualtrics$country_reside == "194"] <- "Viet Nam"

unique(Qualtrics$country_reside)


# age_move_US - confirm this is right
Qualtrics$age_move_US <- as.numeric(Qualtrics$age_move_US)-1

```

```{r Sexual Orientation}

Qualtrics$sexual_orientation_2 <-
  as.character(Qualtrics$sexual_orientation_2)
Qualtrics$sexual_orientation_2[Qualtrics$sexual_orientation_2 == "1"] <- "Heterosexual"
Qualtrics$sexual_orientation_2[Qualtrics$sexual_orientation_2 == "2"] <- "Gay or Lesbian"
Qualtrics$sexual_orientation_2[Qualtrics$sexual_orientation_2 == "3"] <- "Plurisexual (Bisexual, Pansexual, etc.)"
Qualtrics$sexual_orientation_2[Qualtrics$sexual_orientation_2 == "4"] <- "Not Listed"
Qualtrics <- Qualtrics %>% mutate(sexual_orientation_2 = 
                       ifelse(is.na(sexual_orientation_2), "Prefer Not to Respond", sexual_orientation_2))


unique(Qualtrics$sexual_orientation_2)

```


```{r SES}
#10 is best off, 1 is worst off
Qualtrics$ses_ladder <- as.numeric(Qualtrics$ses_ladder)

```



#DEFINING SCORES ON MEASURES


```{r Rename Summed Qualtrics Values}

#ffmq - create total score manually with and without observing 
#personality - subtract 1 from everything (qualtrics had a +1 on all items; 12 items per subgroup so it's -12 total)
# SC1 - awareness
# SC2 - observing
# SC3 - non reactivity
# SC4  - nonjudgement 
# SC5 - describe 
# SC6 - openness 
# SC7 - conscientiousness 
# SC8 - extraversion 
# SC9 - agreeableness
# SC10 - neuroticism 

#
Qualtrics$neuroticism <- as.numeric(Qualtrics$SC10)
Qualtrics$neuroticism <- Qualtrics$neuroticism -12

Qualtrics$extraversion <- as.numeric(Qualtrics$SC8)
Qualtrics$extraversion <- Qualtrics$extraversion -12

Qualtrics$openness <- as.numeric(Qualtrics$SC6)
Qualtrics$openness <- Qualtrics$openness -12

Qualtrics$agreeableness <- as.numeric(Qualtrics$SC9)
Qualtrics$agreeableness <- Qualtrics$agreeableness -12

Qualtrics$conscientiousness <- as.numeric(Qualtrics$SC7)
Qualtrics$conscientiousness <- Qualtrics$conscientiousness -12


#
Qualtrics$observing <- as.numeric(Qualtrics$SC2)
Qualtrics$describe <- as.numeric(Qualtrics$SC5)
Qualtrics$awareness <- as.numeric(Qualtrics$SC1)
Qualtrics$nonjudging <- as.numeric(Qualtrics$SC4)
Qualtrics$nonreactivity <- as.numeric(Qualtrics$SC3)

#ffmq totals 
Qualtrics <-
  Qualtrics %>%
  mutate(ffmq_all = (describe+awareness+nonjudging+nonreactivity+observing)/5) %>%
    mutate(ffmq_no_observe = (describe+awareness+nonjudging+nonreactivity)/4)

```



#Combine ESM with pre/post
```{r Combine everything}

ESM <-
  merge(x = phone,
        y = Qualtrics,
        by = "PID",
        no.dups = F)


length(unique(ESM$PID))

```

```{r Clean everything}
#check if any NA rows... there shouldn't be 
ESM <- ESM %>% 
  drop_na(wb)
#this leaves you with only rows where a participant answered a prompt


str(ESM$PID) 

# Number of prompts answered (out of 42 total that were sent to participants)
prompts<- ESM %>%
  group_by(PID) %>%
 dplyr::summarise(n = length(PID)) %>%
   arrange(desc(n))
prompts

psych::describe(prompts$n)
hist(prompts$n)

###there seems to be duplicate entries for some people. 
ESM <- ESM %>%
  distinct(duration, PID,
           .keep_all=T)


prompts<- ESM %>%
  group_by(PID) %>%
 dplyr::summarise(n = length(PID)) %>%
   arrange(desc(n))
prompts

psych::describe(prompts$n)
hist(prompts$n)


```

```{r Final Counts}

#sample size
length(unique(ESM$PID))

#prompts
length(ESM$PID)



```



#Publish CSV for Analysis
```{r Publish CSV}


write.csv(ESM, "ESM.Clean.Nov2022.csv")


```







