---
title: "ESM analysis"
author: "Stephen Raynes"
date: "6/30/2022"
output: html_document
---


#Setup
```{r Libraries, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(dplyr)
library(car)
library("ggpubr")
library("corrplot")
# install.packages("lme4")
library(lme4)
# install.packages("backports")
library(backports)     # to revive the isFALSE() function for sim_slopes()
# install.packages("effects")
library(effects)       # for probing interactions
library(ggplot2)       # for data visualization
# install.packages("interactions")
library(interactions)  # for probing/plotting interactions
# install.packages("lmerTest")
library(lmerTest)      # for p-values
# install.packages("psych")
library(psych)         # for describing the data
# detach(package:plyr)
# install.packages("chisq.posthoc.test")
library(chisq.posthoc.test)
# install.packages("MuMIn")
library(MuMIn)


packageVersion("lme4")
```

```{r CSVs}
#load in most recent csv's 
ESM <- read_csv("/Users/Stephen.Raynes/Downloads/ESM.Clean.Nov2022.csv")

#remove extra column this creates which gets annoying later on
ESM <- subset(ESM, select = -c(...1))

#distinguish just the pre/post measures for things like demo tables
Qualtrics <- ESM[!duplicated(ESM$PID), ]

```


```{r Counts}
#should be equal 
length(unique(ESM$PID))
length(unique(Qualtrics$PID))


#avg prompts per person
nrow(ESM) / length(unique(ESM$PID))


#SD/ range
 sd<- ESM %>%
 group_by(PID) %>%
  dplyr::summarise(prompts = length(PID),
                   avg = nrow(ESM)/prompts) %>%
    arrange(desc(prompts))
 sd

SD(sd$prompts)
range(sd$prompts)
mean(sd$prompts)

round((mean(sd$prompts) / 42 * 100),2)

round(4454/10009*100,2)


```



#Demographics
```{r Clean Up}
##clean up demo data first
###consider combining low counts with a "other" group

# Asian Nationals
# Born in Asia and moved to the USA after the age of 13
# Asian-American
# Born in Asia and moved to the USA before the age of 13
# Asian-American
# Both born and grew up in America but identified as ethnoracially Asia

unique(Qualtrics$ethnoracial)
#create asian national vs asian american category
Qualtrics$ethnoracial[Qualtrics$ethnoracial == "Asian" &
                          Qualtrics$age_move_US < 13] <- "Asian American"
Qualtrics$ethnoracial[Qualtrics$ethnoracial == "Asian" &
                          Qualtrics$country_born == "United States of America" &
                   Qualtrics$country_raised == "United States of America"] <- "Asian American"

Qualtrics$ethnoracial[Qualtrics$ethnoracial == "Asian" &
                          Qualtrics$age_move_US > 13] <- "Asian National"
Qualtrics$ethnoracial[Qualtrics$ethnoracial == "Asian" &
                          Qualtrics$country_born != "United States of America" |
                   Qualtrics$country_raised != "United States of America"] <- "Asian National"

group_by(Qualtrics, ethnoracial) %>%
 dplyr::summarise(n = length(ethnoracial)) %>%
   arrange(desc(n))



#create other to combine low cells - only do as needed!!!!!
# Qualtrics$ethnoracial[Qualtrics$ethnoracial == "Middle Eastern or North African" |
#                   Qualtrics$ethnoracial == "Prefer not to say" |
#                    Qualtrics$ethnoracial == "Black or African American"] <- "Other"

group_by(Qualtrics, ethnoracial) %>%
 dplyr::summarise(n = length(ethnoracial),
  `%` = (n/nrow(Qualtrics)*100)) %>%
   arrange(desc(n))

```


```{r Demo Table}
#create table 
table1::label(Qualtrics$age) <- "Age"
table1::label(Qualtrics$ses_ladder) <- "SES Ladder (1:10)"
table1::label(Qualtrics$gender) <- "Gender Identity"
table1::label(Qualtrics$sex_at_birth) <- "Sex at Birth"
table1::label(Qualtrics$sexual_orientation_2) <- "Sexual Orientation"
table1::label(Qualtrics$ethnoracial) <- "Ethno-Racial Category"

table1::table1(
  ~age + ses_ladder + gender + sex_at_birth + sexual_orientation_2 + ethnoracial 
               , data = Qualtrics, digits=3)


# my.render <- function(x, name, ...) {
#   if (name == "age") {
#    table1::render.default(x=x, name=name, ..., digits=3)
#   # } else if (name == "qrs_pre") {
#   #   table1::render.default(x=x, name=name, ..., digits=4)
#   } else {
#     table1::render.default(x=x, name=name, ..., digits=3)
#   }
# }
# 
# table1::table1(
#   ~age + ses_ladder + gender + sex_at_birth + sexual_orientation_2 + ethnoracial 
#                , data = Qualtrics, render=my.render)
# 
# 
# 
# 
# 
# my.render.cont2 <- function(x) {
#   with(table1::stats.default(x), sprintf("%s &plusmn; %s (%s, %s)",
#                                          table1::round_pad(MEAN,2),
#                                          table1::round_pad(SD,2),
#                                          MIN,MAX)) }
# # ?round_pad
# # my.render.cat <- function(x) {
# #     with(table1::stats.default(x),  sprintf("%d (%0.0f %%)", table1::round_pad(frequency,2)))
# # }
#             
# 
# 
# table1::table1(
#   ~age + ses_ladder + gender + sex_at_birth + sexual_orientation_2 + ethnoracial 
#                , data = Qualtrics
#                  ,render.continuous=my.render.cont2,
#                    render.categorical=my.render.cat)



round(mean(Qualtrics$age, na.rm=T),2)
round(mean(Qualtrics$age, na.rm=T),2)
1/337*100

```


```{r Trait Table}
#Other individual traits


#create table 
table1::label(Qualtrics$neuroticism) <- "Neuroticism"
table1::label(Qualtrics$extraversion) <- "Extraversion"
table1::label(Qualtrics$openness) <- "Openness"
table1::label(Qualtrics$agreeableness) <- "Agreeableness"
table1::label(Qualtrics$conscientiousness) <- "Conscientiousness"
table1::label(Qualtrics$observing) <- "FFMQ_Observing" 
table1::label(Qualtrics$describe) <- "FFMQ_Describing"
table1::label(Qualtrics$awareness) <- "FFMQ_Awareness"
table1::label(Qualtrics$nonjudging) <- "FFMQ_Nonjudging"
table1::label(Qualtrics$nonreactivity) <- "FFMQ_Nonreactivity"
table1::label(Qualtrics$ffmq_all) <- "FFMQ Total"
table1::label(Qualtrics$ffmq_no_observe) <- "FFMQ Total without Observing"

table1::table1(~neuroticism + extraversion + openness + agreeableness + conscientiousness +
                 observing + describe + awareness + nonjudging + nonreactivity + ffmq_all +ffmq_no_observe
               , data = Qualtrics) 

```


No groups to compare demo/traits against, so just need descriptive data on that. 


#Cleanup/Visualize Individual Variables


```{r Create Inner Speech Variables}

ESM <- ESM %>%
  mutate(clarity_all = coalesce(clarity,no_inner_speech_clarity)) %>%
  mutate(valence_all = coalesce(valence,no_inner_speech_valence)) %>%
  mutate(reaction_all = coalesce(reaction,no_inner_speech_reaction)) %>%
  mutate(interesting_all = coalesce(interesting,no_inner_speech_interesting))

# attention
# wb
# inner_speech 
# clarity
# valence
# reaction
# interesting
# inner_experience
# no_inner_speech_clarity
# no_inner_speech_valence
# no_inner_speech_reaction
# no_inner_speech_interesting
# activity

```


```{r Wellbeing}
# WELL-BEING: How were you feeling?
# [ 1 = '-3: Very bad' 2 = '-2' 3 = '-1' 4 = '0: Neutral' 5 = '1' 6 = '2' 7 = '3: Very good'  ]

ESM$wb[ESM$wb==1] <- -3
ESM$wb[ESM$wb==2] <- -2
ESM$wb[ESM$wb==3] <- -1
ESM$wb[ESM$wb==4] <- 0
ESM$wb[ESM$wb==5] <- 1
ESM$wb[ESM$wb==6] <- 2
ESM$wb[ESM$wb==7] <- 3


hist(ESM$wb) 

group_by(ESM, wb) %>%
 dplyr::summarise(n = length(wb),
                  `%` = (n/nrow(ESM)*100))

describe(ESM$wb)
hist(ESM$wb)

```


```{r Inner Speech}

# Which best describes what you were experiencing?
# [ 1 = 'INNER SPEECH: “I was experiencing inner speech (talking to myself INTERNALLY)”' 2 = 'NO INNER SPEECH: “I was NOT experiencing inner speech (NOT talking to myself INTERNALLY)”'  ]

ESM$inner_speech[ESM$inner_speech==0] = "Inner Speech"
ESM$inner_speech[ESM$inner_speech==1] = "No Inner Speech"

group_by(ESM, inner_speech) %>%
 dplyr::summarise(n = length(inner_speech), 
                `%` = (n/nrow(ESM)*100))


inner_pie <- 
  data.frame(`Inner Speech` = ESM$inner_speech, 
             participant = ESM$PID)

# df <- inner_pie %>% 
#   group_by(Inner.Speech) %>% # Variable to be transformed
#   count() %>% 
#   ungroup() %>% 
#   mutate(perc = `n` / sum(`n`)) %>% 
#   arrange(perc) %>%
#   mutate(labels = scales::percent(perc))
# 
# ggplot(df, aes(x = "", y = perc, fill = Inner.Speech)) +
#   geom_col() +
#   geom_text(aes(label = labels),
#             position = position_stack(vjust = 0.5)) +
#   coord_polar(theta = "y") +
#   guides(fill = guide_legend(title = "Inner Speech")) +
#   theme_void()


##old pie chart 

# 
# piedata<- c(length(ESM$inner_speech[ESM$inner_speech=="Inner Speech"]),
#             length(ESM$inner_speech[ESM$inner_speech=="No Inner Speech"]))
# 
# 
# pielabels<- c('Inner Speech', 
#               'No Inner Speech')
# 
# pie(piedata, pielabels,
#     border='black',
#     main = 'Inner Speech')
# 


```

```{r Prompt histograms}
##need to define esm-no-inner and esm-inner first, which is below somewhere


# histogram of no inner speech frequencies
# prompts<- ESM_no_inner %>%
#   group_by(PID) %>%
#  dplyr::summarise(n = length(PID)) %>%
#    arrange(desc(n))
# prompts

# hist(prompts$n, 
     # main = "Frequencies of No Inner Speech Prompts by Participant", 
     # breaks = 38,
     # xlab = "Number of No Inner Speech Prompts")

#histogram of inner speech frequencies
# prompts<- ESM_inner %>%
#   group_by(PID) %>%
#  dplyr::summarise(n = length(PID)) %>%
#    arrange(desc(n))
# prompts
# 
# hist(prompts$n, 
#      main = "Frequencies of Inner Speech Prompts by Participant", 
#      breaks = 38,
#      xlab = "Number of Inner Speech Prompts")


#histogram of inner speech as a percent per person 
# prompts<-group_by(ESM, PID) %>%
#  dplyr::summarise(inner_speech = length(inner_speech[inner_speech=="Inner Speech"]),
#                   no_inner_speech = length(inner_speech[inner_speech!="Inner Speech"]),
#                 percent_inner = (inner_speech/(inner_speech+no_inner_speech))*100) %>%
#    arrange(desc(percent_inner))
# 
# prompts
# 
# hist(prompts$percent_inner,
#      main = "Frequencies of % of Prompts that were Inner Speech by Participant",
#      # breaks = 100,
#      xlab = "% of Prompts that were Inner Speech")

```


inner experience - make separate data frame for that 
```{r Inner Experience}
# “Which of these were you primarily experiencing? (Select one)”
# [ 1 = 'BODY: “I was experiencing body sensations, e.g. hunger” ' 2 = 'EMOTION : “I was experiencing emotions, e.g. sadness"' 3 = 'ENVIRONMENT : “I was noticing the environment, e.g. looking at the trees”' 4 = 'MUSIC/SOUNDS : “I was listening to music/podcast, e.g. with my earphones in, or imagining music/sounds”' 5 = 'VISUAL IMAGERY: “I was experiencing visual imagery, e.g. imagining my dog”' 6 = 'ANOTHER PERSON: “I was experiencing another person, e.g. holding hands”' 7 = 'BLANK MIND:  “I was not thinking about anything at all-- my mind was completely blank”' 8 = 'Other' ]

ESM$inner_experience[ESM$inner_experience==1] = "Body"
ESM$inner_experience[ESM$inner_experience==2] = "Emotion"
ESM$inner_experience[ESM$inner_experience==3] = "Environment"
ESM$inner_experience[ESM$inner_experience==4] = "Music/Sounds"
ESM$inner_experience[ESM$inner_experience==5] = "Visual Imagery"
ESM$inner_experience[ESM$inner_experience==6] = "Another Person"
ESM$inner_experience[ESM$inner_experience==7] = "Blank Mind"
ESM$inner_experience[ESM$inner_experience==8] = "Other"


ESM_noinnerspeech <- ESM %>%
  filter(inner_speech=="No Inner Speech")

group_by(ESM_noinnerspeech, inner_experience) %>%
 dplyr::summarise(n = length(inner_experience), 
                `%` = (n/nrow(ESM_noinnerspeech)*100)) %>%
  arrange(desc(n))

inner_ex_pie <- 
  data.frame(`Inner Experience` = ESM_noinnerspeech$inner_experience, 
             participant = ESM_noinnerspeech$PID)

# df <- inner_ex_pie %>% 
#   group_by(Inner.Experience) %>% # Variable to be transformed
#   count() %>% 
#   ungroup() %>% 
#   mutate(perc = `n` / sum(`n`)) %>% 
#   arrange(perc) %>%
#   mutate(labels = scales::percent(perc))

# ggplot(df, aes(x = "", y = perc, fill = Inner.Experience)) +
#   geom_col() +
#   geom_text(aes(label = labels),
#             position = position_stack(vjust = .5)) +
#   coord_polar(theta = "y") +
#   guides(fill = guide_legend(title = "Inner Experience")) +
#   theme_void()



#old pie chart
# piedata<- c(length(ESM_noinnerspeech$inner_experience[ESM_noinnerspeech$inner_experience=="BODY: I was experiencing body sensations, e.g. hunger"]),
#             length(ESM_noinnerspeech$inner_experience[ESM_noinnerspeech$inner_experience=="EMOTION: I was experiencing emotions, e.g. sadness"]),
#             length(ESM_noinnerspeech$inner_experience[ESM_noinnerspeech$inner_experience=="ENVIRONMENT: I was noticing the environment, e.g. looking at the trees"]),
#             length(ESM_noinnerspeech$inner_experience[ESM_noinnerspeech$inner_experience=="MUSIC/SOUNDS : I was listening to music/podcast, e.g. with my earphones in, or imagining music/sounds"]),
#             length(ESM_noinnerspeech$inner_experience[ESM_noinnerspeech$inner_experience=="VISUAL IMAGERY: I was experiencing visual imagery, e.g. imagining my dog"]),
#             length(ESM_noinnerspeech$inner_experience[ESM_noinnerspeech$inner_experience=="ANOTHER PERSON: I was experiencing another person, e.g. holding hands"]),
#             length(ESM_noinnerspeech$inner_experience[ESM_noinnerspeech$inner_experience=="BLANK MIND:  I was not thinking about anything at all-- my mind was completely blank"]),
#             length(ESM_noinnerspeech$inner_experience[ESM_noinnerspeech$inner_experience=="Other"])
#             )
# 
# pielabels<- c('Body',
#               'Emotion',
#               'Environment',
#               'Music/Sounds',
#               'Visual Imagery',
#               'Another Person',
#               'Blank Mind',
#               'Other')
# 
# pie(piedata, pielabels,
#     border='black',
#     main = 'Inner Experience', 
#     clockwise=T)
# 



```

activity
```{r Activity}
# CURRENT ACTIVITY: “Whether in-person or online, what type of activity were you primarily doing? (select one)”
# [ 1 = 'Social activity (e.g., being with family, friends, or peers; phone calls or messages; attending a party or group outing)' 2 = 'Physical activity (e.g., exercising, sports, walking, bicycling, hiking) ' 3 = 'Restful activity (e.g., eating, resting, taking a nap, doing nothing, reading for fun, watching TV or videos, browsing the internet or social media) ' 4 = 'Household activity (e.g., preparing meals, grocery shopping, household finances, cleaning or other chores)' 5 = 'Cognitive activity (e.g., studying, homework, attending lecture, learning something new, puzzle solving)' 6 = 'Other' ]

ESM$activity[ESM$activity==1] = "Social"
ESM$activity[ESM$activity==2] = "Physical"
ESM$activity[ESM$activity==3] = "Restful"
ESM$activity[ESM$activity==4] = "Household"
ESM$activity[ESM$activity==5] = "Cognitive"
ESM$activity[ESM$activity==6] = "Other"

group_by(ESM, activity) %>%
 dplyr::summarise(n = length(activity), 
                `%` = (n/nrow(ESM)*100)) %>%
  arrange(desc(n))




inner_ac_pie <- 
  data.frame(activity = ESM$activity, 
             participant = ESM$PID)

# df <- inner_ac_pie %>% 
#   group_by(activity) %>% # Variable to be transformed
#   count() %>% 
#   ungroup() %>% 
#   mutate(perc = `n` / sum(`n`)) %>% 
#   arrange(perc) %>%
#   mutate(labels = scales::percent(perc))

# ggplot(df, aes(x = "", y = perc, fill = activity)) +
#   geom_col() +
#   geom_text(aes(label = labels),
#             position = position_stack(vjust = 0.5)) +
#   coord_polar(theta = "y") +
#   guides(fill = guide_legend(title = "Activity")) +
#   theme_void()



##old pie chart
# piedata<- c(length(ESM$activity[ESM$activity=="Social activity (e.g., being with family, friends, or peers; phone calls or messages; attending a party or group outing)"]),
#             length(ESM$activity[ESM$activity=="Physical activity (e.g., exercising, sports, walking, bicycling, hiking)"]),
#             length(ESM$activity[ESM$activity=="Restful activity (e.g., eating, resting, taking a nap, doing nothing, reading for fun, watching TV or videos, browsing the internet or social media))"]),
#             length(ESM$activity[ESM$activity=="Household activity (e.g., preparing meals, grocery shopping, household finances, cleaning or other chores)"]),
#             length(ESM$activity[ESM$activity=="Cognitive activity (e.g., studying, homework, attending lecture, learning something new, puzzle solving)"]),
#             length(ESM$activity[ESM$activity=="Other"]))
# 
# 
# pielabels<- c('Social', 
#               'Physical',
#               'Restful',
#               'Household',
#               'Cognitive',
#               'Other')
# 
# pie(piedata, pielabels,
#     border='black',
#     main = 'Activity', 
#     clockwise=T)

```


attention state
```{r Attention State}

ESM$attention[ESM$attention==1] = "Present"
ESM$attention[ESM$attention==2] = "Not Present"


group_by(ESM, attention) %>%
 dplyr::summarise(n = length(attention), 
                `%` = (n/nrow(ESM)*100)) %>%
  arrange(desc(n))



```



```{r Clarity}

# CLARITY: “What was the clarity of your inner speech/experience?”
# [ 1 = '1: Not at all clear' 2 = '2' 3 = '3' 4 = '4: Moderately clear' 5 = '5' 6 = '6' 7 = '7: Extremely clear'  ]

ESM$clarity_all 

hist(ESM$clarity_all) 

group_by(ESM, clarity_all) %>%
 dplyr::summarise(n = length(clarity_all),
                  `%` = (n/nrow(ESM)*100))


#total
describe(ESM$clarity_all)
hist(ESM$clarity_all) 
#prompts with inner speech
describe(ESM$clarity)
hist(ESM$clarity) 
#prompts without inner speech
describe(ESM$no_inner_speech_clarity)
hist(ESM$no_inner_speech_clarity) 


```


```{r Valence}

# VALENCE: “What was the valence of your inner speech/experience? If a stranger saw the content of your inner speech (i.e., just the actual words), how would they rate it?”

# [ 1 = '-3: Very negative' 2 = '-2' 3 = '-1' 4 = '0: Neutral' 5 = '1' 6 = '2' 7 = '3: Very positive'  ]

ESM$valence[ESM$valence==1] <- -3
ESM$valence[ESM$valence==2] <- -2
ESM$valence[ESM$valence==3] <- -1
ESM$valence[ESM$valence==4] <- 0
ESM$valence[ESM$valence==5] <- 1
ESM$valence[ESM$valence==6] <- 2
ESM$valence[ESM$valence==7] <- 3

ESM$valence_all[ESM$valence_all==1] <- -3
ESM$valence_all[ESM$valence_all==2] <- -2
ESM$valence_all[ESM$valence_all==3] <- -1
ESM$valence_all[ESM$valence_all==4] <- 0
ESM$valence_all[ESM$valence_all==5] <- 1
ESM$valence_all[ESM$valence_all==6] <- 2
ESM$valence_all[ESM$valence_all==7] <- 3

ESM$no_inner_speech_valence[ESM$no_inner_speech_valence==1] <- -3
ESM$no_inner_speech_valence[ESM$no_inner_speech_valence==2] <- -2
ESM$no_inner_speech_valence[ESM$no_inner_speech_valence==3] <- -1
ESM$no_inner_speech_valence[ESM$no_inner_speech_valence==4] <- 0
ESM$no_inner_speech_valence[ESM$no_inner_speech_valence==5] <- 1
ESM$no_inner_speech_valence[ESM$no_inner_speech_valence==6] <- 2
ESM$no_inner_speech_valence[ESM$no_inner_speech_valence==7] <- 3

ESM$valence_all 

group_by(ESM, valence_all) %>%
 dplyr::summarise(n = length(valence_all),
                  `%` = (n/nrow(ESM)*100))


#total
describe(ESM$valence_all)
hist(ESM$valence_all) 
#prompts with inner speech
describe(ESM$valence)
hist(ESM$valence) 
#prompts without inner speech
describe(ESM$no_inner_speech_valence)
hist(ESM$no_inner_speech_valence) 



#total prompts with mind wandering vs not 
describe(ESM$valence_all[ESM$attention=="Present"])
describe(ESM$valence_all[ESM$attention=="Not Present"])

#inner speech prompts with mind wandering vs not 
describe(ESM$valence[ESM$attention=="Present"])
describe(ESM$valence[ESM$attention=="Not Present"])

#no inner speech prompts with mind wandering vs not 
describe(ESM$no_inner_speech_valence[ESM$attention=="Present"])
describe(ESM$no_inner_speech_valence[ESM$attention=="Not Present"])


```


```{r Reaction}

# REACTION: “How much did you feel reactive to your inner speech/experience?”
# [ 1 = '1: No reaction at all' 2 = '2' 3 = '3' 4 = '4: Moderate reaction' 5 = '5' 6 = '6' 7 = '7: Extreme reaction'  ]

ESM$reaction_all 

group_by(ESM, reaction_all) %>%
 dplyr::summarise(n = length(reaction_all),
                  `%` = (n/nrow(ESM)*100))


#total
describe(ESM$reaction_all)
hist(ESM$reaction_all) 
#prompts with inner speech
describe(ESM$reaction)
hist(ESM$reaction) 
#prompts without inner speech
describe(ESM$no_inner_speech_reaction)
hist(ESM$no_inner_speech_reaction) 

```


```{r Interesting}
# INTERESTING: “How interesting was the inner speech/experience?”
# [ 1 = '1: Not at all interesting' 2 = '2' 3 = '3' 4 = '4: Moderately interesting' 5 = '5' 6 = '6' 7 = '7: Extremely interesting'  ]

ESM$interesting_all 

group_by(ESM, interesting_all) %>%
 dplyr::summarise(n = length(interesting_all),
                  `%` = (n/nrow(ESM)*100))


#total
describe(ESM$interesting_all)
hist(ESM$interesting_all) 
#prompts with inner speech
describe(ESM$interesting)
hist(ESM$interesting) 
#prompts without inner speech
describe(ESM$no_inner_speech_interesting)
hist(ESM$no_inner_speech_interesting) 

```




NOTE I am using inner speech prompts only now; and then I'll repeat stuff at end with no inner speech. I repeat this later on but I need to create it here for the descriptive stuff
```{r Make inner speech dataset}
#inner
ESM_inner <- ESM %>%
  filter(inner_speech=="Inner Speech")

```

#Visual Depictions

Note - wb goes from -3:3
```{r WB by Activity}

table1::label(ESM_inner$activity) <- "Activity"
table1::label(ESM_inner$wb) <- "Wellbeing"
table1::table1(~wb | activity , data = ESM_inner, digits=2)



# ESM_inner %>%
#   group_by(activity) %>%
#  summarise(Frequency = length(activity), Wellbeing = mean(wb)) %>%
#   arrange(desc(Frequency)) %>%
#   ggplot(aes(x = Wellbeing, y = Frequency), 
#          legend=FALSE) +
#   geom_point(aes(color = activity, size = Frequency), alpha = 0.5) +
#   scale_size(range = c(5, 25)) +
#     geom_label(aes(label=activity, size=8)) +
#   theme_minimal()+
#   geom_vline(xintercept=mean(ESM_inner$wb), linetype="solid", color = "red", size=.3)+
#   geom_text(aes(x=mean(ESM_inner$wb), label="\nMean Wellbeing", y=800), colour="red", angle=90, size=4) +
#   theme(legend.position = 'none')+
#   theme(plot.title = element_text(face = "bold", hjust = 0.5, size=14))+
#   # theme(axis.title.x = element_blank())+
#   theme(axis.title.y = element_text(size=14))+
#   theme(axis.text.x = element_text(size=14, angle = 45, hjust = 1))+
#   theme(axis.text.y = element_text(size=14))+
#   theme(legend.text = element_text(size=14))+
#   theme(legend.title = element_text(size=14))+
#   theme(panel.border = element_rect("black",  fill=NA))+
#   theme(plot.title = element_text(face = "bold"))+
#   theme(plot.title = element_text(hjust = 0))+
#   xlim(-1,2)
#   # ylim(0,60)
# 



sd(ESM_inner$wb)
sd(ESM_inner$wb[ESM_inner$activity=="Social"])
sd(ESM_inner$wb[ESM_inner$activity=="Physical"])
sd(ESM_inner$wb[ESM_inner$activity=="Household"])
sd(ESM_inner$wb[ESM_inner$activity=="Restful"])
sd(ESM_inner$wb[ESM_inner$activity=="Cognitive"])
sd(ESM_inner$wb[ESM_inner$activity=="Other"])


```


Note - wb goes from -3:3
```{r WB by Attention State}
table1::label(ESM_inner$attention) <- "Attention"
table1::label(ESM_inner$wb) <- "Wellbeing"

table1::table1(~wb | attention , data = ESM_inner, digits=2)


# ESM_inner %>%
#   group_by(attention) %>%
#  summarise(Frequency = length(attention), Wellbeing = mean(wb)) %>%
#   arrange(desc(Frequency)) %>%
#   ggplot(aes(x = Wellbeing, y = Frequency), 
#          legend=FALSE) +
#   geom_point(aes(color = attention, size = Frequency), alpha = 0.5) +
#   scale_size(range = c(5, 25)) +
#     geom_label(aes(label=attention, size=8)) +
#   theme_minimal()+
#   geom_vline(xintercept=mean(ESM_inner$wb), linetype="solid", color = "red", size=.3)+
#     geom_text(aes(x=mean(ESM_inner$wb), label="\nMean Wellbeing", y=2500), colour="red", angle=90, size=4) +
#   theme(legend.position = 'none')+
#   theme(plot.title = element_text(face = "bold", hjust = 0.5, size=14))+
#   # theme(axis.title.x = element_blank())+
#   theme(axis.title.y = element_text(size=14))+
#   theme(axis.text.x = element_text(size=14, angle = 45, hjust = 1))+
#   theme(axis.text.y = element_text(size=14))+
#   theme(legend.text = element_text(size=14))+
#   theme(legend.title = element_text(size=14))+
#   theme(panel.border = element_rect("black",  fill=NA))+
#   theme(plot.title = element_text(face = "bold"))+
#   theme(plot.title = element_text(hjust = 0))+
#   xlim(-1,2)
#   # ylim(0,60)


sd(ESM_inner$wb[ESM_inner$attention=="0"])
3602/4454

```


```{r visual depiction graphs for paper}
#combine above 2


library(ggrepel)
?ggrepel

# p1<-ESM_inner %>%
#   group_by(activity) %>%
#  summarise(
#    Frequency = length(activity),
#    Wellbeing = mean(wb)) %>%
#    arrange(desc(Wellbeing)) %>%
#   ggplot(aes(x = Wellbeing,
#              y = (seq_along(Wellbeing)),),
#          legend=FALSE) +
#       coord_cartesian(ylim=c(.5, 6.25))+
#   # scale_y_continuous(expand=c(.3,.3)) +
#   geom_point(aes(size = Frequency), alpha = 0.5) +
#   scale_size(range = c(5, 25)) +
#     geom_text(aes(label=activity, size=8, hjust=-.6),
#             check_overlap = TRUE,
#             position = position_dodge(width = 1), inherit.aes=T
#             )+
#   # geom_text(aes(label=activity, size=8, hjust=-.6),
#   #           # check_overlap = TRUE,
#   #           position = position_dodge(width = 1), inherit.aes=T)+
#   theme_minimal()+
#   geom_vline(xintercept=mean(ESM_inner$wb), linetype="dashed", size=.5)+
#   # geom_text(aes(x=mean(ESM_inner$wb),
#   #               label="\nMean Wellbeing"), angle=90, size=4) +
#   theme(legend.position = 'none')+
#   # theme(plot.title = element_text(face = "bold", hjust = 0.5, size=14))+
#   theme(axis.title.x = element_blank())+
#   theme(axis.title.y = element_blank())+
#   theme(axis.text.x = element_blank())+
#   theme(axis.text.y = element_blank())+
#   theme(legend.text = element_text(size=14))+
#   theme(legend.title = element_text(size=14))+
#   theme(panel.border = element_rect("black",  fill=NA))+
#   theme(plot.title = element_text(face = "bold"))+
#   theme(plot.title = element_text(hjust = 0))+
#   xlim(-1,2)+
#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
# p1<-p1+theme(plot.margin=unit(c(1,1,0,1),"cm"))
# 
# 
# 
# p2<-ESM_inner %>%
#   group_by(attention) %>%
#  summarise(
#    Frequency = length(attention),
#    Mood = mean(wb)) %>%
#    arrange(desc(Mood)) %>%
#   ggplot(aes(x = Mood,
#              y = (seq_along(Mood)),),
#          legend=FALSE) +
#       coord_cartesian(ylim=c(.5, 3))+
#   # scale_y_continuous(expand=c(.3,.3)) +
#   geom_point(aes(size = Frequency), alpha = 0.5) +
#   scale_size(range = c(5, 25)) +
#  geom_text(aes(label=c("Present", "Mind Wandering"), size=8, hjust=-.6),
#             check_overlap = TRUE)+
#   theme_minimal()+
#     geom_vline(xintercept=mean(ESM_inner$wb), linetype="dashed", size=.5)+
#   # geom_text(aes(x=mean(ESM_inner$wb),
#   #               label="\nMean Wellbeing"), angle=90, size=4) +
#   theme(legend.position = 'none')+
#   theme(plot.title = element_text(face = "bold", hjust = 0.5, size=14))+
#   # theme(axis.title.x = element_blank())+
#   theme(axis.title.y = element_blank())+
#   theme(axis.text.x = element_text(size=14, angle = 45, hjust = 1))+
#   theme(axis.text.y = element_blank())+
#   theme(legend.text = element_text(size=14))+
#   theme(legend.title = element_text(size=14))+
#   theme(panel.border = element_rect("black",  fill=NA))+
#   theme(plot.title = element_text(face = "bold"))+
#   theme(plot.title = element_text(hjust = 0))+
#   xlim(-1,2)+
#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
# p2<-p2+theme(plot.margin=unit(c(-0.1,1,1,1),"cm"))
# 
# 
# library(grid)
# require(gridExtra)
# grid.arrange(p1, p2, ncol = 1, heights = c(2, 1))



round(188/4454*100,2)

```


Convert to long format 
It seems the Exiwell default is long format, so I can skip this step actually!



```{r Activity as Covariate}

#activity by attention state
table <- table(ESM_inner$activity, ESM_inner$attention)
table
chisq.test(table, 
           simulate.p.value = F)

chisq.posthoc.test::chisq.posthoc.test(table,
                   method = "bonferroni",
                   round = 3,
                   simulate.p.value=F)


table1::label(ESM_inner$activity) <- "Activity"
table1::label(ESM_inner$attention) <- "Attention State"

table1::table1(~activity | attention
               , data = ESM_inner, digits=2) 



#activity alone in mlm - done in MLM section


```


##Zero order analysis
```{r Continuous vs Continuous}
# https://stats.stackexchange.com/questions/348901/correlation-between-two-variables-within-a-third-group

##continuous vs. continuous variables 

#dummy code attention first so it can go in here
ESM_inner$attention <- ifelse(ESM_inner$attention == 'Present', 1, 0)

##try rmcorr for repeated measures correlation
# install.packages("rmcorr")
# library(rmcorr)
# 
# 
# tab1<-rmcorr_mat(PID,
#            c("wb", "attention", "valence", "reaction", "clarity", "interesting"),
#             ESM_inner,
#            .95)
# 
# #matrix
# tab<-tab1$matrix
# tab<-round(tab,2)
# 
# #p values and CIs
# tab1$summary
# round(tab1$summary[,7],3)
# 
# data.frame(c(tab1$summary[,1]),
#        tab1$summary[,2],
#   round(tab1$summary[,7],3))



```


```{r Continuous vs. Categorical}

# - t test  / ANOVA

## categorical:
# ESM$attention
# ESM$inner_speech
# ESM$activity

## continuous:
# ESM$wb,
# ESM$valence_all,
# ESM$reaction_all,
# ESM$ffmq_all,
# ESM$ffmq_no_observe,
# ESM$awareness,
# ESM$describe,
# ESM$observing,
# ESM$nonjudging,
# ESM$nonreactivity,
# ESM$openness,
# ESM$conscientiousness,
# ESM$extraversion,
# ESM$agreeableness,
# ESM$neuroticism,
# ESM$clarity_all,
# ESM$interesting_all


# paired t test?  - we say that in pre-reg but i think it's anova

## *attenion

#wb
round(anova(lm(
  wb~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  wb~attention,
  data=ESM)),
  which="attention")

ggplot(ESM,
       aes(x=attention,y=wb,fill=attention))+
  stat_summary(fun.y="mean", geom="bar", position=position_dodge(),
               # aes(width=.25)
               )+
  stat_summary(geom="errorbar", position=position_dodge(), color='black',
               # aes(width=.25)
               )+
  theme_minimal()+
  ylab('Wellbeing')+
  ylim(-3,3)+
  xlab('Attention State')+
  theme(legend.position = 'none')+
  geom_hline(yintercept=0, linetype="solid",
             color = "black", size=1)+
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size=14))+
  theme(axis.title.x = element_text(size=14))+
  theme(axis.title.y = element_text(size=14))+
  theme(axis.text.x = element_text(size=14))+
  theme(axis.text.y = element_text(size=14))+
  theme(panel.border = element_rect("black",  fill=NA))+
  theme(plot.title = element_text(face = "bold"))+
  theme(plot.title = element_text(hjust = 0))

#valence
round(anova(lm(
  valence_all~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  valence_all~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=valence_all,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()

#reaction
round(anova(lm(
  reaction_all~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  reaction_all~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=reaction_all,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()


#clarity
round(anova(lm(
  clarity_all~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  clarity_all~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=clarity_all,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()

#interesting
round(anova(lm(
  interesting_all~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  interesting_all~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=interesting_all,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()


##inner_speech
#wb
round(anova(lm(
  wb~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  wb~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=wb,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#valence
round(anova(lm(
  valence_all~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  valence_all~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=valence_all,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#reaction
round(anova(lm(
  reaction_all~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  reaction_all~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=reaction_all,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()

#clarity
round(anova(lm(
  clarity_all~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  clarity_all~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=clarity_all,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#interesting
round(anova(lm(
  interesting_all~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  interesting_all~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=interesting_all,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()




##activity
#wb
round(anova(lm(
  wb~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  wb~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=wb,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()

#valence
round(anova(lm(
  valence_all~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  valence_all~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=valence_all,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()

#reaction
round(anova(lm(
  reaction_all~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  reaction_all~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=reaction_all,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()

#clarity
round(anova(lm(
  clarity_all~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  clarity_all~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=clarity_all,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#interesting
round(anova(lm(
  interesting_all~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  interesting_all~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=interesting_all,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()

```


```{r Categorical vs Categorical}
# attention state
# inner speech 
# activity

#attention by inner speech
table <- table(ESM$attention, ESM$inner_speech)
table
chisq.test(table, simulate.p.value = T)
chisq.posthoc.test::chisq.posthoc.test(table,
                   method = "bonferroni",
                   round = 3,
                   simulate.p.value=T)

table1::label(ESM$inner_speech) <- "Inner Speech"
table1::label(ESM$attention) <- "Attention State"
table1::table1(~inner_speech | attention
               , data = ESM)  ##this is an important result to show yes you have inner speech even when present!!!!
#flipped
table1::table1(~attention | inner_speech
               , data = ESM)



#attention by activity
table <- table(ESM_inner$attention, ESM_inner$activity)
table
chisq.test(table, simulate.p.value = T)
chisq.posthoc.test::chisq.posthoc.test(table,
                   method = "bonferroni",
                   round = 3,
                   simulate.p.value=T)

table1::label(ESM_inner$activity) <- "Activity"
table1::label(ESM_inner$attention) <- "Attention State"
table1::table1(~activity | attention
               , data = ESM_inner) 


#inner speech by activity
table <- table(ESM_inner$activity, ESM_inner$inner_speech)
table
chisq.test(table, simulate.p.value = T)
# chisq.posthoc.test::chisq.posthoc.test(table,
#                    method = "bonferroni",
#                    round = 3,
#                    simulate.p.value=T)


table1::label(ESM_inner$activity) <- "Activity"
table1::label(ESM_inner$inner_speech) <- "Inner Speech"
table1::table1(~activity | inner_speech
               , data = ESM_inner) 

```


```{r As individual MLMs}

##NOTE - do the next chunk (confirmatory analyses) FIRST, then go back and run this block.


## wb by:
# ESM_inner$attention

ESM_inner <- ESM_inner %>%
  mutate(attention = ifelse(attention == "Present", 1, -1))

ESM_inner$attention

#attention
model00_fit <- lmer(formula =
                      wb ~ attention+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 

summary(model00_fit)
Anova(model00_fit, type=3)
confint(model00_fit)

##I think I need to compare against a null for these
#Note modelcompare_fit will be the same when the DV is the same...
modelcompare_fit <- lmer(formula =
                      wb ~ 
                        # attention+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 

round(r.squaredLR(model00_fit)[1],4) - 
  round(r.squaredLR(modelcompare_fit)[1],4)



#valence
model00_fit <- lmer(formula =
                      wb ~ valence_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)

modelcompare_fit <- lmer(formula =
                      wb ~ 
                       # valence_all_cw2+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 

r.squaredLR(model00_fit)[1] - 
  r.squaredLR(modelcompare_fit)[1]


#reaction
model00_fit <- lmer(formula =
                      wb ~ reaction_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#clarity
model00_fit <- lmer(formula =
                      wb ~ clarity_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)



r.squaredLR(model00_fit)[1] - 
  r.squaredLR(modelcompare_fit)[1]


#interesting
model00_fit <- lmer(formula =
                      wb ~ interesting_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)

r.squaredLR(model00_fit)[1] - 
  r.squaredLR(modelcompare_fit)[1]


#activity
model00_fit <- lmer(formula =
                      wb ~ activity+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
# confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)



##



## attention by --> skip because DV being binary doesn't work


##

## valence by:

#attention
model00_fit <- lmer(formula =
                      valence_all ~ attention+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


modelcompare_fit <- lmer(formula =
                        valence_all ~ 
                          # attention+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 

r.squaredLR(model00_fit)[1] - 
  r.squaredLR(modelcompare_fit)[1]

#wb
model00_fit <- lmer(formula =
                      valence_all ~ wb+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
# confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#reaction
model00_fit <- lmer(formula =
                      valence_all ~ reaction_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#clarity
model00_fit <- lmer(formula =
                      valence_all ~ clarity_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#interesting
model00_fit <- lmer(formula =
                      valence_all ~ interesting_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#activity
model00_fit <- lmer(formula =
                      valence_all ~ activity+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
# confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


##

## reaction by:

#wb
model00_fit <- lmer(formula =
                      reaction_all ~wb+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
# confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)

#attention
model00_fit <- lmer(formula =
                      reaction_all ~ attention+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
Anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)

ESM_inner$attention


#valence
model00_fit <- lmer(formula =
                      reaction_all ~ valence_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)



#clarity
model00_fit <- lmer(formula =
                      reaction_all ~ clarity_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#interesting
model00_fit <- lmer(formula =
                      reaction_all ~ interesting_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#activity
model00_fit <- lmer(formula =
                      reaction_all ~ activity+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
# confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


##

## clarity by:

#attention
model00_fit <- lmer(formula =
                      clarity_all ~ attention+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#valence
model00_fit <- lmer(formula =
                      clarity_all ~ valence_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#reaction
model00_fit <- lmer(formula =
                      clarity_all ~ reaction_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#clarity
model00_fit <- lmer(formula =
                      clarity_all ~ wb+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
# confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#interesting
model00_fit <- lmer(formula =
                      clarity_all ~ interesting_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#activity
model00_fit <- lmer(formula =
                      clarity_all ~ activity+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
# confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


##

## Interesting by:

#attention
model00_fit <- lmer(formula =
                      interesting_all ~ attention+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#valence
model00_fit <- lmer(formula =
                      interesting_all ~ valence_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#reaction
model00_fit <- lmer(formula =
                      interesting_all ~ reaction_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#clarity
model00_fit <- lmer(formula =
                      interesting_all ~ clarity_all+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#wb
model00_fit <- lmer(formula =
                      interesting_all ~wb+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
# confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


#activity
model00_fit <- lmer(formula =
                      interesting_all ~ activity+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
# confint(model00_fit)
round(r.squaredLR(model00_fit)[1],4)


range(ESM_inner$wb)


```


***************************


#Confirmatory analyses


Disaggregating within-person center and between-person center variables
Make separate data sets for inner speech vs not, since that is easier for the variables like attention and activity that aren't separated like that
```{r Person mean centering}
##not disaggregating
# attention
# inner_speech 
# activity
# inner_experience 

##disaggregating
# wb
# clarity_all
# valence_all
# reaction_all
# interesting_all

ESM <- ESM %>% group_by(PID) %>% 
  mutate(
    wb_mean2 = mean(wb, na.rm = T),
    clarity_all_mean2 = mean(clarity_all, na.rm = T),
    valence_all_mean2 = mean(valence_all, na.rm = T),
    reaction_all_mean2 = mean(reaction_all, na.rm = T),
    interesting_all_mean2 = mean(interesting_all, na.rm = T)
  ) %>% ungroup() %>% 
  mutate(
    #these are grand mean centered variables
        wb_c2 = scale(wb, center = T, scale = F), 
    clarity_all_c2 = scale(clarity_all, center = T, scale = F), 
    valence_all_c2 = scale(valence_all, center = T, scale = F), 
    reaction_all_c2 = scale(reaction_all, center = T, scale = F), 
    interesting_all_c2 = scale(interesting_all, center = T, scale = F),
    #these are within-person centered variables
         wb_cw2 = wb-wb_mean2,
         clarity_all_cw2 = clarity_all-clarity_all_mean2,
         valence_all_cw2 = valence_all-valence_all_mean2,
         reaction_all_cw2 = reaction_all-reaction_all_mean2,
         interesting_all_cw2 = interesting_all-interesting_all_mean2,
    #these are between-person centered variables 
             wb_cb2 = wb_c2-wb_cw2,
         clarity_all_cb2 = clarity_all_c2-clarity_all_cw2,
         valence_all_cb2 = valence_all_c2-valence_all_cw2,
         reaction_all_cb2 = reaction_all_c2-reaction_all_cw2,
         interesting_all_cb2 = interesting_all_c2-interesting_all_cw2) 



```


Create inner speech vs not datasets 
```{r Inner speech datasets}
#inner
ESM_inner <- ESM %>%
  filter(inner_speech=="Inner Speech")

ESM_inner$inner_speech

#no inner
ESM_no_inner <- ESM %>%
  filter(inner_speech!="Inner Speech")

ESM_no_inner$inner_speech

```


#MLM

NOTE this is all for inner speech only! 

```{r Null Model}
# unconditional means model: will the model have a grand mean (intercept) greater than 0?
# reject the null model 
# Run unconditional means model with summary - Using PID as the (nested) random effect

#model
model0_fit <- lmer(formula = wb ~ 1 + (1|PID), 
              data=ESM_inner)
summary(model0_fit)

##for all of these, I was using loglik to see what fits the best. BUT loglik technically only applies when comparing a larger model that contains a smaller model; a less conservative and better way to compare is the AIC, where smallest AIC = best fitting model. Usually AIC and loglik will align 

##here you want the logLik (or preferably AIC) number to decrease (closer to 0 on loglik when it's negative is better fit) each time you add variables to the model (this shows you're improving the fit of your model), then you can test if that decease is sig different 
# StdDev of random effects is used to calculate ICC - 
# intercept variance is between person variance (0.31) - some people do on average have higher wb (by 0.31 units) than others 
# residual variance is within person variance (2.39) - yes meaningful fluctuation in wb from moment to moment within a person (w/ variance of 2.39) beyond what we'd expect from random chance alone
#Fixed effect tells you there is a sig (p-value showing 0 is okay) effect of the intercept that is different from 0; the Value tells you what the value of the grand mean is for your DV (0.8 in mine; recall I had WB go from -3 to +3, so this makes sense); mean wb across all people and prompts 

# note - mean happiness in killingsworth was 65/100 ; similar to mine being slightly higher than halfway point 

# IMPORTANT NOTES ABOUT THIS MODEL
# No predictors in the model (no independent variables)
# This is the null model (beginning of intercept only)
# Measuring the grand mean here

#so, intercept (grand mean) is significant so we can reject null model that it doesn't equal 0 
# there is enough variability to conduct an MLM

#used for ICC table in below block
wb_values <- summary(model0_fit)


##confidence intervals:
#using lme4:
round(confint(model0_fit, oldNames=FALSE),2)

```


ICC calculation
```{r Overall ICC}
##ICC calculation
# Calculate intra-class correlation coefficient (ICC) for the unconditional means model

VarCorr(model0_fit)
RandomEffects <- as.data.frame(VarCorr(model0_fit))
RandomEffects
ICC_between <- RandomEffects[1,4]/(RandomEffects[1,4]+RandomEffects[2,4]) 
round(ICC_between*100,2)
# of the total variance in DV, XX% is attributable to between-person variation 
# Any value below 5% here suggests clustering is not taking place and MLM should not take place

round((100-(ICC_between*100)),2)
# whereas XX% is attributatable to within-person variation.

#consider adding info on null model - as a first step, the intra-class correlation coefficient (ICC) for the unconditional means model was calculated and revealed that of the total variance in mood scores, 27.53% is attributable to between-person variation, whereas 72.47% is attributable to within-person variation. This suggests that clustering is taking place and multilevel modeling is appropriate in our data. 


```


Do ICC for each PV to ensure there is sufficeint within and between variation to disaggregate 
```{r ICC per Variable}

##possible variables to disaggregate:
# wb
# clarity
# valence
# reaction
# interesting

clarity_fit <- lmer(formula = clarity_all ~ 1 + (1|PID), 
              data=ESM_inner)
summary(clarity_fit) #recall Fixed effect tells you there is a sig (p-value showing 0 is okay) effect of the intercept that is different from 0; the Value tells you what the value of the grand mean is for your PV
clarity_values <- summary(clarity_fit) 
VarCorr(clarity_fit)
RandomEffects_clarity <- as.data.frame(VarCorr(clarity_fit))
RandomEffects_clarity
ICC_between_clarity <- RandomEffects_clarity[1,4]/(RandomEffects_clarity[1,4]+RandomEffects_clarity[2,4]) 
round(ICC_between_clarity*100,2)
round((100-(ICC_between_clarity*100)),2)

valence_fit <- lmer(formula = valence_all ~ 1 + (1|PID), 
              data=ESM_inner)
summary(valence_fit) #recall Fixed effect tells you there is a sig (p-value showing 0 is okay) effect of the intercept that is different from 0; the Value tells you what the value of the grand mean is for your PV
valence_values <- summary(valence_fit) 
VarCorr(valence_fit)
RandomEffects_valence <- as.data.frame(VarCorr(valence_fit))
RandomEffects_valence
ICC_between_valence <- RandomEffects_valence[1,4]/(RandomEffects_valence[1,4]+RandomEffects_valence[2,4]) 
round(ICC_between_valence*100,2)
round((100-(ICC_between_valence*100)),2)

reaction_fit <- lmer(formula = reaction_all ~ 1 + (1|PID), 
              data=ESM_inner)
summary(reaction_fit) #recall Fixed effect tells you there is a sig (p-value showing 0 is okay) effect of the intercept that is different from 0; the Value tells you what the value of the grand mean is for your PV
reaction_values <- summary(reaction_fit) 
VarCorr(reaction_fit)
RandomEffects_reaction <- as.data.frame(VarCorr(reaction_fit))
RandomEffects_reaction
ICC_between_reaction <- RandomEffects_reaction[1,4]/(RandomEffects_reaction[1,4]+RandomEffects_reaction[2,4]) 
round(ICC_between_reaction*100,2)
round((100-(ICC_between_reaction*100)),2)


interesting_fit <- lmer(formula = interesting_all ~ 1 + (1|PID), 
              data=ESM_inner)
summary(interesting_fit) #recall Fixed effect tells you there is a sig (p-value showing 0 is okay) effect of the intercept that is different from 0; the Value tells you what the value of the grand mean is for your PV
interesting_values <- summary(interesting_fit) 
VarCorr(interesting_fit)
RandomEffects_interesting <- as.data.frame(VarCorr(interesting_fit))
RandomEffects_interesting
ICC_between_interesting <- RandomEffects_interesting[1,4]/(RandomEffects_interesting[1,4]+RandomEffects_interesting[2,4]) 
round(ICC_between_interesting*100,2)
round((100-(ICC_between_interesting*100)),2)

#create a table of this to make it clear including wb ICC

ICC_table <- matrix(c(
                    ICC_between*100,(100-(ICC_between*100)), 
                    wb_values$coefficients[1], wb_values$coefficients[5], 
                    ICC_between_clarity*100,(100-(ICC_between_clarity*100)),
                    clarity_values$coefficients[1], clarity_values$coefficients[5], 
                    ICC_between_valence*100,(100-(ICC_between_valence*100)),
                    valence_values$coefficients[1], valence_values$coefficients[5], 
                    ICC_between_reaction*100,(100-(ICC_between_reaction*100)),
                    reaction_values$coefficients[1], reaction_values$coefficients[5], 
                    ICC_between_interesting*100,(100-(ICC_between_interesting*100)),
                    interesting_values$coefficients[1], interesting_values$coefficients[5]
                    ), 
                    ncol=4,byrow=TRUE)


colnames(ICC_table) <- c("Between-Variance %", "Within-Variance %", "Estimate", "P-value")
rownames(ICC_table) <- c("Wellbeing (-3:3)","Clarity (1:7)","Valence (-3:3)", "Reaction (1:7)", "Interesting (1:7)")
ICC_table <- round(ICC_table,3)
ICC_table
# all seem good to go; use this table to prove  
# p value just tells you the estimate is diff from 0; body reaction not being sig is okay since it's a -3:+3 scale.... right? I think so....

```

```{r Activity}
#activity alone in mlm as further support about it being a covariate

modela_fit <- lmer(formula = wb ~ activity + (1|PID), 
              data=ESM_inner)
summary(modela_fit)
car::Anova(modela_fit, type=3)
anova(modela_fit)
round(confint(modela_fit, oldNames=FALSE),2)

(r.squaredLR(modela_fit)[1]) - (r.squaredLR(model0_fit)[1])


#yes it should be a covariate
```

```{r Clarity}

modelc_fit <- lmer(formula = wb ~ clarity_all_cw2 + (1|PID), 
              data=ESM_inner)
summary(modelc_fit)

round(confint(modelc_fit, oldNames=FALSE),2)


(r.squaredLR(modelc_fit)[1]) - (r.squaredLR(model0_fit)[1])

```


Adding PV's to model -  
full model =  conditional growth model = model with all your PV's

##Model 1: attention state
```{r Without Covariates}

model1_fit <- lmer(formula = wb ~
                attention+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) #must set this to F to return loglik and AIC


# the intercept here represents the referent category, which I can change 
summary(model1_fit)

#interpreting results:
# Fixed effects:
#   - Intercept: expected value of WB for prototypical person on a prototypical prompt is XX
# -   aware_cw2: on prompts when the prototypical person's attention was higher than normal, their wb tended to be XX units higher than usual, which was stat sig 
# Random effects:
# - intercept: there is XX between-person variance in individual's expected value of WB

#generally can ignore the correlation table thing:
# https://stats.stackexchange.com/questions/57240/how-do-i-interpret-the-correlations-of-fixed-effects-in-my-glmer-output

#for singular fit error: 
#When you obtain a singular fit, this is often indicating that the model is overfitted – that is, the random effects structure is too complex to be supported by the data, which naturally leads to the advice to remove the most complex part of the random effects structure (usually random slopes)
# summary(rePCA(model1_fit))



# https://stats.stackexchange.com/questions/339678/interpreting-effects-of-categorical-and-continuous-predictors-in-multiple-linear
#but we can do this on the model to see the "global" effect of the factor
anova(model1_fit, type=3)


#the difference in MLM vs ANOVA for activity, which is the same for a linear regression vs ANOVA generally, is that:
    # In the ANOVA, the categorical variable is effect coded. This means that the categories  are coded with 1’s and -1 so that each category’s mean is compared to the grand mean.
    # In the regression, the categorical variable is dummy coded**, which means that each  category’s intercept is compared to the reference group‘s intercept.  Since the intercept is defined as the mean value when all other predictors = 0, and there are no other  predictors, the three intercepts are just means.


confint(model1_fit)


#effect size estimate 
# compare with- model0_fit - null
# library(MuMIn)
(r.squaredLR(model1_fit)[1]) - (r.squaredLR(model0_fit)[1])


# #plot within-person differences of main effects
# ##repeat this to ensure direction of effects is as expected
ggplot(data=ESM_inner, aes(x=attention,
                            y=wb_cw2, group=factor(PID), colour="gray"), legend=FALSE)+
  geom_smooth(method=lm, se=FALSE, fullrange=FALSE, lty=1, size=.05, color="gray40") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="blue") +
  xlab("Awareness") + ylab("Wellbeing") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Within-Person Association of Attention State and Wellbeing") +
    # scale_x_continuous(limits=c(1,5),   #check range of PV
    #                  breaks = c(1,2,3,4,5)
    #                  ) +
    #       scale_y_continuous(limits=c(-3,3),
    #                  breaks = c(-3, -2, -1, 0, 1, 2, 3)
    #                  ) +
  geom_hline(yintercept=0,
               # color="red",
               size=1)+
  xlab("Attention State")+
  ylab("WellBeing \n (higher = greater wb)")

```

```{r test factors in mlm, include=FALSE}

# ESM_inner_test <- ESM_inner
# 
# ESM_inner_test$activity <- as.factor(ESM_inner_test$activity)
# ESM_inner_test$attention <- ESM_inner_test$attention
# 
# # ESM_inner_test$attention <- factor(ESM_inner_test$attention,
#                                    # levels = c("Present", "Not Present"))
# 
# 
# #try to get activity and attention as one factor variable
# modeltest_fit <- lmer(formula = wb ~
#                      activity+
#                 attention+
#                  (1|PID), 
#                     data=ESM_inner_test,
#                    REML = F) #must set this to F to return loglik and AIC
# summary(modeltest_fit)
# anova(modeltest_fit, type=3)
# anova(modeltest_fit)
# car::Anova(modeltest_fit, type=3)
# 
# 
# # lmerTest::anova(modeltest_fit)
# 
# 
# 8.79/100
# .44/6
# 
# 
# ## code as 1 and 2
ESM_inner_test <- ESM_inner
# 
# 
# ESM_inner_test <- ESM_inner
# # ESM_inner_test$activity <- as.factor(ESM_inner_test$activity)
# ESM_inner_test$attention[ESM_inner_test$attention=="Present"]<- "1"
# ESM_inner_test$attention[ESM_inner_test$attention=="Not Present"]<- "0"
# ESM_inner_test$attention <- as.numeric(ESM_inner_test$attention)
# 
modeltest_fit <- lmer(formula = wb ~
                     activity+
                attention+
                 (1|PID),
                    data=ESM_inner_test,
                   REML = F) #must set this to F to return loglik and AIC
summary(modeltest_fit)
anova(modeltest_fit, type=3)

# ESM_inner_test$activity <- as.factor(ESM_inner_test$activity)
# 
# 
# #
# # install.packages("recipes")
# library(recipes)
# 
ESM_inner_test <- ESM_inner

ESM_inner_test$activity[ESM_inner_test$activity=="Cognitive"]<- "0"
ESM_inner_test$activity[ESM_inner_test$activity=="Restful"]<- "1"
ESM_inner_test$activity[ESM_inner_test$activity=="Social"]<- "2"
ESM_inner_test$activity[ESM_inner_test$activity=="Household"]<- "3"
ESM_inner_test$activity[ESM_inner_test$activity=="Physical"]<- "4"
ESM_inner_test$activity[ESM_inner_test$activity=="Other"]<- "5"
ESM_inner_test$activity <- as.numeric(ESM_inner_test$activity)


ESM_inner_test$activity <- factor(ESM_inner_test$activity)

```

```{r With Covariates}
#check if attention is dummy coded or not 
ESM_inner$attention

#make -1 and +1 if it's not already
# ESM_inner <- ESM_inner %>%
#   mutate(attention = ifelse(attention == "Present", 1, -1))

model1a_fit <- lmer(formula = wb ~
                     activity+
                      clarity_all_cw2+ #as a covariate
                    interesting_all_cw2+ #MAKE SURE THIS IS ADDED TO ALL MODELS NOW
                attention+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) #must set this to F to return loglik and AIC
summary(model1a_fit)
anova(model1a_fit, type=3)
confint(model1a_fit)




# test_fit <- lmer(formula = wb ~
#                      # activity+clarity_all_cw2+ #as a covariate
#                 attention+
#                  (1|PID), 
#                     data=ESM_inner,
#                    REML = F) #m
# tab_model(test_fit)


#effect size 
#change # for each variable
modelcompare_fit <- lmer(formula = wb ~
                     activity+
                       clarity_all_cw2+
                       interesting_all_cw2+
                # attention+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F)
round((r.squaredLR(model1a_fit)[1]) - (r.squaredLR(modelcompare_fit)[1]),4)





###model comparison 
anova(model1_fit, model1a_fit)



##try scaling DV to compare easily with killingsworth
ESM_inner_1 <- ESM_inner
ESM_inner_1$wb <- ESM_inner_1$wb*(100/6)


model1aa_fit <- lmer(formula = wb ~
                     activity+clarity_all_cw2+ #as a covariate
                attention+
                 (1|PID), 
                    data=ESM_inner_1,
                   REML = F) #must set this to F to return loglik and AIC
summary(model1aa_fit)
anova(model1aa_fit, type=3)

```

extra for karen
```{r check individual variables}

model1aa_fit <- lmer(formula = wb ~
                     activity+
                      clarity_all_cw2+
                    interesting_all_cw2+
                attention+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) #must set this to F to return loglik and AIC
summary(model1aa_fit)
anova(model1aa_fit, type=3)


#effect size 
#change # for each variable
modelcompare1aa_fit <- lmer(formula = wb ~
                     activity+
                       clarity_all_cw2+
                       interesting_all_cw2+
                # attention+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F)
round((r.squaredLR(model1aa_fit)[1]) - (r.squaredLR(modelcompare1aa_fit)[1]),4)


## direction of interesting
mean(ESM_inner$interesting_all[ESM_inner$attention==1])
mean(ESM_inner$interesting_all[ESM_inner$attention==-1])


# ggplot(ESM_inner, aes(x = interesting, y = wb, fill = attention, color=attention)) +
#   # geom_point() +
#   geom_smooth(method = "lm", se = FALSE) +  # Add a linear regression line
#   labs(x = "Interesting All", y = "WB") 
#   # + ggtitle("Correlation Plot")
# 
# ggplot(ESM_no_inner, aes(x = interesting, y = wb, fill = attention, color=attention)) +
#   # geom_point() +
#   geom_smooth(method = "lm", se = FALSE) +  # Add a linear regression line
#   labs(x = "Interesting All", y = "WB") 
#   # + ggtitle("Correlation Plot")

```

##Model 2: Mediation of Valeince
```{r Without Covariates}

#add valence in first
model2_fit <- lmer(formula = wb ~ 
                     attention+valence_all_cw2+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model2_fit)
anova(model2_fit, type=3)
confint(model2_fit)

#effect size
modelcompare_fit <- lmer(formula = wb ~ 
                     attention+
                       # valence_all_cw2+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
round((r.squaredLR(model2_fit)[1]) - (r.squaredLR(modelcompare_fit)[1]),4)

#comparing model fit
# anova(model2_fit, model1_fit)


# #plot within-person differences of main effects
# ##repeat this to ensure direction of effects is as expected

ggplot(data=ESM_inner, aes(x=valence_all_cw2,
                            y=wb_cw2, group=factor(PID), colour="gray"), legend=FALSE)+
  geom_smooth(method=lm, se=FALSE, fullrange=FALSE, lty=1, size=.05, color="gray40") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="blue") +
  xlab("Objective Valence") + ylab("Wellbeing") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Within-Person Association of Objective Valence and Wellbeing") +
    # scale_x_continuous(limits=c(1,5),   #check range of PV
    #                  breaks = c(1,2,3,4,5)
    #                  ) +
    #       scale_y_continuous(limits=c(-3,3),
    #                  breaks = c(-3, -2, -1, 0, 1, 2, 3)
    #                  ) +
  geom_hline(yintercept=0,
               # color="red",
               size=1)+
  xlab("Objective Valence \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")


##mediation 

#There is a lot of discussion / uncertainty online about how to properly do a mediation MLM. Just say that I use the Tingley, Dustin, et al, 2014, "Mediation" R package; and that this is a "1-1-1" mediation (hence the cw2 for each thing). The output is similar, though not exactly the same, without the cw2. 

# https://cran.r-project.org/web/packages/mediation/vignettes/mediation.pdf
# https://stats.stackexchange.com/questions/491503/mediation-analysis-for-mixed-models
# https://stats.stackexchange.com/questions/104692/comprehending-output-from-mediation-analysis-in-r
# https://towardsdatascience.com/doing-and-reporting-your-first-mediation-analysis-in-r-2fe423b92171

#libraries can mess up results
library(lme4)
library(lmerTest)

ESM_inner$attention <- as.factor(ESM_inner$attention)

fit.totaleffect <- lme4::lmer(wb_cw2 ~ attention + (1|PID)
                          , data=ESM_inner)
summary(fit.totaleffect) #estimate of attention = total effect; IV to DV line


fit.mediator<- lme4::lmer(valence_all_cw2 ~ attention + (1|PID) 
                    , data=ESM_inner)
summary(fit.mediator) #effect of IV onto mediator; IV to Mediator line


fit.dv <- lme4::lmer(wb_cw2 ~ attention + valence_all_cw2 + (1|PID)
                      , data=ESM_inner)
summary(fit.dv) #effect of mediator on DV; Mediator to DV line (ignore IV here)
#since IV is still sig here, we say it's a partial meditation as opposed to a complete mediation 


# install.packages("mediation")
# library("mediation")
detach("package:lmerTest", unload=TRUE)

results<-mediation::mediate(fit.mediator, fit.dv, treat='attention',
                            mediator='valence_all_cw2', na.action="na.omit")
summary(results)

#Interpretation - of the estimated 0.38 (Total Effect) increase in wellbeing that appears to be due to attention state, an estimated 0.16 (ACME) of that is actually a result of valence changes generated by attention state, while the remaining 0.23 (ADE) is from attention state itself
# proportion of the causal effect of attention state that is mediated by valence rather than direct effect is 0.41 (Prop.Mediated)

# The effect of attention state on wellbeing was partially mediated via objective valence. As Figure 1 illustrates, the coefficient between attention state and objective valence, and the coefficient between objective valence and wellbeing, was significant. A 95% confidence interval of the indirect effect was computed by using a quasi-Bayesian approximation using 1000 simulations. The indirect effect was (.25)*(.63) = .16, and the 95% confidence interval ranged from .11 to .21. Thus, the indirect effect was statistically significant (p<.001).


# ACME is an acronym for "Average Causal Mediation Effects" - is the estimated average increase in the dependent variable among the treatment group that arrives as a result of the mediators rather than 'directly' from the treatment
# ADE is an acronym for "Average Direct Effects"
# Total Effect is the sum of ACME and ADE





##graphing - need to manually input each part from above

#these are coefficients, like regression coefficients 

# install.packages("diagram")
library(diagram)

data <- c(0, "'.25***'", 0,
          0, 0, 0, 
          "'.63***'", "'.38***'", 0)
M<- matrix (nrow=3, ncol=3, byrow = TRUE, data=data)
plot<- plotmat (M, pos=c(1,2), 
                name= c( "Objective Valence","Attention State", "WellBeing"), 
                box.type = "rect", box.size = 0.12, box.prop=0.2,  curve=0,
                arr.width = .08, arr.type = "simple",
                main = "1-1-1 Multilevel Mediation Analysis")



```



```{r With covariates}

#add valence in first
model2a_fit <- lmer(formula = wb ~ 
                     activity+clarity_all_cw2+interesting_all_cw2+
                     attention+valence_all_cw2+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model2a_fit)
anova(model2a_fit, type=3)
confint(model2a_fit)

#effect size
modelcompare_fit <- lmer(formula = wb ~ 
                     activity+
                       clarity_all_cw2+
                       interesting_all_cw2+
                     # attention+
                       valence_all_cw2+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
# (r.squaredLR(model2a_fit)[1]) - (r.squaredLR(modelcompare_fit)[1])
round((r.squaredLR(model2a_fit)[1]) - (r.squaredLR(modelcompare_fit)[1]),4)



library(lme4)
library(lmerTest)

fit.totaleffect1 <- lme4::lmer(wb_cw2 ~ attention + (1|PID)
                        + activity+ clarity_all_cw2 + interesting_all_cw2 #covariate
                          , data=ESM_inner)
summary(fit.totaleffect1) #estimate of attention = total effect; IV to DV line; .19, p<.001
Anova(fit.totaleffect1, type=3)

fit.mediator1<- lme4::lmer(valence_all_cw2 ~ attention + (1|PID) 
                     +activity+ clarity_all_cw2+ interesting_all_cw2   #covariate
                    , data=ESM_inner)
summary(fit.mediator1) #effect of IV onto mediator; IV to Mediator line; .12, p<.001
Anova(fit.mediator1, type=3)

fit.dv1 <- lme4::lmer(wb_cw2 ~ attention + valence_all_cw2 + (1|PID)
                    + activity+ clarity_all_cw2 + interesting_all_cw2 #covariate
                      , data=ESM_inner)
summary(fit.dv1) #effect of mediator on DV; Mediator to DV line (ignore IV here); .60
#since IV is still sig here, we say it's a partial meditation as opposed to a complete mediation 
Anova(fit.dv1, type=3)


# install.packages("mediation")
# library("mediation")
detach("package:lmerTest", unload=TRUE)

results1<-mediation::mediate(fit.mediator1, fit.dv1, treat='attention',
                            mediator='valence_all_cw2', 
              covariates =  c("activity", "clarity_all_cw2", "interesting_all_cw2"),  #NEW
                            na.action="na.omit")
summary(results1)


#Interpretation - of the estimated 0.19 (Total Effect) increase in wellbeing that appears to be due to attention state, an estimated 0.07 (ACME) of that is actually a result of valence changes generated by attention state, while the remaining 0.12 (ADE) is from attention state itself
# proportion of the causal effect of attention state that is mediated by valence rather than direct effect is 0.37 (Prop.Mediated)

# The effect of attention state on wellbeing was partially mediated via objective valence. As Figure 1 illustrates, the coefficient between attention state and objective valence, and the coefficient between objective valence and wellbeing, was significant. A 95% confidence interval of the indirect effect was computed by using a quasi-Bayesian approximation using 1000 simulations. The indirect effect was (.12)*(.60) = .07, and the 95% confidence interval ranged from .05 to .11. Thus, the indirect effect was statistically significant (p<.001).


# ACME is an acronym for "Average Causal Mediation Effects" - is the estimated average increase in the dependent variable among the treatment group that arrives as a result of the mediators rather than 'directly' from the treatment
# ADE is an acronym for "Average Direct Effects"
# Total Effect is the sum of ACME and ADE





data <- c(0, "'.12***'", 0,
          0, 0, 0, 
          "'.60***'", "'.19***'", 0)
M<- matrix (nrow=3, ncol=3, byrow = TRUE, data=data)
plot<- plotmat (M, pos=c(1,2), 
                name= c( "Thought Valence","Attention State", "Mood"), 
                box.type = "rect", box.size = 0.12, box.prop=0.2,  curve=0,
                arr.width = .08, arr.type = "simple",
                main = "1-1-1 Multilevel Mediation Analysis with Covariates")


#comparing model fit
anova(model2a_fit, model2_fit)
```


##Model 3: Reactivity  Moderation
```{r Without Covariates}
# for interactions you just do that in the fixed part; leave the random part alone, ex. personality*(aware_cw2 + observe_cw2...) + (aware_cw2 | PID)...

#just valence*reaction as PV's 
model3_fit <- lmer(formula = wb ~
                     # activity+clarity_all_cw2+
            attention+
              valence_all_cw2*reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
summary(model3_fit)
anova(model3_fit, type=3)
confint(model3_fit)


#plotting interactions 
mod<-probe_interaction(model3_fit, #use w final model
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)

mod$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Valence*Reaction") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Valence \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")



# ##effect sizes 
# #of interaction
modelcomparison_fit <- lmer(formula = wb ~
            attention+
              valence_all_cw2+
              reaction_all_cw2+
              # valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
round(r.squaredLR(model3_fit)[1] - r.squaredLR(modelcomparison_fit)[1],4)

```

```{r With Covariates}

#just valence*reaction as PV's 
model3a_fit <- lmer(formula = wb ~
                     activity+clarity_all_cw2+
            attention+
              valence_all_cw2*reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
summary(model3a_fit)
anova(model3a_fit, type=3)
confint(model3a_fit)


#plotting interactions 
??probe_interaction

mod<-probe_interaction(model3a_fit, #use w final model
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2, 
                  interval = TRUE, #95% CI is default
                  modx.values = "plus-minus" #gets rid of mean 
                  # alpha = .05
                  )

mod$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  # ggtitle("Valence*Reaction") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Thought Valence")+
  ylab("WellBeing")+ 
  guides(fill = guide_legend(title = "Reactivity", 
                             override.aes = list(color = NA)
                             )) 


# ##effect sizes 
# #of interaction
modelcomparison_fit <- lmer(formula = wb ~
                  activity+
                    clarity_all_cw2+
                 attention+
              valence_all_cw2+
              reaction_all_cw2+
              # valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
round(r.squaredLR(model3a_fit)[1] - r.squaredLR(modelcomparison_fit)[1],4)



#comparison
anova(model3a_fit, model3_fit)


#post-hoc interaction
library(interactions)
# fiti <- lm(mpg ~ hp * wt, data = mtcars)
sim_slopes(model3a_fit, pred = valence_all_cw2, modx = reaction_all_cw2, jnplot = TRUE)



interact_plot(model3a_fit, pred = valence_all_cw2, modx = reaction_all_cw2, interval = TRUE,
                                modx.values = "plus-minus")


interact_plot(model3a_fit, pred = valence_all_cw2, modx = reaction_all_cw2,  plot.points = TRUE, modx.values = "plus-minus", interval=T)

```

```{r 3-way interaction}

model3b_fit <- lmer(formula = wb ~
                     activity+clarity_all_cw2+
              valence_all_cw2*reaction_all_cw2*attention+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
summary(model3b_fit)
anova(model3b_fit, type=3)
confint(model3b_fit)



mod_above<-probe_interaction(model3b_fit, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_above$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  # ggtitle("Above-Median ffmq_all Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) 
 # + xlab("Valence \n (higher = more positive)")+
 #  ylab("WellBeing \n (higher = greater wb)")
  
#

```


```{r MLM reporting package}

# https://cran.r-project.org/web/packages/sjPlot/vignettes/tab_mixed.html

# install.packages("sjPlot")
library(sjPlot)

tab_model(model3a_fit)

tab_model(model1a_fit, model2a_fit 
          # ,model3a_fit
          )

```



#MLM Assumptions

```{r Linearity}
##assumption setup:
# https://ademos.people.uic.edu/Chapter18.html
# install.packages("HLMdiag")
# install.packages("DHARMa")
library("HLMdiag")
library("DHARMa")


#assumption 1: linearity - assumption that your data follows a straight line (though the models can be expanded to handle curvilinear data).
# Graphically, plotting the model residuals (the difference between the observed value and the model-estimated value) vs the predictor is one simple way to test. If a pattern emerges (anything that looks non-random), a higher order term may need to be included or you may need to mathematically transform a predictor/response. 
#resid() calls for the residuals of the model, wb is DV- we're plotting the residuals vs observered DV 

# plot(resid(model1_fit),
#      ESM_inner$wb)
plot(resid(model1a_fit),
     ESM_inner$wb) 

# plot(resid(model2_fit),
#      ESM_inner$wb) 
plot(resid(model2a_fit),
     ESM_inner$wb) 

# plot(resid(model3_fit),
#      ESM_inner$wb) 
plot(resid(model3a_fit),
     ESM_inner$wb) 
```

```{r Variance}
#assumption 2: homogeneity of variance - variance of residuals is equal across groups (groups here = at level of individual)
# This procedure is a variation of “Levene’s Test”. Essentially, we’ll extract the residuals from the model, place them in our original table, take their absolute value, and then square them. Finally we’ll take a look at the ANOVA of the between subjects residuals.
#assumption is that the variance is not going to differ, so we would hope to see NO STATISTICAL DIFFERENCES in the following procedure (i.e. p>0.05) 

ESM_inner$model1_fit.Res<- residuals(model1_fit) #extracts the residuals and places them in a new column in our original data table
ESM_inner$Abs.model1_fit.Res <-abs(ESM_inner$model1_fit.Res) #creates a new column with the absolute value of the residuals
ESM_inner$model1_fit.Res2 <- ESM_inner$Abs.model1_fit.Res^2 #squares the absolute values of the residuals to provide the more robust estimate
Levene.model1_fit <- lm(model1_fit.Res2 ~ PID, data=ESM_inner) #ANOVA of the squared residuals
anova(Levene.model1_fit) #displays the results
# Since the p value is greater than 0.05, we can say that the variance of the residuals is equal and therefore the assumption of homoscedasticity is met 
plot(model1_fit) #creates a fitted vs residual plot - even spread across horizontal line? Not sure what this is meant to look like...
#there should also be a x axis x=0 line so it's quadrants
abline(v = 0) 



ESM_inner$model1a_fit.Res<- residuals(model1a_fit) 
ESM_inner$Abs.model1a_fit.Res <-abs(ESM_inner$model1a_fit.Res)
ESM_inner$model1a_fit.Res2 <- ESM_inner$Abs.model1a_fit.Res^2 
Levene.model1a_fit <- lm(model1a_fit.Res2 ~ PID, data=ESM_inner) 
anova(Levene.model1a_fit) 
# Since the p value is greater than 0.05, we can say that the variance of the residuals is equal and therefore the assumption of homoscedasticity is met 
plot(model1a_fit) 



# ESM_inner$model2_fit.Res<- residuals(model2_fit) 
# ESM_inner$Abs.model2_fit.Res <-abs(ESM_inner$model2_fit.Res)
# ESM_inner$model2_fit.Res2 <- ESM_inner$Abs.model2_fit.Res^2 
# Levene.model2_fit <- lm(model2_fit.Res2 ~ PID, data=ESM_inner) 
# anova(Levene.model2_fit) 
# # Since the p value is greater than 0.05, we can say that the variance of the residuals is equal and therefore the assumption of homoscedasticity is met 
# plot(model2_fit) 


ESM_inner$model2a_fit.Res<- residuals(model2a_fit) 
ESM_inner$Abs.model2a_fit.Res <-abs(ESM_inner$model2a_fit.Res)
ESM_inner$model2a_fit.Res2 <- ESM_inner$Abs.model2a_fit.Res^2 
Levene.model2a_fit <- lm(model2a_fit.Res2 ~ PID, data=ESM_inner) 
anova(Levene.model2a_fit) 
# Since the p value is greater than 0.05, we can say that the variance of the residuals is equal and therefore the assumption of homoscedasticity is met 
plot(model2a_fit) 

# 
# ESM_inner$model3_fit.Res<- residuals(model3_fit) 
# ESM_inner$Abs.model3_fit.Res <-abs(ESM_inner$model3_fit.Res)
# ESM_inner$model3_fit.Res2 <- ESM_inner$Abs.model3_fit.Res^2 
# Levene.model3_fit <- lm(model3_fit.Res2 ~ PID, data=ESM_inner) 
# anova(Levene.model3_fit) 
# # Since the p value is greater than 0.05, we can say that the variance of the residuals is equal and therefore the assumption of homoscedasticity is met 
# plot(model3_fit) 


ESM_inner$model3a_fit.Res<- residuals(model3a_fit) 
ESM_inner$Abs.model3a_fit.Res <-abs(ESM_inner$model3a_fit.Res)
ESM_inner$model3a_fit.Res2 <- ESM_inner$Abs.model3a_fit.Res^2 
Levene.model3a_fit <- lm(model3a_fit.Res2 ~ PID, data=ESM_inner) 
anova(Levene.model3a_fit) 
# Since the p value is greater than 0.05, we can say that the variance of the residuals is equal and therefore the assumption of homoscedasticity is met 
plot(model3a_fit) 

```


```{r Residuals}

##assumption 3: residuals are normally distributed - MLM assume that the residuals of the analysis ARE normally distributed (unlike regression models)
# QQ plots can provide an estimation of where the standardized residuals lie with respect to normal quantiles. Strong deviation from the provided line indicates that the residuals themselves are not normally distributed.
##qq plot (similar to a diagnostic plot provided by the lm function) for an estimation of the linearity of the residuals
require("lattice")
# qqmath(model1_fit, id=0.05) #id: identifies values that may be exerting undue influence on the model (i.e. outliers)
#id thing is too annoying let's just hide that...
# qqmath(model1_fit)
# There is some deviation from from the expected normal line towards the tails, but overall the line looks straight and therefore pretty normal and suggests that the assumption is not violated

qqmath(model1a_fit)
# qqmath(model2_fit)
qqmath(model2a_fit)
# qqmath(model3_fit)
qqmath(model3a_fit)


```

```{r Normality}
#assumption 4: normality of predictors and DV's 

# inspect ncol frequency distribution  - visual inspection shows these are normally distributed (hopefully)

#check predictors seem normally distributed 
#just do in chunks to make easier to interpret 
library(reshape2)

#wb
df <- ESM_inner %>%
  dplyr::select(
               wb_cw2, wb_cb2, 
                PID)
df.plots <- melt(df,id.vars='PID')
ggplot(df.plots, aes(value)) +
  facet_wrap(~variable, scales='free_x') + 
   theme(
      strip.text.x = element_text(
        size = 16, face = "bold"))+
  geom_histogram(binwidth = function(x) 2*IQR(x) / length(x)^(1/3))+
    # theme_classic() +
  theme(axis.title=element_text(size=14),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5))

hist(ESM_inner$wb)


#clarity
df <- ESM_inner %>%
  dplyr::select(
               clarity_all_cw2, clarity_all_cb2, 
                PID)
df.plots <- melt(df,id.vars='PID')
ggplot(df.plots, aes(value)) +
  facet_wrap(~variable, scales='free_x') + 
   theme(
      strip.text.x = element_text(
        size = 16, face = "bold"))+
  geom_histogram(binwidth = function(x) 2*IQR(x) / length(x)^(1/3))+
    # theme_classic() +
  theme(axis.title=element_text(size=14),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5))

hist(ESM_inner$clarity_all)


#valence
df <- ESM_inner %>%
  dplyr::select(
               valence_all_cw2, valence_all_cb2, 
                PID)
df.plots <- melt(df,id.vars='PID')
ggplot(df.plots, aes(value)) +
  facet_wrap(~variable, scales='free_x') + 
   theme(
      strip.text.x = element_text(
        size = 16, face = "bold"))+
  geom_histogram(binwidth = function(x) 2*IQR(x) / length(x)^(1/3))+
    # theme_classic() +
  theme(axis.title=element_text(size=14),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5))

hist(ESM_inner$valence_all)


#reaction
df <- ESM_inner %>%
  dplyr::select(
               reaction_all_cw2, reaction_all_cb2, 
                PID)
df.plots <- melt(df,id.vars='PID')
ggplot(df.plots, aes(value)) +
  facet_wrap(~variable, scales='free_x') + 
   theme(
      strip.text.x = element_text(
        size = 16, face = "bold"))+
  geom_histogram(binwidth = function(x) 2*IQR(x) / length(x)^(1/3))+
    # theme_classic() +
  theme(axis.title=element_text(size=14),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5))

hist(ESM_inner$reaction_all)


#interesting
df <- ESM_inner %>%
  dplyr::select(
               interesting_all_cw2, interesting_all_cb2, 
                PID)
df.plots <- melt(df,id.vars='PID')
ggplot(df.plots, aes(value)) +
  facet_wrap(~variable, scales='free_x') + 
   theme(
      strip.text.x = element_text(
        size = 16, face = "bold"))+
  geom_histogram(binwidth = function(x) 2*IQR(x) / length(x)^(1/3))+
    # theme_classic() +
  theme(axis.title=element_text(size=14),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5))

hist(ESM_inner$interesting_all)



```

```{r Extra; Multicollinearity}
##to test for multicollinearity amongs PV's, use VIF (variance inflation factor) function
# If VIF > 4.0 then I generally assume multicollinearity remove all those Predictor Variables before fitting them into my model

# car::vif(model1_fit) #not enough terms 
car::vif(model1a_fit)
# car::vif(model2_fit)
car::vif(model2a_fit)
# car::vif(model3_fit)
car::vif(model3a_fit)

```



************************

#Exploratory analyses

##Trait Mindfulness 3-way Moderations

I'm including just the main effects and a 3-way effect; not the 2-way interactions
- not sure if i need to include activity/clarity/attention here, but no errrors so far so leave I guess

--> make sure axis titles are correct, I think I need to find/replace them after the first batch

```{r FFMQ total}
model4a_fit <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+ffmq_all+
              valence_all_cw2:reaction_all_cw2:ffmq_all+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
summary(model4a_fit)
anova(model4a_fit, type=3)

###plotting 3-way is a pain

## Create above mean vs below MEDIAN dataframes

# mean(ESM_inner$ffmq_all)
ESM_inner_ffmq_all_above <- ESM_inner %>%
  filter(ffmq_all > median(ffmq_all))
length(unique(ESM_inner_ffmq_all_above$PID))
# ESM_inner_ffmq_all_above$ffmq_all
ESM_inner_ffmq_all_below <- ESM_inner %>%
  filter(ffmq_all < median(ffmq_all))
length(unique(ESM_inner_ffmq_all_below$PID))
# ESM_inner_ffmq_all_below$ffmq_all

## add in the 2-way interaction terms for each dataframe (by removing ffmq)
model4a_fit_above <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+
              valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner_ffmq_all_above,
                   REML = F)

model4a_fit_below <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+
              valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner_ffmq_all_below,
                   REML = F)

#side by side doesn't work with these
mod_above<-probe_interaction(model4a_fit_above, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_above$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Above-Median ffmq_all Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Valence \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")
  
#
mod_below<-probe_interaction(model4a_fit_below, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_below$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Below Median ffmq_all Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Valence \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")



#try attentional state*FFMQ
model_new_fit <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention*ffmq_all+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
summary(model_new_fit)
anova(model_new_fit, type=3)

```

```{r FFMQ Total minus Observing}
model4b_fit <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+ffmq_no_observe+
              valence_all_cw2:reaction_all_cw2:ffmq_no_observe+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
summary(model4b_fit)
anova(model4b_fit, type=3)

###plotting 3-way is a pain

## Create above mean vs below MEDIAN dataframes

# mean(ESM_inner$ffmq_no_observe)
ESM_inner_ffmq_no_observe_above <- ESM_inner %>%
  filter(ffmq_no_observe > median(ffmq_no_observe))
length(unique(ESM_inner_ffmq_no_observe_above$PID))
# ESM_inner_ffmq_no_observe_above$ffmq_no_observe
ESM_inner_ffmq_no_observe_below <- ESM_inner %>%
  filter(ffmq_no_observe < median(ffmq_no_observe))
length(unique(ESM_inner_ffmq_no_observe_below$PID))
# ESM_inner_ffmq_no_observe_below$ffmq_no_observe

## add in the 2-way interaction terms for each dataframe (by removing ffmq)
model4b_fit_above <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+
              valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner_ffmq_no_observe_above,
                   REML = F)

model4b_fit_below <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+
              valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner_ffmq_no_observe_below,
                   REML = F)

#side by side doesn't work with these
mod_above<-probe_interaction(model4b_fit_above, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_above$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Above-Median ffmq_no_observe Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Reaction \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")
  
#
mod_below<-probe_interaction(model4b_fit_below, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_below$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Below Median ffmq_no_observe Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Reaction \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")


#try attentional state*FFMQ
model_new_fit <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention*ffmq_no_observe+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
summary(model_new_fit)
anova(model_new_fit, type=3)


```

```{r FFMQ Awareness}
model4c_fit <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+awareness+
              valence_all_cw2:reaction_all_cw2:awareness+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
summary(model4c_fit)
anova(model4c_fit, type=3)

###plotting 3-way is a pain

## Create above mean vs below MEDIAN dataframes

# mean(ESM_inner$awareness)
ESM_inner_awareness_above <- ESM_inner %>%
  filter(awareness > median(awareness))
length(unique(ESM_inner_awareness_above$PID))
# ESM_inner_awareness_above$awareness
ESM_inner_awareness_below <- ESM_inner %>%
  filter(awareness < median(awareness))
length(unique(ESM_inner_awareness_below$PID))
# ESM_inner_awareness_below$awareness

## add in the 2-way interaction terms for each dataframe (by removing ffmq)
model4c_fit_above <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+
              valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner_awareness_above,
                   REML = F)

model4c_fit_below <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+
              valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner_awareness_below,
                   REML = F)

#side by side doesn't work with these
mod_above<-probe_interaction(model4c_fit_above, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_above$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Above-Median awareness Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Reaction \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")
  
#
mod_below<-probe_interaction(model4c_fit_below, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_below$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Below Median awareness Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Reaction \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")


#try attentional state*FFMQ
model_new_fit <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention*awareness+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
summary(model_new_fit)
anova(model_new_fit, type=3)


```

```{r Describe}

model4d_fit <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+describe+
              valence_all_cw2:reaction_all_cw2:describe+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
summary(model4d_fit)
anova(model4d_fit, type=3)

###plotting 3-way is a pain

## Create above mean vs below MEDIAN dataframes

# mean(ESM_inner$describe)
ESM_inner_describe_above <- ESM_inner %>%
  filter(describe > median(describe))
length(unique(ESM_inner_describe_above$PID))
# ESM_inner_describe_above$describe
ESM_inner_describe_below <- ESM_inner %>%
  filter(describe < median(describe))
length(unique(ESM_inner_describe_below$PID))
# ESM_inner_describe_below$describe

## add in the 2-way interaction terms for each dataframe (by removing ffmq)
model4d_fit_above <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+
              valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner_describe_above,
                   REML = F)

model4d_fit_below <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+
              valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner_describe_below,
                   REML = F)

#side by side doesn't work with these
mod_above<-probe_interaction(model4d_fit_above, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_above$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Above-Median describe Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Reaction \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")
  
#
mod_below<-probe_interaction(model4d_fit_below, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_below$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Below Median describe Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Reaction \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")


```

```{r Observing}
model4e_fit <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+observing+
              valence_all_cw2:reaction_all_cw2:observing+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
summary(model4e_fit)
anova(model4e_fit, type=3)

###plotting 3-way is a pain

## Create above mean vs below MEDIAN dataframes

# mean(ESM_inner$observing)
ESM_inner_observing_above <- ESM_inner %>%
  filter(observing > median(observing))
length(unique(ESM_inner_observing_above$PID))
# ESM_inner_observing_above$observing
ESM_inner_observing_below <- ESM_inner %>%
  filter(observing < median(observing))
length(unique(ESM_inner_observing_below$PID))
# ESM_inner_observing_below$observing

## add in the 2-way interaction terms for each dataframe (by removing ffmq)
model4e_fit_above <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+
              valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner_observing_above,
                   REML = F)

model4e_fit_below <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+
              valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner_observing_below,
                   REML = F)

#side by side doesn't work with these
mod_above<-probe_interaction(model4e_fit_above, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_above$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Above-Median observing Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Reaction \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")
  
#
mod_below<-probe_interaction(model4e_fit_below, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_below$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Below Median observing Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Reaction \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")


```

```{r Nonjudging}
model4f_fit <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+nonjudging+
              valence_all_cw2:reaction_all_cw2:nonjudging+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
summary(model4f_fit)
anova(model4f_fit, type=3)

###plotting 3-way is a pain

## Create above mean vs below MEDIAN dataframes

# mean(ESM_inner$nonjudging)
ESM_inner_nonjudging_above <- ESM_inner %>%
  filter(nonjudging > median(nonjudging))
length(unique(ESM_inner_nonjudging_above$PID))
# ESM_inner_nonjudging_above$nonjudging
ESM_inner_nonjudging_below <- ESM_inner %>%
  filter(nonjudging < median(nonjudging))
length(unique(ESM_inner_nonjudging_below$PID))
# ESM_inner_nonjudging_below$nonjudging

## add in the 2-way interaction terms for each dataframe (by removing ffmq)
model4f_fit_above <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+
              valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner_nonjudging_above,
                   REML = F)

model4f_fit_below <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+
              valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner_nonjudging_below,
                   REML = F)

#side by side doesn't work with these
mod_above<-probe_interaction(model4f_fit_above, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_above$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Above-Median nonjudging Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Reaction \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")
  
#
mod_below<-probe_interaction(model4f_fit_below, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_below$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Below Median nonjudging Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Reaction \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")

```

```{r Nonreactivity}
model4g_fit <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+nonreactivity+
              valence_all_cw2:reaction_all_cw2:nonreactivity+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
summary(model4g_fit)
anova(model4g_fit, type=3)

###plotting 3-way is a pain

## Create above mean vs below MEDIAN dataframes

# mean(ESM_inner$nonreactivity)
ESM_inner_nonreactivity_above <- ESM_inner %>%
  filter(nonreactivity > median(nonreactivity))
length(unique(ESM_inner_nonreactivity_above$PID))
# ESM_inner_nonreactivity_above$nonreactivity
ESM_inner_nonreactivity_below <- ESM_inner %>%
  filter(nonreactivity < median(nonreactivity))
length(unique(ESM_inner_nonreactivity_below$PID))
# ESM_inner_nonreactivity_below$nonreactivity

## add in the 2-way interaction terms for each dataframe (by removing ffmq)
model4g_fit_above <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+
              valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner_nonreactivity_above,
                   REML = F)

model4g_fit_below <- lmer(formula = wb ~
            activity+
            clarity_all_cw2+
            attention+
             valence_all_cw2+reaction_all_cw2+
              valence_all_cw2:reaction_all_cw2+
                 (1|PID),
                    data=ESM_inner_nonreactivity_below,
                   REML = F)

#side by side doesn't work with these
mod_above<-probe_interaction(model4g_fit_above, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_above$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Above-Median nonreactivity Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Reaction \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")
  
#
mod_below<-probe_interaction(model4g_fit_below, 
                  pred = valence_all_cw2,
                  modx = reaction_all_cw2,
                  alpha = .05)
mod_below$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Below Median nonreactivity Score") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Reaction \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")

```


#Other Exploratory Analyses

```{r Interestingness Moderation}

model5_fit <- lmer(formula = wb ~
                     activity+clarity_all_cw2+
            attention+ 
              valence_all_cw2*reaction_all_cw2+
              valence_all_cw2*interesting_all_cw2+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
summary(model5_fit)
anova(model5_fit, type=3)


mod<-probe_interaction(model5_fit, #use w final model
                  pred = valence_all_cw2,
                  modx = interesting_all_cw2,
                  alpha = .05)

mod$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Valence*Interestingness") +
    scale_x_continuous(limits=c(-3,3),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Valence \n (higher = more positive)")+
  ylab("WellBeing \n (higher = greater wb)")



ggplot(data=ESM_inner, aes(x=interesting_all_cw2,
                            y=wb_cw2, group=factor(PID), colour="gray"), legend=FALSE)+
  geom_smooth(method=lm, se=FALSE, fullrange=FALSE, lty=1, size=.05, color="gray40") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="blue") +
  xlab("Awareness") + ylab("Wellbeing") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Within-Person Association of Interestingness and Wellbeing") +
    # scale_x_continuous(limits=c(1,5),   #check range of PV
    #                  breaks = c(1,2,3,4,5)
    #                  ) +
    #       scale_y_continuous(limits=c(-3,3),
    #                  breaks = c(-3, -2, -1, 0, 1, 2, 3)
    #                  ) +
  geom_hline(yintercept=0,
               # color="red",
               size=1)+
  xlab("Interestingness \n (higher = more interesting)")+
  ylab("WellBeing \n (higher = greater wb)")



# ##effect sizes 
# #of main effect of interestingness
model_comparison_fit <- lmer(formula = wb ~
                     activity+
                       clarity_all_cw2+
            attention+
              valence_all_cw2+
              reaction_all_cw2+
               valence_all_cw2:reaction_all_cw2+
                interesting_all_cw2+
              # valence_all_cw2:interesting_all_cw2+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)

round(r.squaredLR(model5_fit)[1] - r.squaredLR(model_comparison_fit)[1],4)

```

#Interesting as mediator
```{r Without Covariates}

#add interesting in first
model2_fit <- lmer(formula = wb ~ 
                     attention+interesting_all_cw2+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model2_fit)
anova(model2_fit, type=3)
# confint(model2_fit)

#effect size
modelcompare_fit <- lmer(formula = wb ~ 
                     attention+
                       # interesting_all_cw2+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
round((r.squaredLR(model2_fit)[1]) - (r.squaredLR(modelcompare_fit)[1]),4)

#comparing model fit
# anova(model2_fit, model1_fit)


# #plot within-person differences of main effects
# ##repeat this to ensure direction of effects is as expected

ggplot(data=ESM_inner, aes(x=interesting_all_cw2,
                            y=wb_cw2, group=factor(PID), colour="gray"), legend=FALSE)+
  geom_smooth(method=lm, se=FALSE, fullrange=FALSE, lty=1, size=.05, color="gray40") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="blue") +
  xlab("Objective Valence") + ylab("Wellbeing") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Within-Person Association of Interestingness and Wellbeing") +
    # scale_x_continuous(limits=c(1,5),   #check range of PV
    #                  breaks = c(1,2,3,4,5)
    #                  ) +
    #       scale_y_continuous(limits=c(-3,3),
    #                  breaks = c(-3, -2, -1, 0, 1, 2, 3)
    #                  ) +
  geom_hline(yintercept=0,
               # color="red",
               size=1)+
  xlab("Interesting \n (higher = more interesting)")+
  ylab("WellBeing \n (higher = greater wb)")


##mediation 

#There is a lot of discussion / uncertainty online about how to properly do a mediation MLM. Just say that I use the Tingley, Dustin, et al, 2014, "Mediation" R package; and that this is a "1-1-1" mediation (hence the cw2 for each thing). The output is similar, though not exactly the same, without the cw2. 

# https://cran.r-project.org/web/packages/mediation/vignettes/mediation.pdf
# https://stats.stackexchange.com/questions/491503/mediation-analysis-for-mixed-models
# https://stats.stackexchange.com/questions/104692/comprehending-output-from-mediation-analysis-in-r
# https://towardsdatascience.com/doing-and-reporting-your-first-mediation-analysis-in-r-2fe423b92171

#libraries can mess up results
library(lme4)
library(lmerTest)

ESM_inner$attention <- as.factor(ESM_inner$attention)

fit.totaleffect <- lmer(wb_cw2 ~ attention + (1|PID)
                          , data=ESM_inner)
summary(fit.totaleffect) #estimate of attention = total effect; IV to DV line


fit.mediator<- lmer(interesting_all_cw2 ~ attention + (1|PID) 
                    , data=ESM_inner)
summary(fit.mediator) #effect of IV onto mediator; IV to Mediator line


fit.dv <- lmer(wb_cw2 ~ attention + interesting_all_cw2 + (1|PID)
                      , data=ESM_inner)
summary(fit.dv) #effect of mediator on DV; Mediator to DV line (ignore IV here)
#since IV is still sig here, we say it's a partial meditation as opposed to a complete mediation 


# install.packages("mediation")
# library("mediation")
detach("package:lmerTest", unload=TRUE)

# results<-mediation::mediate(fit.mediator, fit.dv, treat='attention',
                            # mediator='interesting_all_cw2', na.action="na.omit")
# summary(results)

##NOT UPDATED TEXT:
  
#Interpretation - of the estimated 0.38 (Total Effect) increase in wellbeing that appears to be due to attention state, an estimated 0.16 (ACME) of that is actually a result of valence changes generated by attention state, while the remaining 0.23 (ADE) is from attention state itself
# proportion of the causal effect of attention state that is mediated by valence rather than direct effect is 0.41 (Prop.Mediated)

# The effect of attention state on wellbeing was partially mediated via objective valence. As Figure 1 illustrates, the coefficient between attention state and objective valence, and the coefficient between objective valence and wellbeing, was significant. A 95% confidence interval of the indirect effect was computed by using a quasi-Bayesian approximation using 1000 simulations. The indirect effect was (.25)*(.63) = .16, and the 95% confidence interval ranged from .11 to .21. Thus, the indirect effect was statistically significant (p<.001).



##graphing - need to manually input each part from above

#these are coefficients, like regression coefficients 

# install.packages("diagram")
library(diagram)

data <- c(0, "'.13**'", 0,
          0, 0, 0, 
          "'.20***'", "'.38***'", 0)
M<- matrix (nrow=3, ncol=3, byrow = TRUE, data=data)
plot<- plotmat (M, pos=c(1,2), 
                name= c( "Interestingness","Attention State", "WellBeing"), 
                box.type = "rect", box.size = 0.12, box.prop=0.2,  curve=0,
                arr.width = .08, arr.type = "simple",
                main = "1-1-1 Multilevel Mediation Analysis")



```

```{r With covariates}

#add valence in first
model2a_fit <- lmer(formula = wb ~ 
                     activity+clarity_all_cw2+
                     attention+interesting_all_cw2+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model2a_fit)
anova(model2a_fit, type=3)
# confint(model2a_fit)

#effect size
modelcompare_fit <- lmer(formula = wb ~ 
                     # activity+
                       clarity_all_cw2+
                     attention+
                       interesting_all_cw2+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
round((r.squaredLR(model2a_fit)[1]) - (r.squaredLR(modelcompare_fit)[1]),4)



library(lme4)
library(lmerTest)

fit.totaleffect1 <- lme4::lmer(wb_cw2 ~ attention + (1|PID)
                        + activity+ clarity_all_cw2 #covariate
                          , data=ESM_inner)
summary(fit.totaleffect1) #estimate of attention = total effect; IV to DV line; .39, p<.001
Anova(fit.totaleffect1, type=3)

fit.mediator1<- lme4::lmer(interesting_all_cw2 ~ attention + (1|PID) 
                     +activity+ clarity_all_cw2   #covariate
                    , data=ESM_inner)
summary(fit.mediator1) #effect of IV onto mediator; IV to Mediator line; .09, p=.05
Anova(fit.mediator1, type=3)

fit.dv1 <- lme4::lmer(wb_cw2 ~ attention + interesting_all_cw2 + (1|PID)
                    + activity+ clarity_all_cw2  #covariate
                      , data=ESM_inner)
summary(fit.dv1) #effect of mediator on DV; Mediator to DV line (ignore IV here); .17, p<.001
#since IV is still sig here, we say it's a partial meditation as opposed to a complete mediation 
Anova(fit.dv1, type=3) 



# install.packages("mediation")
# library("mediation")
detach("package:lmerTest", unload=TRUE)

# results1<-mediation::mediate(fit.mediator1, fit.dv1, treat='attention',
#                             mediator='interesting_all_cw2', na.action="na.omit")
# summary(results1)



data <- c(0, "'.09'", 0,
          0, 0, 0, 
          "'.17***'", "'.39***'", 0)
M<- matrix (nrow=3, ncol=3, byrow = TRUE, data=data)
plot<- plotmat (M, pos=c(1,2), 
                name= c( "Interestingness","Attention State", "WellBeing"), 
                box.type = "rect", box.size = 0.12, box.prop=0.2,  curve=0,
                arr.width = .08, arr.type = "simple",
                main = "1-1-1 Multilevel Mediation Analysis with Covariates")


#comparing model fit
anova(model2a_fit, model2_fit)
```



#clarity as mediator
```{r Without Covariates}

#add clarity in first
model2_fit <- lmer(formula = wb ~ 
                     attention+clarity_all_cw2+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model2_fit)
anova(model2_fit, type=3)
# confint(model2_fit)

#effect size
modelcompare_fit <- lmer(formula = wb ~ 
                     # attention+
                       clarity_all_cw2+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
round((r.squaredLR(model2_fit)[1]) - (r.squaredLR(modelcompare_fit)[1]),4)

#comparing model fit
# anova(model2_fit, model1_fit)


# #plot within-person differences of main effects
# ##repeat this to ensure direction of effects is as expected

ggplot(data=ESM_inner, aes(x=clarity_all_cw2,
                            y=wb_cw2, group=factor(PID), colour="gray"), legend=FALSE)+
  geom_smooth(method=lm, se=FALSE, fullrange=FALSE, lty=1, size=.05, color="gray40") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="blue") +
  xlab("Objective Valence") + ylab("Wellbeing") +
  theme_classic() +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Within-Person Association of clarity and Wellbeing") +
    # scale_x_continuous(limits=c(1,5),   #check range of PV
    #                  breaks = c(1,2,3,4,5)
    #                  ) +
    #       scale_y_continuous(limits=c(-3,3),
    #                  breaks = c(-3, -2, -1, 0, 1, 2, 3)
    #                  ) +
  geom_hline(yintercept=0,
               # color="red",
               size=1)+
  xlab("clarity \n (higher = more clarity)")+
  ylab("WellBeing \n (higher = greater wb)")


##mediation 

#There is a lot of discussion / uncertainty online about how to properly do a mediation MLM. Just say that I use the Tingley, Dustin, et al, 2014, "Mediation" R package; and that this is a "1-1-1" mediation (hence the cw2 for each thing). The output is similar, though not exactly the same, without the cw2. 

# https://cran.r-project.org/web/packages/mediation/vignettes/mediation.pdf
# https://stats.stackexchange.com/questions/491503/mediation-analysis-for-mixed-models
# https://stats.stackexchange.com/questions/104692/comprehending-output-from-mediation-analysis-in-r
# https://towardsdatascience.com/doing-and-reporting-your-first-mediation-analysis-in-r-2fe423b92171

#libraries can mess up results
library(lme4)
library(lmerTest)

ESM_inner$attention <- as.factor(ESM_inner$attention)

fit.totaleffect <- lmer(wb_cw2 ~ attention + (1|PID)
                          , data=ESM_inner)
summary(fit.totaleffect) #estimate of attention = total effect; IV to DV line


fit.mediator<- lmer(clarity_all_cw2 ~ attention + (1|PID) 
                    , data=ESM_inner)
summary(fit.mediator) #effect of IV onto mediator; IV to Mediator line


fit.dv <- lmer(wb_cw2 ~ attention + clarity_all_cw2 + (1|PID)
                      , data=ESM_inner)
summary(fit.dv) #effect of mediator on DV; Mediator to DV line (ignore IV here)
#since IV is still sig here, we say it's a partial meditation as opposed to a complete mediation 


# install.packages("mediation")
# library("mediation")
detach("package:lmerTest", unload=TRUE)

# results2<-mediation::mediate(fit.mediator, fit.dv, treat='attention',
#                             mediator='clarity_all_cw2', na.action="na.omit")
# summary(results2)

##NOT UPDATED TEXT:
  
#Interpretation - of the estimated 0.38 (Total Effect) increase in wellbeing that appears to be due to attention state, an estimated 0.16 (ACME) of that is actually a result of valence changes generated by attention state, while the remaining 0.23 (ADE) is from attention state itself
# proportion of the causal effect of attention state that is mediated by valence rather than direct effect is 0.41 (Prop.Mediated)

# The effect of attention state on wellbeing was partially mediated via objective valence. As Figure 1 illustrates, the coefficient between attention state and objective valence, and the coefficient between objective valence and wellbeing, was significant. A 95% confidence interval of the indirect effect was computed by using a quasi-Bayesian approximation using 1000 simulations. The indirect effect was (.25)*(.63) = .16, and the 95% confidence interval ranged from .11 to .21. Thus, the indirect effect was statistically significant (p<.001).



##graphing - need to manually input each part from above

#these are coefficients, like regression coefficients 

# install.packages("diagram")
# library(diagram)
# 
# data <- c(0, "'.13**'", 0,
#           0, 0, 0, 
#           "'.20***'", "'.38***'", 0)
# M<- matrix (nrow=3, ncol=3, byrow = TRUE, data=data)
# plot<- plotmat (M, pos=c(1,2), 
#                 name= c( "clarityness","Attention State", "WellBeing"), 
#                 box.type = "rect", box.size = 0.12, box.prop=0.2,  curve=0,
#                 arr.width = .08, arr.type = "simple",
#                 main = "1-1-1 Multilevel Mediation Analysis")



```

```{r With covariates}

#add valence in first
model2a_fit <- lmer(formula = wb ~ 
                     activity+clarity_all_cw2+
                     attention+clarity_all_cw2+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model2a_fit)
anova(model2a_fit, type=3)
# confint(model2a_fit)

#effect size
modelcompare_fit <- lmer(formula = wb ~ 
                     # activity+
                       clarity_all_cw2+
                     attention+
                       clarity_all_cw2+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
round((r.squaredLR(model2a_fit)[1]) - (r.squaredLR(modelcompare_fit)[1]),4)



library(lme4)
library(lmerTest)

fit.totaleffect1 <- lme4::lmer(wb_cw2 ~ attention + (1|PID)
                        + activity+ clarity_all_cw2 #covariate
                          , data=ESM_inner)
summary(fit.totaleffect1) #estimate of attention = total effect; IV to DV line; .39, p<.001
Anova(fit.totaleffect1, type=3)

fit.mediator1<- lme4::lmer(clarity_all_cw2 ~ attention + (1|PID) 
                     +activity+ clarity_all_cw2   #covariate
                    , data=ESM_inner)
summary(fit.mediator1) #effect of IV onto mediator; IV to Mediator line; .09, p=.05
Anova(fit.mediator1, type=3)

fit.dv1 <- lme4::lmer(wb_cw2 ~ attention + clarity_all_cw2 + (1|PID)
                    + activity+ clarity_all_cw2  #covariate
                      , data=ESM_inner)
summary(fit.dv1) #effect of mediator on DV; Mediator to DV line (ignore IV here); .17, p<.001
#since IV is still sig here, we say it's a partial meditation as opposed to a complete mediation 
Anova(fit.dv1, type=3) 



# install.packages("mediation")
# library("mediation")
detach("package:lmerTest", unload=TRUE)

results1<-mediation::mediate(fit.mediator1, fit.dv1, treat='attention',
                            mediator='clarity_all_cw2', na.action="na.omit")
summary(results1)



data <- c(0, "'.09'", 0,
          0, 0, 0, 
          "'.17***'", "'.39***'", 0)
M<- matrix (nrow=3, ncol=3, byrow = TRUE, data=data)
plot<- plotmat (M, pos=c(1,2), 
                name= c( "clarityness","Attention State", "WellBeing"), 
                box.type = "rect", box.size = 0.12, box.prop=0.2,  curve=0,
                arr.width = .08, arr.type = "simple",
                main = "1-1-1 Multilevel Mediation Analysis with Covariates")


#comparing model fit
anova(model2a_fit, model2_fit)
```




#Others
```{r Activity by Attention State}
table <- table(ESM$activity, ESM$attention)
table
chisq.test(table, 
           simulate.p.value = F)

chisq.posthoc.test::chisq.posthoc.test(table,
                   method = "bonferroni",
                   round = 3,
                   simulate.p.value=F)


table1::label(ESM$activity) <- "Activity"
table1::label(ESM$attention) <- "Attention State"

table1::table1(~activity | attention
               , data = ESM) 


###NOTE I do these backwards since i already use activity as a covariate early on...

#attention state model
model1ACT_fit <- lmer(formula = wb ~
                     # activity+ 
                attention+
                  # interesting_all_cw2+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F)
anova(model1ACT_fit, type=3)
anova(model1_fit, model1ACT_fit)

#valence mediation model
model2aACT_fit <- lmer(formula = wb ~
                      # activity+
                clarity_all_cw2+
            attention+
              valence_all_cw2+
               # interesting_all_cw2+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
anova(model2aACT_fit, type=3)
anova(model2a_fit, model2aACT_fit)

#valence*reaction model
model3ACT_fit <- lmer(formula = wb ~
                     # activity+
                clarity_all_cw2+
            attention+
              valence_all_cw2*reaction_all_cw2+
                 # interesting_all_cw2+
                 (1|PID),
                    data=ESM_inner,
                   REML = F)
anova(model3ACT_fit, type=3)
anova(model3_fit, model3ACT_fit)


```


```{r Valence to Reactivity with Attention State as Moderator}
# -valence —> Reactivity, with attention state as a moderator 

#alreadydo this way above
# #had trouble plotting as is, so need to dummy code attention first
# ESM_inner_test <- ESM_inner
# ESM_inner_test$attention <- ifelse(ESM_inner_test$attention == 'Present', 1, 0)
# #present = 1


##without covariates
model6_fit <- lmer(formula = reaction_all ~
                     # activity+clarity_all_cw2+
              valence_all_cw2*attention+
                 (1|PID),
                    data=ESM_inner,
                   REML = F, na.action = "na.omit")
summary(model6_fit)
anova(model6_fit, type=3)

#plot
mod<-probe_interaction(model6_fit, 
                  pred = valence_all_cw2,
                  modx = attention,
                  alpha = .05)
mod$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Valence*Attention on Reaction \n (1 = Present, 0 = Not Present)") +
    # scale_x_continuous(limits=c(-3,3),
    #                  ) +
          scale_y_continuous(limits=c(1,7)
                     ) +
  xlab("Valence (person mean centered) \n (higher = more positive)")+
  ylab("Reactivity \n (higher = more Reactive)")




# ##effect sizes 
# #of interaction
model_comparison_fit <- lmer(formula = reaction_all ~
               valence_all_cw2+
               attention+
              # valence_all_cw2:attention+
                 (1|PID),
                    data=ESM_inner,
                   REML = F, na.action = "na.omit")

round(r.squaredLR(model6_fit)[1] - r.squaredLR(model_comparison_fit)[1],4)



###

ESM_inner_1 <- ESM_inner %>%
  mutate(attention = as.factor(attention))

ESM_inner_1$attention <- factor(ESM_inner_1$attention, ordered=F)
  
##with covariates
model6a_fit <- lme4::lmer(formula = reaction_all ~
                     activity+clarity_all_cw2+
              valence_all_cw2*attention+
                 (1|PID),
                    data=ESM_inner_1,
                   REML = F, na.action = "na.omit")
summary(model6a_fit)
Anova(model6a_fit, type=3)

#plot
mod<-probe_interaction(model6a_fit, #use w final model
                  pred = valence_all_cw2,
                  modx = attention, center=T,
                  interval = TRUE #95% CI is default
                  # modx.values = "plus-minus" #gets rid of mean 
                  # alpha = .05
                  )

mod$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
   # ggtitle("Valence*Attention on Reaction \n (1 = Present, 0 = Not Present)") +
    # scale_x_continuous(limits=c(-3,3),
    #                  ) +
          scale_y_continuous(limits=c(-2,2)
                     ) +
  xlab("Thought Valence")+
  ylab("Reactivity")+
  guides(fill = guide_legend(title = "Attention State", 
                             override.aes = list(color = NA)
                             )) 



interact_plot(model6a_fit, pred = valence_all_cw2,
              modx = attention,modx.values = c(-1,1))


interact_plot(model6a_fit, pred = valence_all_cw2, modx = attention)
# 
interactions::sim_slopes(model6a_fit, pred = valence_all_cw2, modx = attention, jnplot = TRUE
           )


reghelper::simple_slopes(model6a_fit)



# 
# probe_interaction(model6a_fit, pred = valence_all_cw2, modx = attention)
# 
# cat_plot(model6a_fit, pred = valence_all_cw2, modx = attention)
# 
# install.packages("reghelper")
# library(reghelper)
# sig_regions(model = model6a_fit)


install.packages("SIMPLE.REGRESSION")
library(SIMPLE.REGRESSION)
REGIONS_OF_SIGNIFICANCE(model = model6a_fit)



# ##effect sizes 
# #of interaction
model_comparison_fit <- lmer(formula = reaction_all ~
                     activity+
                       clarity_all_cw2+
              valence_all_cw2+
                attention+
              # valence_all_cw2:attention+
                 (1|PID),
                    data=ESM_inner,
                   REML = F, na.action = "na.omit")

round(r.squaredLR(model6a_fit)[1] - r.squaredLR(model_comparison_fit)[1],4)


tab_model(model6a_fit)




###model comparison
anova(model6_fit, model6a_fit)

```

```{r OLS Regressions}

#make attention a numeric thing
ESM_inner_test <- ESM_inner
ESM_inner_test$attention <- as.numeric(ESM_inner_test$attention)

ESM_inner_test <- ESM_inner_test %>% group_by(PID) %>% 
  mutate(
    attention_mean2 = mean(attention, na.rm = T)
  ) %>% ungroup() %>% 
  mutate(
    #these are grand mean centered variables
    attention_c2 = scale(attention, center = T, scale = F),
    #these are within-person centered variables
         attention_cw2 = attention-attention_mean2,
    #these are between-person centered variables 
         attention_cb2 = attention_c2-attention_cw2)


lmodel <- lm(wb_cw2 ~ activity, data = ESM_inner_test)
lmodel$coefficients
summary(lmodel)


#testing
lmodel <- lm(wb_cw2 ~ attention, data = ESM_inner_test)
lmodel$coefficients
summary(lmodel)

#scaling like this doesn't make a differece
# ESM_inner_test$wb_cw2 <- ESM_inner_test$wb_cw2*100

#making it a repeated regression doesn't help
test<-aov(data=ESM_inner_test,
          wb_cw2~
            attention+
            Error(PID/(attention)))
summary(test)
summary(lm(test))

#making it a MLM doesn't help
model00_fit <- lmer(formula =
                      wb_cw2 ~ attention+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) 
summary(model00_fit)
anova(model00_fit, type=3)
round(r.squaredLR(model00_fit)[1],4)


lmodel <- lm(wb_cw2 ~ attention_cw2, data = ESM_inner_test)
lmodel$coefficients
summary(lmodel)


lmodel <- lm(wb_cw2 ~ attention, data = ESM_inner_test)
lmodel$coefficients
summary(lmodel)


## clarity is similar to attention; putting it as cw2 doesn't impact R2 much
# lmodel <- lm(wb_cw2 ~ clarity, data = ESM_inner)
# lmodel$coefficients
# summary(lmodel)


lmodel <- lm(wb_cw2 ~ attention+activity, data = ESM_inner)
lmodel$coefficients
summary(lmodel)


# simple regression - 
lmodel <- lm(wb_cw2 ~ attention, data = ESM_inner)
lmodel$coefficients
summary(lmodel)
emmeans(lmodel, list(pairwise ~ Attention), adjust = "tukey")

lmodel <- lm(wb_cw2 ~ activity, data = ESM_inner)
lmodel$coefficients
summary(lmodel)
emmeans(lmodel, list(pairwise ~ activity), adjust = "tukey")



lmodel <- lm(wb_cb2 ~ attention, data = ESM_inner)
lmodel$coefficients
summary(lmodel)
emmeans(lmodel, list(pairwise ~ Attention), adjust = "tukey")

```


```{r Attention Moderators on Wellbeing}
#done by playing around over and over with attention*XX
#just checking trait moderators on attention 

# ESM$ffmq_all,
# ESM$ffmq_no_observe,
# ESM$awareness,
# ESM$describe,
# ESM$observing,
# ESM$nonjudging,
# ESM$nonreactivity,

# ESM$openness,
# ESM$conscientiousness,
# ESM$extraversion,
# ESM$agreeableness,
# ESM$neuroticism,

# ESM$age
# ESM$ethnoracial
# ESM$sex_at_birth
# ESM$sexual_orientation_2
# ESM$ses_ladder



model1a1_fit <- lmer(formula = wb ~
                     activity+clarity_all_cw2+interesting_all_cw2+ #as a covariate
                attention*age+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) #must set this to F to return loglik and AIC
summary(model1a1_fit)
anova(model1a1_fit, type=3)
confint(model1a1_fit)

tab_model(model1a1_fit)

#effect size 
#change # for each variable
modelcompare_fit <- lmer(formula = wb ~
                     activity+
                       clarity_all_cw2+
                       interesting_all_cw2+
                attention+
                  age+
                  # attention:age+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F)
round((r.squaredLR(model1a1_fit)[1]) - (r.squaredLR(modelcompare_fit)[1]),3)
??r.squaredLR

#plot
mod<-probe_interaction(model1a1_fit, #use w final model
                  pred = age,
                  modx = attention,
                  alpha = .05)
mod$interactplot +
  theme(axis.title=element_text(size=18),
        axis.text=element_text(size=14),
        plot.title=element_text(size=18, hjust=.5)) +
  ggtitle("Attention*Age") +
    scale_x_continuous(limits=c(18,45),
                     # breaks = c(-3, -2, -1, 0, 1,2,3)
                     ) +
          scale_y_continuous(limits=c(-3,3)
          #            breaks = c(-3, -2, -1, 0, 1, 2, 3)
                     ) +
  xlab("Age")+
  ylab("Mood \n (higher = greater wb)")

#plot to show outliers 

ESM_inner_fix<-ESM_inner %>%
  rename(`Attention State` = attention)

range(ESM_inner$wb)

ESM_inner_fix$`Attention State` <- ifelse(
  ESM_inner_fix$`Attention State` == -1, "Mind Wandering", 
   ifelse(
     ESM_inner_fix$`Attention State` == 1, "Present", 
                                                 ESM_inner_fix$`Attention State`))

ggplot(data=ESM_inner_fix,
       aes(x=age,y=wb, fill=`Attention State`, color=`Attention State`)) +
  geom_jitter(size=.5, alpha=0.5, width = .1)+
  stat_smooth(method="lm", fullrange=TRUE) +
    geom_hline(yintercept = 0)+
  xlab("Age") + ylab("Mood") +
 theme_minimal()+
  theme(legend.position = 'right')+
  theme(plot.title = element_text(face = "bold", hjust = 6, size=24))+
  theme(axis.title.x = element_text(size=24))+
  theme(axis.title.y = element_text(size=24))+
  theme(axis.text.x = element_text(size=24))+
  theme(axis.text.y = element_text(size=24))+
  theme(legend.text = element_text(size=24))+
  theme(legend.title = element_text(size=24))+
  theme(panel.border = element_rect("black",  fill=NA))+
  theme(plot.title = element_text(face = "bold"))+
  theme(plot.title = element_text(hjust = 0))



tab_model(model1a1_fit)

#include valence as a covariate
model1a1_fit <- lmer(formula = wb ~
                     activity+clarity_all_cw2+valence_all_cw2+ #as a covariate
               # +interesting_all_cw2+
                        attention*age+
                 (1|PID), 
                    data=ESM_inner,
                   REML = F) #must set this to F to return loglik and AIC
summary(model1a1_fit)
anova(model1a1_fit, type=3)


modelcompare_fit <- lmer(formula = wb ~
                     activity+
                       clarity_all_cw2+
                       valence_all_cw2+
                attention+age+
                  # attention:age
                 (1|PID), 
                    data=ESM_inner,
                   REML = F)
(r.squaredLR(model1a1_fit)[1]) - (r.squaredLR(modelcompare_fit)[1])






### % of inner speech by attention

ESM_inner1 <- ESM %>%
  group_by(PID) %>%
  mutate(inner_speech = length(inner_speech[inner_speech=="Inner Speech"])) %>%
 mutate(no_inner_speech = length(inner_speech[inner_speech!="Inner Speech"])) %>%
    mutate(percent_inner = 
             (inner_speech/(inner_speech+no_inner_speech))*100)

ESM_inner1$inner_speech
ESM_inner1$no_inner_speech
ESM_inner1$percent_inner


model1a1_fit <- lmer(formula = wb ~
                     activity+clarity_all_cw2+ #as a covariate
                attention*percent_inner+
                 (1|PID), 
                    data=ESM_inner1,
                   REML = F) #must set this to F to return loglik and AIC
summary(model1a1_fit)
anova(model1a1_fit, type=3)
# confint(model1a1_fit)


cor.test(ESM_inner1$percent_inner, ESM_inner1$ffmq_all)



```


```{r Random Slopes}
#fixed slope suggests everyone in data is following a similar pattern, ex. increasing over time or decreasing over time
#random slope allows people to vary in how they progress over time; people may have certain traits that allow them to progress at variable rates or directions
#goal here is to know if your repeated measure if best represented as a fixed or a random slope; do this by comparing both types of models (fixed slope vs random slope) to the unconditional means model 


# model with random intercept and random slope
# note that m1 has the same outcome whether you include the "1+" or not in the ()
m1<- lmer(wb~ attention + (1+attention | PID), ESM_inner, REML=F)

#model with random intercept and fixed slope
m2<- lmer(wb~ attention + (1 | PID), ESM_inner, REML=F)

#model with fixed intercept and random slope
m3<- lmer(wb~ attention + (0 + attention | PID), ESM_inner, REML=F)

anova(m1,m2,m3)

## assuming these are all the same (m1), you can put this into a model together with something like this for the random effect:
# (aware_cw2 + observe_cw2 + describe_cw2 + nonjudge_cw2 + nonreact_cw2 | PID)
# for the above test if doing the 1 + at the beginning (just once, not for each variable) makes a differnece? I don't think it should 
# I think 'simplifying' the model would look like (aware_cw2 | PID) + (observe_cw2 | PID) 



model1a1_fit <- lmer(formula = wb ~
                     activity+clarity_all_cw2+ #as a covariate
                attention+ 
                  (attention|PID)+(1|PID),
                    data=ESM_inner,
                   REML = F) #must set this to F to return loglik and AIC
summary(model1a1_fit)
anova(model1a1_fit, type=3)
# confint(model1a1_fit)



anova(model1a1_fit, model1a_fit)


```



##Descriptive Frequencies
```{r Frequencies}
ESM_inner$attention
# Step 2: Group the data by 'Person' and calculate the count of 'Not Present' and total counts per person.
prop_wander <- ESM %>%  #note this is overall
  group_by(PID) %>%
  summarise(
    not_present_count = sum(attention == -1),
    total_count = n(), 
    Age = first(age), 
    FFMQ = first(ffmq_all)
  )
# Step 3: Calculate the proportion and percentage of 'Not Present' per person.
prop_wander <- prop_wander %>%
  mutate(prop_wander = not_present_count / total_count * 100)
prop_wander

cor.test(prop_wander$Age, prop_wander$prop_wander)
cor.test(prop_wander$FFMQ, prop_wander$prop_wander)


# Step 2: Calculate the correlation coefficient between 'Age' and 'prop_wander'
correlation_result <- cor.test(prop_wander$Age, prop_wander$prop_wander)

# Step 3: Create the correlation plot with the callout
ggscatter(prop_wander, x = "Age", y = "prop_wander", 
          add = "reg.line", cor.coef = TRUE, 
          cor.method = "pearson",
          title = "Correlation between Age and prop_wander",
          xlab = "Age", ylab = "Percentage of Not Present prompts",
          conf.int = TRUE)



filtered_prop_wander <- prop_wander[prop_wander$FFMQ > 0, ]
# Step 2: Calculate the correlation coefficient between 'Age' and 'prop_wander'
correlation_result <- cor.test(filtered_prop_wander$FFMQ, filtered_prop_wander$prop_wander)

# Step 3: Create the correlation plot with the callout
ggscatter(filtered_prop_wander, x = "FFMQ", y = "prop_wander", 
          add = "reg.line", cor.coef = TRUE, 
          cor.method = "pearson",
          title = "Correlation between Trait Mindfulness and prop_wander",
          xlab = "Trait FFMQ", ylab = "Percentage of Not Present prompts",
          conf.int = TRUE)



#try zooming in 
filtered_prop_wander <- prop_wander[prop_wander$Age < 26, ]
# Step 3: Calculate the correlation coefficient between 'Age' and 'prop_wander'
correlation_result <- cor.test(filtered_prop_wander$Age, filtered_prop_wander$prop_wander)
# Step 4: Create the correlation plot with the callout
ggscatter(filtered_prop_wander, x = "Age", y = "prop_wander", 
          add = "reg.line", cor.coef = TRUE, 
          cor.method = "pearson",
          title = "Correlation between Age and prop_wander (Ages < 26)",
          xlab = "Age", ylab = "Percentage of Not Present prompts",
          conf.int = TRUE) 

##A lot of this was already analyzed above, but at least it's all in one place here



## try as bar chart
# Step 2: Convert 'Age' to a categorical variable
prop_wander <- prop_wander %>%
  mutate(Age_Category = as.character(Age))

# Step 3: Calculate means and standard errors for each age category
means_se <- prop_wander %>%
  group_by(Age_Category) %>%
  summarise(
    mean_prop_wander = mean(prop_wander),
    se_prop_wander = sd(prop_wander) / sqrt(n())
  )

# Step 4: Create the bar chart
ggplot(means_se, aes(x = Age_Category, y = mean_prop_wander, fill = Age_Category)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = mean_prop_wander - se_prop_wander,
                    ymax = mean_prop_wander + se_prop_wander),
                width = 0.25, position = position_dodge(0.9)) +
  labs(x = "Age", y = "Mean prop_wander", title = "Mean prop_wander by Age") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        legend.position = "none")  # Remove the legend








##frequencies:

#Attention state
group_by(ESM, attention) %>%
 dplyr::summarise(n = length(attention),
                  `%` = (n/nrow(ESM)*100)) %>%
    arrange(desc(n))

# table1::label(ESM$attention) <- "Attention State"
# table1::table1(~attention, data = ESM, digits=3)

#Inner speech vs not
group_by(ESM, inner_speech) %>%
 dplyr::summarise(n = length(inner_speech),
                  `%` = (n/nrow(ESM)*100)) %>%
    arrange(desc(n))


#Type of inner speech 
group_by(ESM_no_inner, inner_experience) %>%
 dplyr::summarise(n = length(inner_experience),
                  `%` = (n/nrow(ESM)*100)) %>% 
  arrange(desc(n))

#Clarity 
hist(ESM$clarity_all)

group_by(ESM, clarity_all) %>%
 dplyr::summarise(n = length(clarity_all),
                  `%` = (n/nrow(ESM)*100)) %>% 
  arrange(desc(n))


#Interestingness
hist(ESM$interesting_all)

group_by(ESM, interesting_all) %>%
 dplyr::summarise(n = length(interesting_all),
                  `%` = (n/nrow(ESM)*100)) %>% 
  arrange(desc(n))

#Activities
group_by(ESM, activity) %>%
 dplyr::summarise(n = length(activity), 
                `%` = (n/nrow(ESM)*100)) %>%
  arrange(desc(n))
```

```{r Tests}
##Tests:


#attention state by inner experience
table1::label(ESM$inner_experience) <- "Inner Experience"
table1::label(ESM$attention) <- "Attention State"

table1::table1(~inner_experience | attention , data = ESM, digits=3)

#missing here = inner speech ; do ESM_no_inner to omit that 



#wb by Inner speech vs no inner speech 
table1::label(ESM$inner_speech) <- "Inner Speech"
table1::label(ESM$wb) <- "Wellbeing"

table1::table1(~wb | inner_speech , data = ESM, digits=3)

round(anova(lm(
  wb~inner_speech,
  data=ESM)),2)

TukeyHSD(aov(lm(
  wb~inner_speech,
  data=ESM)),
  which="inner_speech")

ggplot(ESM,
       aes(x=inner_speech,y=wb,fill=inner_speech))+
  stat_summary(fun.y="mean", geom="bar", position=position_dodge(),
               # aes(width=.25)
               )+
  stat_summary(geom="errorbar", position=position_dodge(), color='black',
               # aes(width=.25)
               )+
  theme_minimal()+
  ylab('Wellbeing')+
  ylim(-3,3)+
  xlab('Inner Speech')+
  theme(legend.position = 'none')+
  geom_hline(yintercept=0, linetype="solid",
             color = "black", size=1)+
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size=14))+
  theme(axis.title.x = element_text(size=14))+
  theme(axis.title.y = element_text(size=14))+
  theme(axis.text.x = element_text(size=14))+
  theme(axis.text.y = element_text(size=14))+
  theme(panel.border = element_rect("black",  fill=NA))+
  theme(plot.title = element_text(face = "bold"))+
  theme(plot.title = element_text(hjust = 0))


#wb by type of inner speech 
table1::label(ESM_no_inner$inner_experience) <- "Inner Experience"
table1::label(ESM_no_inner$wb) <- "Wellbeing"

table1::table1(~wb | inner_experience , data = ESM_no_inner, digits=3)

round(anova(lm(
  wb~inner_experience,
  data=ESM_no_inner)),2)

TukeyHSD(aov(lm(
  wb~inner_experience,
  data=ESM_no_inner)),
  which="inner_experience")

ggplot(ESM_no_inner,
       aes(x=inner_experience,y=wb,fill=inner_experience))+
  stat_summary(fun.y="mean", geom="bar", position=position_dodge(),
               # aes(width=.25)
               )+
  stat_summary(geom="errorbar", position=position_dodge(), color='black',
               # aes(width=.25)
               )+
  theme_minimal()+
  ylab('Wellbeing')+
  ylim(-3,3)+
  xlab('Inner Experience')+
  theme(legend.position = 'none')+
  geom_hline(yintercept=0, linetype="solid",
             color = "black", size=1)+
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size=14))+
  theme(axis.title.x = element_text(size=14))+
  theme(axis.title.y = element_text(size=14))+
  theme(axis.text.x = element_text(size=14))+
  theme(axis.text.y = element_text(size=14))+
  theme(panel.border = element_rect("black",  fill=NA))+
  theme(plot.title = element_text(face = "bold"))+
  theme(plot.title = element_text(hjust = 0))




#gender by Inner speech vs no inner speech 
table1::label(ESM$inner_speech) <- "Inner Speech"
table1::label(ESM$sex_at_birth) <- "Sex at Birth"

table1::table1(~inner_speech | gender , data = ESM, digits=3)

group_by(ESM, gender) %>%
 dplyr::summarise(n = length(gender),
                  `%` = (n/nrow(ESM)*100)) %>% 
  arrange(desc(n))

table <- table(ESM$gender, ESM$inner_speech)
table
chisq.test(table, simulate.p.value = T)
chisq.posthoc.test::chisq.posthoc.test(table,
                   method = "bonferroni",
                   round = 3,
                   simulate.p.value=T)





#gender by type of inner speech 
table1::label(ESM_no_inner$inner_experience) <- "Inner Experience"
table1::label(ESM_no_inner$sex_at_birth) <- "Sex at Birth"

table1::table1(~inner_experience | gender , data = ESM_no_inner, digits=3)

table <- table(ESM_no_inner$gender, ESM_no_inner$inner_experience)
table
chisq.test(table, simulate.p.value = T)
chisq.posthoc.test::chisq.posthoc.test(table,
                   method = "bonferroni",
                   round = 3,
                   simulate.p.value=T)


#gender by activity 
table1::label(ESM$activity) <- "Activity"
table1::label(ESM$sex_at_birth) <- "Sex at Birth"

table1::table1(~activity | gender , data = ESM, digits=3)

table <- table(ESM$gender, ESM$activity)
table
chisq.test(table, simulate.p.value = T)
chisq.posthoc.test::chisq.posthoc.test(table,
                   method = "bonferroni",
                   round = 3,
                   simulate.p.value=T)


#FFMQ by Inner speech vs no inner speech 
#NOTE - this is off because it's just repeating ffmq as a trait score versus a state score
table1::label(ESM$ffmq_all) <- "FFMQ Total"
table1::label(ESM$inner_speech) <- "Inner Speech"

table1::table1(~ffmq_all | inner_speech , data = ESM, digits=3)

# round(anova(lm(
#   ffmq_all~inner_speech,
#   data=ESM)),2)


#FFMQ by type of inner speech 
table1::label(ESM$ffmq_all) <- "FFMQ Total"
table1::label(ESM$inner_experience) <- "Inner Experience"

table1::table1(~ffmq_all | inner_experience , data = ESM, digits=3)


#FFMQ by activity 
table1::label(ESM$ffmq_all) <- "FFMQ Total"
table1::label(ESM$activity) <- "Activity"

table1::table1(~ffmq_all | activity , data = ESM, digits=3)

#personality by Inner speech vs no inner speech 

#personality by type of inner speech 

#personality by activity 


```





```{r Extra correlations / relationships}

#ffmq_all
round(anova(lm(
  ffmq_all~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  ffmq_all~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=ffmq_all,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#ffmq_no_observe
round(anova(lm(
  ffmq_no_observe~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  ffmq_no_observe~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=ffmq_no_observe,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#awareness
round(anova(lm(
  awareness~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  awareness~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=awareness,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#describe
round(anova(lm(
  describe~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  describe~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=describe,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#observing
round(anova(lm(
  observing~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  observing~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=observing,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#nonjudging
round(anova(lm(
  nonjudging~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  nonjudging~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=nonjudging,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#nonreactivity
round(anova(lm(
  nonreactivity~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  nonreactivity~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=nonreactivity,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#openness
round(anova(lm(
  openness~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  openness~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=openness,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#conscientiousness 
round(anova(lm(
  conscientiousness~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  conscientiousness~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=consientiousness,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#extraversion
round(anova(lm(
  extraversion~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  extraversion~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=extraversion,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#agreeableness
round(anova(lm(
  agreeableness~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  agreeableness~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=agreeableness,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#neuroticism
round(anova(lm(
  neuroticism~attention,
  data=ESM)),2)
TukeyHSD(aov(lm(
  neuroticism~attention,
  data=ESM)),
  which="attention")
ggplot(ESM,
       aes(x=attention,
           y=neuroticism,
           fill=attention))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()






#
#ffmq_all
round(anova(lm(
  ffmq_all~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  ffmq_all~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=ffmq_all,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#ffmq_no_observe
round(anova(lm(
  ffmq_no_observe~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  ffmq_no_observe~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=ffmq_no_observe,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#awareness
round(anova(lm(
  awareness~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  awareness~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=awareness,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#describe
round(anova(lm(
  describe~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  describe~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=describe,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#observing
round(anova(lm(
  observing~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  observing~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=observing,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#nonjudging
round(anova(lm(
  nonjudging~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  nonjudging~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=nonjudging,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#nonreactivity
round(anova(lm(
  nonreactivity~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  nonreactivity~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=nonreactivity,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#openness
round(anova(lm(
  openness~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  openness~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=openness,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#conscientiousness 
round(anova(lm(
  conscientiousness~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  conscientiousness~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=consientiousness,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#extraversion
round(anova(lm(
  extraversion~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  extraversion~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=extraversion,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#agreeableness
round(anova(lm(
  agreeableness~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  agreeableness~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=agreeableness,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#neuroticism
round(anova(lm(
  neuroticism~inner_speech,
  data=ESM)),2)
TukeyHSD(aov(lm(
  neuroticism~inner_speech,
  data=ESM)),
  which="inner_speech")
ggplot(ESM,
       aes(x=inner_speech,
           y=neuroticism,
           fill=inner_speech))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()







#
#ffmq_all
round(anova(lm(
  ffmq_all~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  ffmq_all~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=ffmq_all,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#ffmq_no_observe
round(anova(lm(
  ffmq_no_observe~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  ffmq_no_observe~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=ffmq_no_observe,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#awareness
round(anova(lm(
  awareness~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  awareness~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=awareness,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#describe
round(anova(lm(
  describe~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  describe~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=describe,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#observing
round(anova(lm(
  observing~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  observing~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=observing,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#nonjudging
round(anova(lm(
  nonjudging~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  nonjudging~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=nonjudging,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#nonreactivity
round(anova(lm(
  nonreactivity~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  nonreactivity~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=nonreactivity,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#openness
round(anova(lm(
  openness~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  openness~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=openness,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#conscientiousness 
round(anova(lm(
  conscientiousness~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  conscientiousness~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=consientiousness,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#extraversion
round(anova(lm(
  extraversion~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  extraversion~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=extraversion,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#agreeableness
round(anova(lm(
  agreeableness~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  agreeableness~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=agreeableness,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
#neuroticism
round(anova(lm(
  neuroticism~activity,
  data=ESM)),2)
TukeyHSD(aov(lm(
  neuroticism~activity,
  data=ESM)),
  which="activity")
ggplot(ESM,
       aes(x=activity,
           y=neuroticism,
           fill=activity))+stat_summary(fun.y="mean", geom="bar", position=position_dodge(),)+stat_summary(geom="errorbar", position=position_dodge(), color='black')+theme_minimal()
```

```{r No inner speech}
#just copy paste the confirmatory analyses here and replace with no inner speech dataframe

model0_fit <- lmer(formula = wb ~ 1 + (1|PID), 
              data=ESM_no_inner)
summary(model0_fit)

VarCorr(model0_fit)
RandomEffects <- as.data.frame(VarCorr(model0_fit))
RandomEffects
ICC_between <- RandomEffects[1,4]/(RandomEffects[1,4]+RandomEffects[2,4]) 
round(ICC_between*100,2)
# of the total variance in DV, XX% is attributable to between-person variation 
# Any value below 5% here suggests clustering is not taking place and MLM should not take place

round((100-(ICC_between*100)),2)
# whereas XX% is attributatable to within-person variation.



##attention model
model1a_fit <- lmer(formula = wb ~
                     activity+clarity_all_cw2+ #as a covariate
                attention+
                 (1|PID), 
                    data=ESM_no_inner,
                   REML = F) #must set this to F to return loglik and AIC
summary(model1a_fit)
anova(model1a_fit, type=3)
confint(model1a_fit)

#effect size 
#change # for each variable
modelcompare_fit <- lmer(formula = wb ~
                     activity+
                       clarity_all_cw2+
                # attention+
                 (1|PID), 
                    data=ESM_no_inner,
                   REML = F)
(r.squaredLR(model1a_fit)[1]) - (r.squaredLR(modelcompare_fit)[1])







```



```{r Stricter Inclusion}
# CondA  - episode 2
#make sure no blanks either like just a space bar 
CondA$`ep2#1_1_1.x`
CondA$`ep2#1_1_1.y`


CondA <- 
  CondA %>% drop_na(`ep2#1_1_1.x`, `ep2#1_1_1.y`) 


```





```{r Extra Probably Unneccesary code}

###plot between-person differences 
ggplot(data=CondA_long, aes(x=extraversion, 
                            y=wb_cb2, #note I changed overall wb to between-person for these. I think unless it's used                                          as a DV in a MLM, you need to specify it here 
                            group=factor(PID)), legend=FALSE) +
  geom_point(colour="gray40") +
  geom_smooth(aes(group=1), method=lm, se=FALSE, fullrange=FALSE, lty=1, size=2, color="blue") +
  xlab("Extraversion") + ylab("WellBeing") +
  theme_classic() +
  theme(axis.title=element_text(size=16),
        axis.text=element_text(size=12),
        plot.title=element_text(size=16, hjust=.5)) +
  ggtitle("Between-Person Association of Extraversion and Mean Wellbeing Scores")

# visualize wb fluctuations over time (to show between and within person variation)
# library(lattice)
# xyplot(wb ~ as.numeric(ESMg$start.time) | PID, data=CondA_long, type = c("p", "r"))


```
`

